### 2022-01-25 paper.Rmd
adding paper

---
title: "Two measures are better than one: Combining iconicity ratings and guessing experiments for a more nuanced picture of iconicity in the lexicon"
output:
  bookdown::word_document2:
    reference_docx: wordstyles.docx
    toc: true
    toc_float: true
    number_sections: true
    css: custom.css
always_allow_html: true
bibliography: sources.bib

---

```{r packages, include=FALSE}
library(tidyverse)
library(kableExtra)
library(bookdown)
library(report)
library(lmerTest)
library(plotly)
library(corrr)
library(boot)
library(zeallot)
library(pander)
library(sjPlot)
library(ggeffects)
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message = FALSE)
```

**Abstract**

Iconicity in language is receiving increased attention from many fields, but our understanding of the roles of iconicity in language is only as good as the measures we use to quantify it. We conducted iconicity rating and guessing experiments with 300 Japanese ideophones and prosaic words with similar meanings, (e.g. *fuwafuwa* ‘fluffy’, *jawarakai* ‘soft’), and found that the two measures together presented a more complete picture of iconicity than either alone. For both groups of words, ratings and guesses were positively correlated—emphasising that both pick up on the same form-meaning associations. Ideophones were consistently associated with higher iconicity ratings, but not higher guessing accuracy. We suggest that the structural markedness of ideophones enhances their perceived iconicity in the rating task, but does not provide any advantage (over and above that provided by form-meaning associations) in the guessing task. Thus, guesses and ratings could be used together to tease apart the relative contribution of structural markedness to iconic effects. Some ideophones were also guessed very poorly, highlighting that construals of iconicity can be language-specific. Combining guesses with ratings from native speakers is thus recommended for a fuller picture of language-external and language-internal mappings (Occhino et al. 2017).

We also critically evaluated different rating and guessing paradigms, and introduce a new guessing paradigm that improves on the robustness, sensitivity and discriminability of previous approaches. Finally, we introduce a reproducible workflow for creating rating and guessing experiments in the form of a Python package, `icotools`, which we hope will improve comparability between future studies, enabling others to confirm and build on current findings, and to ask new questions about the roles of iconicity in language.

# Introduction

What does it mean when we say that something is a "good word for" a concept? Certain words, like *klutz*, *schmooze*, and *smush*, seem to "suit" their meanings. We may have a sense that the French *belle* is a more appropriate word for BEAUTY than the Swedish *vacker*. Such intuitions are likely to be somewhat subjective, and influenced by our own linguistic experiences, but we all have them. The idea that certain forms can be particularly suited to certain meanings is known as *iconicity*.

Iconicity--defined here as a perceived resemblance between aspects of form and meaning--is now increasingly recognised as a *design feature of language* [see e.g. @perniss_iconicity_2010; @perniss_bridge_2014; @dingemanse_arbitrariness_2015 for a review], raising important questions about where iconic mappings come from, and what they do. To answer these questions, we first need to be able to *identify* iconicity in language and, ideally, to *measure* it.

Approaches to measuring iconicity can be divided into descriptive, data-driven, and behavioural methods [@motamedi_iconicity_2019]. Of these, only descriptive approaches target *iconicity* directly, with other methods simply identifying form-meaning association *biases*--whether these be based on resemblance (as in iconicity), co-occurrence (indexicality), statistically driven associations (systematicity), functional advantages, or other factors.

With descriptive approaches, iconicity as a theoretical concept is coded for directly (e.g. @pietrandrea_iconicity_2002; @hwang_body_2017; @ostling_visual_2018; @thompson_defining_2019; @voronin_osnovy_2006; @flaksman2020stanislav). This is more common and straightforward for sign languages than for spoken languages [@thompson_defining_2019]. It is usually done manually, but Östling et al. -@ostling_visual_2018 have shown for sign languages that (for some mappings at least) this can also be automated. Such studies usually involve cross-linguistic data, and aim to uncover universalities in how different languages map sound to meaning--that is, *where* iconicity comes from.

A wider variety of approaches target iconicity *indirectly* through related phenomena. For example, data-driven approaches (e.g. @wichmann_sound_2010; @blasi_soundmeaning_2016; @joo_phonosemantic_2019; @johansson_typology_2020; @winter_trilledr) use comparisons across unrelated languages to identify form-meaning correspondences that occur at rates higher than chance. This requires large amounts of parallel data from distinct phyla, and existing studies usually focus on basic vocabulary--where such data is most readily available. Like descriptive approaches, data-driven approaches identify *specific* form-meaning associations involved in iconic effects, but with the added advantage of not needing to rely on the intuitions and manual labour of individual researchers. However, they *do* rely on the existence of translation equivalents in multiple languages for the words under study. This can pose a particular challenge for highly iconic words, as these tend to also have highly specific meanings (@lupyan_language_2018; @akita_toward_2012). Thus, such approaches are less likely to be helpful for those with existing data for which iconicity measures are required.

Another body of work which capitalises on big data involves the study of *affective iconicity* [e.g. @ullrich_phonological_2016; @aryani_why_2018]. These studies use large datasets of affective norms to identify phonological segments loaded with affective meaning (by taking average affectiveness values across all words containing those segments, and identifying segments with values deviating from the global neutral mean). Although limited to associations involving affect, this approach has been successfully used to investigate iconic effects in language processing [@schmidtke_effects_2018; Ullrich in prep; @aryani_affective_2018], and has even been used to explain the affective meaning of poems [@ullrich_relation_2017].

Behavioural approaches involve the collection of data from naive experimental participants, which can reveal something about the iconicity of given form-meaning pairings. The only requirement is the human participants for the study, and the largest amount of iconicity measurements from the widest variety of languages have been collected using these methods. There are two main approaches: iconicity rating tasks and guessing experiments.

In iconicity rating tasks, the concept of iconicity is explained to participants, and participants are asked to rate the iconicity of given form-meaning pairs directly [e.g. @vinson_british_2008; @perry_iconicity_2015; @winter_which_2017; @occhino_iconicity_2017; @thompson_iconicity_2020; @punselie_iconicity_2020]. Measurements from these studies are shown to correlate in meaningful ways with factors related to iconicity--e.g. encoding of sensory information [@winter_which_2017], semantic neighbourhood density [@sidhu_lonely_2018], age of acquisition [@vinson_british_2008; @perry_iconicity_2015], facilitated processing [@thompson_link_2009; @occhino_role_2020], word class [@perry_iconicity_2015; @thompson_iconicity_2020], semantic domain [@punselie_iconicity_2020], funniness and structural markedness [@dingemanse_playful_2020]. However, ratings given are strongly influenced by the linguistic experience of participants (@occhino_iconicity_2017; @sevcikova_sehyr_perceived_2019), which could make comparing measurements between studies difficult.

In guessing experiments, participants are asked to guess the meaning of foreign/novel signs from a choice of two or more alternatives [e.g. @kohler_gestalt_1929; @tsuru_problem_1933; @brown_phonetic_1955; @kunihira_effects_1971; @ramachandran_synaesthesia_2001; @dingemanse_what_2016; @tzeng_specificity_2017; @perlman_iconicity_2015; @perlman_people_2018; @lockwood_sound-symbolism_2016]. Signs whose meanings are correctly guessed at rates higher than chance are considered iconic. The guessability of signs has also been linked to facilitated processing [@ormel_role_2009] and learnability [@perlman_people_2018; @lockwood_sound-symbolism_2016], and correlated with iconicity ratings [@punselie_iconicity_2020]. However, some signs that were given low iconicity ratings were actually highly guessable, while there were also a few signs that, despite receiving high ratings, were not easily guessed  [@punselie_iconicity_2020: 23]. This suggests that guessing and rating tasks may tap into slightly different constructs, or be sensitive to experimental design constraints.

Despite these complications, behavioural measures of iconicity are particularly appealing for four reasons: (1) they can be applied to any kind of dataset, (2) they are highly scalable, being particularly amenable to online, crowd-sourced data collection, (3) they are tweakable, meaning that we can experiment with different experimental designs to figure out exactly what these measures are telling us, and (4) they are amenable to standardisation, making them a good option for reproducibility. In fact, they are the only measures of iconicity that we know of to combine all these things.  Moreover, that the measures correlate with each other and with a variety of other meaningful phenomena speaks to their validity.

In this study, we seek to better understand what these guesses and ratings are measuring by comparing and contrasting iconicity ratings and guesses for 300 Japanese words from the sensory vocabulary of Japanese. Sensory language was chosen as this is a domain high in iconicity, where iconicity offers clear advantages [@winter_which_2017]. The data contained a mix of ideophones--depictive, eye-catching words like *fuwafuwa* 'soft' and *pikapika* 'sparkly' that "invite and afford the construal of iconic mappings between form and meaning" [@akita_ideophone_2019: 18]--along with prosaic lexical items, like *yawai* 'soft' and *hikaru* 'shine', which are not necessarily expected to be lacking in iconicity--especially given their sensory meanings--but which are less obvious about it. We were particularly interested in how the iconicity measures for these words would compare between the rating studies--where participants are asked to make a conscious decision about the iconicity of the words--and the guessing studies--which tap into more unconscious biases. We find that when used together, the two methods shed light on each other, as well as raising pertinent questions about where iconicity effects come from. Our conclusion is that, for many of the questions that we have about iconicity in language, two measures may be better than one.

To investigate how to get the most out of each measure, we compare and contrast different rating and guessing paradigms, and in particular introduce a new guessing paradigm that improves on the robustness, discriminability and sensitivity of previous approaches. Finally, to promote the use of these new measures, we introduce a reproducible workflow for automatically generating rating and guessing experiments in a standardised format, via a python package `icotools` [(https://pypi.org/project/icotools/)](https://pypi.org/project/icotools/), with support for a variety of stimulus formats (audio, video, and images). This will make the collection of behavioural based iconicity measures quicker, easier, and more comparable between different studies.

# Method

## Stimuli

The stimuli were 300 Japanese words from the domain of sensory perception, including both ideophones and prosaic lexical items. For all tasks, the words were presented to participants as audio files. The audio files were synthesised using the Google Cloud Text-to-Speech API [(https://cloud.google.com/text-to-speech)](https://cloud.google.com/text-to-speech), with the female Japanese Wavenet voice ja-JP-Wavenet-B. They were then edited using Praat [@boersma_praat_2020] to have a flat pitch of 200Hz. Expressive prosody can enhance performance in guessing tasks [@kunihira_effects_1971; @dingemanse_what_2016], and so using a flat intonation was seen as the best way to ensure comparisons between the words were fair and not influenced by the prosody in a particular recording. ^[We also considered synthesising all the words to have a marked intonation. However, different word lengths would make changes in pitch more dramatic in shorter words compared to longer words, affecting words of different lengths unequally.]. While flat, synthetic voices may be the best option for comparability, they are not a natural reflection of real-world experiences with iconicity--which involve not only segments but also prosody and even multimodal cues (e.g. accompanying gesture). Thus, if anything the results in this and similar studies likely *underestimate* iconicity in language.

In all studies, participants were instructed to use headphones throughout the experiment, and could not procede to the experiment without first passing a listening test designed to require the use of headphones @woods_headphone_2017. The response buttons in each trial also did not appear until *after* the audio files had finished playing. This ensured that participants could not respond without first listening to the audio files.

## Data collection

All studies were conducted online, with participants recruited through the crowd sourcing service Prolific (www.prolific.co). The participants were monolingual English speakers residing in England, with no prior knowledge of Japanese. Although rating tasks are often done with native speakers, we used English speakers in order to make the results as comparable as possible between the guessing and the rating tasks.

The words were split across 12 different experiments, in such a way that each experiment had a balance of words that were expected to be iconic, versus words that were not expected to be iconic. In addition, two 'practice words' and three 'control words' were included in every experiment. The practice items were used to give participants time to familiarise themselves with the experiment design, and were not included in the results. The control items were chosen from words found to be very iconic/highly guessable in previous studies, and were included as a check to identify participants who were perhaps not performing the task as intended. The first two trials in every experiment were the two 'practice words', while the order of the rest of the words in the experiment, including the control words, was randomly varied between participants. After finishing the experiment, participants were asked to describe the task they were performing during the experiment. This was used as an attention check, and to identify participants who had misunderstood the experiment instructions. Strange or lacking task descriptions, particularly when coupled with poor performance on the control items, were used to identify and exclude results from participants who were likely not performing the task as intended.

For the rating task, no data was excluded. There were some task descriptions where participants claimed to be rating based on whether the Japanese word sounded similar to its English translation, rather than whether they thought it was an appropriate word for that meaning. However, as their actual ratings did not seem to reflect this and were similar to those of other participants, their responses were not excluded. The vast majority of participants' task descriptions indicated that they had understood the task very well.

For the first version of the guessing task, in which participants had to match a given form to its correct meaning, data from three participants was excluded. In one case, the participant indicated that they were choosing the translations based on whether they sounded similar to the Japanese word (rather than based on their meaning). In the other two cases, the participants did not provide a task description and performed poorly on the control items, so the data was excluded as it was not clear that they were paying attention/understood the task correctly. In the new version of the guessing task, in which participants had to match a given meaning to its correct form, no data was excluded. Participants' task descriptions indicated that they had understood the task very well and they also performed well on the control items.

```{r identify and exclude outlying participants}
# for guessing between translations
responses_trans <- read.csv('responses-guessingtrans.csv')
control_items <- c("pyoNpyoN","katai","hayai")

responses_trans%>%
  filter(word %in% control_items)%>%
  select(Prolific.ID,word,answer,time_taken,Task.Description)%>%
  group_by(Prolific.ID)%>%
  mutate(check_score=sum(answer=='correct')/sum(answer=='incorrect'|answer=='correct'))%>%
  select(-word,-answer)%>%
  unique()%>%
  # also look at whether they were particularly slow or fast to do the experiment
  mutate(deviation_timetaken=time_taken-mean(.$time_taken))%>%
  mutate(std_deviation=sd(.$time_taken))->examine_participants

# results from the following participants were excluded
exclude_participants<-c('5b3648e7f726b2000192b3f4','5f350486d0c0764216b6745e','5c426de31ddd660001c99cdd')

guesses_trans <- responses_trans%>%
  filter(!(Prolific.ID %in% exclude_participants))

# for guessing between words
guesses_words<-read.csv('responses-guessingwords.csv')
control_items <- c("pyoNpyoN","katai","hisohiso")

guesses_words%>%
  filter(word %in% control_items)%>%
  select(prolific_ID,word,answer,TimeTaken,TaskDesc)%>%
  group_by(prolific_ID)%>%
  mutate(check_score=sum(answer=='correct')/sum(answer=='incorrect'|answer=='correct'))%>%
  select(-word,-answer)%>%
  unique()%>%
  # also look at whether they were particularly slow or fast to do the experiment
  mutate(deviation_timetaken=TimeTaken-mean(.$TimeTaken))%>%
  mutate(std_deviation=sd(.$TimeTaken))->examine_participants

# for ratings
ratings <- read_csv("responses-ratings.csv")

ratings%>%
  filter(form=="pyoNpyoN"|form=="katai"|form=="hisohiso"|form=="yoroyoro"|form=="fuwafuwa")%>%
  select(experiment,prolificID,form,rating,taskdesc)->ratings_examine

#ratings_examine%>%kable()%>%kable_styling()
```

Each experiment took a median of 6 minutes to complete, and participants were paid £0.75 for their participation (based on Prolific's 'good' hourly rate of £7.50). Prolific's prescreening features were used to ensure that participants who had already participated in one experiment (regardless of whether it was a rating or guessing task) could not participate in any subsequent experiments. For each word, we collected 30 guesses and 30 ratings from different participants.

## Guessing experiments -- guessing between translations

In the first guessing experiments, participants were presented with a Japanese word and asked to guess its meaning from a choice of two possible translations. Some of the ideophones in the data had very specific meanings, which were difficult to capture in a single English word. To provide more context, the translations were given in sentence frames, with the translation word in capitals. The instructions were as follows:

> We are interested in how well people can guess the meanings of words in foreign languages. In this experiment, we are interested in your intuitions about the meanings of JAPANESE words.
You will hear 25 Japanese words. After listening to each word, try to guess its meaning from a choice of two possible English translations. For context, meanings are given in a sentence, with the intended meaning in CAPITALS.
For example, if you think the word could mean BRIGHT in the sentence 'The sun is BRIGHT', choose that sentence. If you think it could mean ROUND in the sentence, 'The sun is ROUND', choose that sentence. Trust your gut, and good luck!

A sample trial is shown in Figure \@ref(fig:guessingtrans).

```{r guessingtrans, fig.cap="Guessing task - guessing between translations"}
knitr::include_graphics("images/guessingtransdemo.PNG")
```

The same formulaic structure, "After X, Y", was used for all the sentences--where Y is the target perception and X is the event that causes it. As some sensory modalities (e.g. sound) may better lend themselves to the construal of iconicity than others (e.g. taste), correct translations were always paired with foil translations from the same modality (e.g. sound translations were only paired with other sound translations, and taste translations with other taste translations, etc.). To make the difficulty of the task comparable between different trials, only words that were neither synonyms nor antonyms of the correct translation were chosen as foils. Finally, the length of the sentences was also kept consistent (to a difference of no more than 5 characters) between pairings of translations and foils.

To test the robustness of the guessing procedure to different choices of translation and foil words, the same words were tested multiple times with different translations and foils. We were concerned that participants could choose particular translations because of how they sound (particularly if they sounded similar to the Japanese word), rather than based on their meanings as we intended. So, to minimise any potential effects from this, as much as possible phonologically distinct synonyms were chosen as alternative translations (e.g. SMALL|TINY, BIG|LARGE).

Pilot results showed that in several cases the guessability of a word did differ considerably depending on the translation or foil word used. Some examples are shown in Table \@ref(tab:weirdcases).

```{r weirdcases}
guesses_trans%>%
  mutate(word_spec=paste(word,concept,sep="_"))->guesses_trans

guesses_trans%>%
  filter(word_spec=="piiN_LONG"|word_spec=="hakkiri_CLEAR-HEADED")%>%
  filter(!(grepl("SHARP",answer_sen)))%>%
  select(answer_sen,foil_sen,answer)%>%
  group_by(answer_sen,foil_sen)%>%
  count(answer)%>%
  pivot_wider(names_from=answer,values_from=n, values_fill=0)%>%
  knitr::kable(col.names = c("Answer sentence", "Foil sentence","correct","incorrect"),caption="Effect of different foils and translations on guessing results for hakkiri 'CLEAR HEADED' and piiN 'LONG'")%>%
  kable_styling()

```

We hypothesised that, as well as considering the meaning of the translations and foils, participants may be driven to one option over another because of the way the words sound (particularly if they sounded similar to the Japanese word being tested), or because of lexical features of the words like frequency, valence, arousal, or any other associations they may have with these words.

While we could not do anything about the sound of the words (other than using multiple translations), we realised that we could eliminate at least some of the complications caused by other properties of the words if we flipped the design of the guessing experiments on its head, so that instead of choosing the correct English meaning for a given Japanese word, participants had to choose the correct Japanese word for a given English meaning. In this way, there was only one English word involved in the task, and the options participants chose between were simply two Japanese words which they knew nothing about, other than how they sound. This design was also more comparable to the rating task--where participants are also given the meaning of the word first. We therefore decided to use this new design for the rest of the guessing experiments.

## Guessing experiments -- guessing between words

For the new version of the guessing experiments, we minimised the amount of English words involved in the task by having participants match a single English translation to the corresponding word in Japanese, choosing between two possible Japanese words. The instructions used were as follows:

> We are interested in how well people can guess words in foreign languages. In this experiment, you will be asked to match the English translation with the corresponding word in JAPANESE, guessing from a choice of two Japanese words.

A sample trial is shown in Figure \@ref(fig:guessingwords).

```{r guessingwords, fig.cap="Guessing task - guessing between words"}
knitr::include_graphics("images/guessingwords.PNG")
```

This time, instead of using sentence frames for context, we kept the amount of English to a minimum by using only single-word translations where possible, and where more context was needed this was provided in brackets, as in Figure \@ref(fig:guessingwordsspec).

```{r guessingwordsspec, fig.cap="Guessing task - guessing between words"}
knitr::include_graphics("images/guessingwordsspec.PNG")
```

The foil words were artificially generated to be as phonologically distinct as possible from the answer word, while still conforming to Japanese phonology. For every word, three different foil words were generated by substituting each consonant with its top three most phonologically distant consonants in the Japanese sound system. Phonological distances were calculated using the Phonological Corpus Tools software [@hall_phonological_2019], with the feature system provided by Mielke [-@mielke_phonetically_2012]. Vowels were substituted by rotating the vowel space 180 degrees, so that /a/ > /u/, /i/ > /a/, /u/ > /i/, /e/ > /o/, and /o/ > /e/. Finally, reduplicated words were ‘unreduplicated’ in their foil words. For example, the foils for *fuwafuwa* were *rizyu*, *gityu* and *nitsu* (not *rizyurizyu*, *gityugityu* and *nitsunitsu*).

By using foil words that sound as different as possible to the target word, we hoped to improve the sensitivity of the measure to any potential iconicity in the target word, as if the target word *is* iconic for a concept, then a word that sounds very different to it should be a bad fit for that same concept--making the choice between the two easier. To test whether this was really the case, we ran one of the experiments a second time with foils that were randomly chosen from the other trials in the experiment, instead of using phonologically distinct foils.

## Rating task

We also conducted an iconicity rating task with the same words. In the rating task, the concept of iconicity was defined to participants as "when a word and its meaning resemble one another", using the English examples *wiggle*, *jiggle*, and *wriggle*. The instructions stated that "Even people who do not speak any English can get a sense of the meaning of these words", and contrasted them with words like *walk* and *run* whose meanings are "not so intuitive". The full instructions given were as follows:

> Some words seem to 'fit' their meanings. For example, consider the English words wiggle, jiggle, and wriggle.  
We have an intuitive sense of the meanings of these words, because there is a resemblance between the words and their meanings.  
Even people who do not speak any English can get a sense of the meaning of these words.  
Words like walk and run on the other hand are not so intuitive; people who do not know any English would not be able to guess what these words mean.  
In this task, you will listen to some Japanese words, and we will tell you their meanings. You will then be asked to judge whether there is a resemblance between the word and its meaning.

Participants had to listen to the Japanese words and were told their meanings, then asked to rate the resemblance between the word and its meaning on a scale from 0 'No resemblance' to 6 'Strong resemblance'. Previous studies [@perry_iconicity_2015] also used a negative end of the scale (corresponding to a 'bad resemblance'). However, follow-up analysis found that the negative end of the scale was both underused and inconsistently used, suggesting that anti-iconic relationships are difficult to assess [@motamedi_iconicity_2019]. For this reason, we decided to only use a positive scale in this study. A sample trial is shown in Figure \@ref(fig:ratingdemo).

```{r ratingdemo, fig.cap="Rating task"}
knitr::include_graphics("images/ratingdemo.PNG")
```

As with the guessing experiments, the translation shown for each participant was varied randomly between a set of (wherever possible) phonologically distinct synonyms.

# Results

## Robustness to different choices of translations and foils

We first investigated whether ratings and guesses were robust to different choices of translations (for ratings and guesses) and foils (for guesses only). For each word separately, we performed Fisher's Exact Tests on the guessing data, and anovas on the rating data, to determine whether guessing performance or ratings given differed significantly between different translations and foils.

```{r test robustness guessing experiments}
# for guessing between translations
words<-unique(guesses_trans$word_spec)

# see whether the responses differed significantly depending on the answer sentence given
n=0
doubly_tested_words <- c()
weird_words<-c()
for(w in words){
  d<-subset(guesses_trans,word_spec==w)
  t<-table(d$answer_sen,d$answer)
  # not all words were tested with more than one translation as for some concepts there was only one English word for the concept
  if (nrow(t)>1){
    doubly_tested_words <- c(doubly_tested_words,w)
    n=n+1
    p_val<-fisher.test(t)$p
    if (p_val<0.05){
      weird_words<-c(weird_words,w)}
}
}

# see whether the responses different signficantly depending on the foil sentence given
for(w in words){
  d<-subset(guesses_trans,word_spec==w)
  t<-table(d$foil_sen,d$answer)
  if (nrow(t)>1){
    doubly_tested_words <- c(doubly_tested_words,w)
    n=n+1
    p_val<-fisher.test(t)$p
    if (p_val<0.05){
      weird_words<-c(weird_words,w)}
}
}

weird_res_trans <- length(unique(weird_words))/length(unique(doubly_tested_words))

# for guessing between words

guesses_words%>%
  mutate(word_spec=paste(word,concept,sep="_"))->guesses_words

words<-unique(guesses_words$word_spec)

# see whether the responses differed significantly depending on the answer sentence given
n=0
doubly_tested_words <- c()
weird_words<-c()
for(w in words){
  d<-subset(guesses_words,word_spec==w)
  t<-table(d$trans,d$answer)
  if (nrow(t)>1){
    doubly_tested_words <- c(doubly_tested_words,w)
    n=n+1
    p_val<-fisher.test(t)$p
    if (p_val<0.05){
      weird_words<-c(weird_words,w)}
}
}

# see whether the responses different signficantly depending on the foil sentence given
for(w in words){
  d<-subset(guesses_words,word_spec==w)
  t<-table(d$foil,d$answer)
  if (nrow(t)>1){
    doubly_tested_words <- c(doubly_tested_words,w)
    n=n+1
    p_val<-fisher.test(t)$p
    if (p_val<0.05){
      weird_words<-c(weird_words,w)}
}
}

weird_res_words <- length(unique(weird_words))/length(unique(doubly_tested_words))
```

```{r ratings robustness}
# for the ratings we are using anovas which are not as robust to small amounts of data as the fisher test

# therefore I only looked at data where we had at least ten ratings per translation
ratings%>%
  group_by(identifier)%>%
  add_count(trans)%>%
  filter(n>=10)%>%
  select(identifier,trans,rating)->data

# then within this, we need to get the data where we have at least two translations per word
data%>%
  select(identifier,trans)%>%
  unique()%>%
  group_by(identifier)%>%
  mutate(count=n())%>%
  arrange(identifier)%>%
  filter(count>1)%>%
  pull(identifier) -> test

data <- subset(data,identifier %in% test)

words <- unique(data$identifier)
weird_res <- c()
for(w in words){
  d <- subset(data,identifier==w)
  n_trans <- length(unique(d$trans))

  if(n_trans==2){
  t <- t.test(d$rating~d$trans)
  p <- t$p.value
  }
  else{
    t <- summary(aov(d$rating~d$trans))
    p <- t[[1]][[5]][1]
  }

  if(p<0.05){weird_res <- c(weird_res,w)}
}

weird_res_ratings <- length(weird_res)/length(words)
```

In the first pilot of the guessing task--where participants were guessing between English translations--11 out of the 45 words tested (=24%) showed significant differences in their guessability when either the translation and/or the foil was changed. In the second version of the guessing task--where participants were guessing between Japanese words--15 out of the 131 words tested (=11%) showed significant differences in their guessability when either the translation and/or the foil was changed. In the rating task, 12 out of 92 words tested (=13%) showed significant differences in their iconicity rating when the translation word was changed^[We excluded translations with fewer than 10 ratings from this analysis as the t-test is less robust against small sample sizes than the fisher test.].

## Sensitivity and discriminability

To test whether using phonologically distinct foils in the guessing experiments improved their sensitivity to iconicity, a subset of 30 words were tested twice--once with phonologically distinct "opposite" foils, and once with random foils.

The number of these words which were guessed significantly above chance (with a sample of 30 guesses per word, an accuracy greater than 2/3 is needed to be sure the true accuracy is above 0.5) was higher in the experiment with opposite foils than in the experiment with random foils. Using opposite foils, half of the words in the sample (15/30) were guessed significantly above chance, whereas with the random foils this number fell to just 1 in 5 words (6/30). Only two words were guessed significantly above chance in the random foil condition, but not in the opposite foil condition. However, both were guessed numerically above chance in the opposite foil condition as well (with accuracies of 52% and 57%). The differences between the two conditions are shown in Figure \@ref(fig:sensitivitycheck). A chi-squared test confirmed the differences to be significant (χ2(1)=4.69,p=.03).

```{r sensitivitycheck,fig.cap="Words guessed significantly above chance using opposite versus random foils"}

# we used this binomial test to figure out how many correct guesses (out of 30) were needed to have a result significantly different from chance--it's 21
#binom.test(21,30,p=.5)

randomfoils <- read_csv("results-randomfoils.csv")

randomfoils%>%
  group_by(identifier)%>%
  mutate(score=sum(result=="correct")/sum(result=="correct"|result=="incorrect"))%>%
  select(identifier,score)->randomres

guesses_words%>%
  group_by(word_spec)%>%
  mutate(score=sum(answer=="correct")/sum(answer=="correct"|answer=="incorrect"))%>%
  select(identifier=word_spec,score)->oppres

comparison <- left_join(randomres,oppres,by="identifier")%>%
  rename(random_foils=score.x,opp_foils=score.y)%>%unique()

comparison%>%
  rename(`random foils`=random_foils,`opposite foils`=opp_foils)%>%
  pivot_longer(c("random foils","opposite foils"),names_to="design",values_to="accuracy")%>%
  mutate(`guessing accuracy`=ifelse(accuracy>2/3,"significantly above chance","at chance"))%>%
  ungroup()%>%
  select(design,`guessing accuracy`)%>%
  group_by(design)%>%
  count(`guessing accuracy`)%>%
  ggplot(aes(x=design,y=n,fill=`guessing accuracy`))+geom_col()+theme_classic()+labs(x="Design",y="Number of words")+scale_fill_manual(values=c("#CCCCCC","#000000"))
```

```{r chi square}
comparison%>%
  rename(`random foils`=random_foils,`opposite foils`=opp_foils)%>%
  pivot_longer(c("random foils","opposite foils"),names_to="design",values_to="accuracy")%>%
  mutate(`above chance`=ifelse(accuracy>2/3,"y","n"))->comparison

#table(comparison$design,comparison$`above chance`)
#chisq.test(table(comparison$design,comparison$`above chance`))
```

We also compared the distributions of guessing accuracies and mean iconicity ratings between the different methods. Since the iconicity ratings in this study were collected from naive participants who did not speak any Japanese, whereas rating studies more commonly use native speaker participants, I added one more plot to the figure showing the distribution of iconicity ratings in a separate study by Thompson et al. [-@thompson_iconicity_2020]. Thompson et al. collected iconicity ratings for Japanese words from native Japanese speaking participants. Their dataset contained a wider variety of words than the current dataset, and they also used a different scale. Their scale went from -5 'antiiconic' to 5 'iconic', with 0 being labelled as 'arbitrary'. The scale in this study started at 0 (also labelled as 'arbitrary', or "no resemblance between the word and its meaning"), and went up to 6 for "strong resemblance between the word and meaning". To make the data more comparable between the two studies, and because previous studies have found the negative ratings unreliable [@motamedi_iconicity_2019], I have filtered the data from Thompson et al. to only contain responses using the part of the scale between 0 and 5. I have also filtered the words to only contain verbs, adverbs, and adjectives from the Yamato stratum. The Yamato stratum refers to the native lexicon of Japanese. Thompson et al.'s study included both words from the Yamato stratum, as well as Sino-Japanese and foreign words. This study only included Yamato words, and predominantly these were verbs, adverbs and adjectives. Both the data in this study and in Thompson et al. 2020 contains a mix of ideophones and non-ideophones within the Yamato stratum. Finally, ratings from both studies were transformed so that they varied between 0 and 1, to match with the guessing accuracies. The resulting distributions are shown in Figure \@ref(fig:discriminability)

```{r discriminability,fig.cap="Discriminability of different measures"}
oppres%>%
  mutate(method="guesses between words")%>%
  unique()->oppres

guesses_trans%>%
  group_by(word_spec)%>%
  mutate(score=sum(answer=="correct")/sum(answer=="correct"|answer=="incorrect"))%>%
  select(identifier=word_spec,score)%>%
  unique()%>%
  mutate(method="guesses between translations")->transres

ratings%>%
  group_by(identifier)%>%
  mutate(mean_rating=mean(rating))%>%
  mutate(norm_rating=mean_rating/6)%>%
  select(identifier,score=norm_rating)%>%
  unique()%>%
  mutate(method="iconicity ratings")->ratingres

# also compare with ratings from native speakers

japratings <- read_csv("https://osf.io/2praq/download")

japratings%>%
  filter(stratum=="Yamato"|stratum=="Ideophonic")%>%
  filter(category=="verb"|category=="adverb"|category=="adjective"|category=="ideophone")%>%
  filter(rating>=0)%>%
  group_by(wordCode)%>%
  mutate(iconicityM=mean(rating))%>%
  ungroup()%>%
  mutate(task="Thompson et al. 2020")%>%
  mutate(ideophone=ifelse(category=="ideophone","y","n"))%>%
  select(wordCode,iconicityM,rating,task,ideophone)->thompson

thompson%>%
  select(-rating,-ideophone)%>%
  unique()%>%
  mutate(score=iconicityM/5)%>%
  mutate(method="native iconicity ratings\n(Thompson et al. 2020)")%>%
  select(identifier=wordCode,score,method)->japres

everything <- rbind(oppres,transres,ratingres,japres)
#everything$method <- as.factor(everything$method)
#levels(everything$method) <- c("guessing between words (n=131)","guessing between translations (n=77)","iconicity ratings (n=118)")

everything%>%
  ggplot(aes(x=method,y=score))+geom_violin()+theme_classic()+labs(x="Method",y="Guessing accuracy / Iconicity rating")+scale_x_discrete(limits=c("guesses between translations","guesses between words","iconicity ratings","native iconicity ratings\n(Thompson et al. 2020)"))+theme(axis.text.x = element_text(angle=15,vjust=0.6))+scale_y_continuous(breaks=c(0,1))
```

Focusing first on the data from the current study, we can see that a greater spread of measures is provided by the guesses compared to the ratings, and that within the guesses, the method of guessing between words provides a better spread of measures than guessing between translations--both at the very high end of the scale (highly guessable words) and at the very low end of the scale (poorly guessable words). However, if we look at the ratings from native Japanese speakers, these have a pretty equivalent spread to the guesses between words. Their distribution is slightly narrower at the very top end of the scale. However, the data from the current study was chosen from a domain known to be high in iconicity, whereas the data from Thompson et al. was more varied, with proportionally less ideophones. Thus, this could well be simply a reflection of the differences between the two datasets rather than relating to the methods used.

## Agreement

Figure \@ref(fig:comparison) compares the guessing accuracies and mean iconicity ratings, for both ideophones and non-ideophones. The words in the pilot study where participants were guessing between translations were different to the words in the subsequent guessing and rating studies, so here only the results from the later guessing study (where participants guessed between words) are shown. At the top end of the scale, the two measures agree--ideophones score higher than non-ideophones for both measures. However, at the bottom of the scale something strange happens. While in the ratings, the bottom of the scale is dominated by non-ideophones (as expected), in the guesses, the bottom of the scale is actually dominated by *ideophones*. That is, ideophones are simultaneously guessed *better* and *worse* than non-ideophones. We will return to this in the discussion.

```{r comparison,fig.cap="Comparison of guesses and ratings, for ideophones and non-ideophones"}
# get info on ideophones
words <- read_csv("wordlist.csv")
words%>%
  select(form,ideophone)->info

# combine data
comparison <- rbind(oppres,ratingres)

comparison%>%
  mutate(method=str_replace(method,"guess.*","guesses"))%>%
  mutate(method=str_replace(method,".* ratings.*","ratings"))%>%
  group_by(method)%>%
  mutate(z_score=(score-mean(score))/sd(score))%>%
  # only look at words where you have both ratings and guesses
  filter(identifier %in% intersect(oppres$identifier,ratingres$identifier))%>%
  rowwise()%>%
  mutate(form=str_split(identifier,"_")[[1]][1])%>%
  left_join(info)%>%
  unique()%>%
  select(identifier,ideophone,method,z_score,score)->comparison_dat

library(gridExtra)
comparison_dat%>%
  filter(method=="ratings")%>%
  mutate(mean_rating=6*score)%>%
  mutate(word_type=ifelse(ideophone=="y","ideophones","non-ideophones"))%>%
  ggplot(aes(x=word_type,y=mean_rating))+geom_violin()+theme_classic()+ylim(0,6)+labs(x="Word type",y="Mean rating")->plot1

comparison_dat%>%
  filter(method=="guesses")%>%
    mutate(word_type=ifelse(ideophone=="y","ideophones","non-ideophones"))%>%
    ggplot(aes(x=word_type,y=score))+geom_violin()+theme_classic()+ylim(0,1)+labs(x="Word type",y="Guessing accuracy")->plot2

#comparison_dat%>%
 # filter(method=="guesses between translations")%>%
#  filter(score>1/3)%>%
  #  ggplot(aes(x=ideophone,y=score))+geom_violin()+theme_classic()+ylim(0,1)->plot3
grid.arrange(plot1,plot2,ncol=2)
```

Setting aside the strange distribution of guesses for the ideophones, it's notable that both measures suggest that the sensory lexicon of Japanese is for the most part *iconic*, rather than arbitrary. In the guesses, this translates to the majority of the words being guessed slightly *above*, rather than at or below chance. In the ratings, this translates to the words receiving mean ratings higher than zero (the arbitrary point on the scale)--though some of these 'iconic' ratings are likely an overstatement, since all of the words received positive iconicity ratings and yet from the guessing results we can see that many of these were not guessed any differently to chance.

To test how well the measures agree on the iconicity of individual words, iconicity ratings and guessability scores for the same words were transformed to z-scores so that they could be directly compared. Figure \@ref(fig:agreement) plots matching z-scores for the guesses and ratings against eachother, to show the agreement between the two measures. In the figure, ideophones are represented by blue dots, and non-ideophones by red dots.

```{r agreement,fig.cap="Agreement between guesses and ratings"}
comparison_dat%>%
  select(-score)%>%
  pivot_wider(names_from = "method",values_from="z_score")->comparison_dat
comparison_dat%>%
  ggplot(aes(x=guesses,y=ratings,colour=ideophone,label=identifier))+geom_point()+theme_classic()+geom_smooth(method="lm")->plot

plot
# If you want to see which words are which dots -- ggplotly will let you hover over them
#ggplotly(plot)
```

For both ideophones and non-ideophones, there was a strong correlation between the ratings and the guesses. This correspondence was slightly better for the ideophones (r = 0.65, 95% CI [0.44, 0.79], t(43) = 5.57, p < .001) than for the non-ideophones (r = 0.43, 95% CI [0.23, 0.60], t(71) = 4.06, p < .001). To explore this relationship further, we created two linear regression models: one predicting guesses from ratings, ideophone status, and the interaction between these two factors, and a second model predicting ratings from guesses, ideophone status, and the interaction between these two factors. Both models again used the z-scores rather than the raw ratings and guesses.

The output of the first model (predicting guesses from ratings) is shown in Table \@ref(tab:guessesmodel).

<caption> (\#tab:guessesmodel) Linear regression model predicting guesses from ratings, ideophone status, and the interaction between these two factors. </caption>
```{r correlations and first regression}
ids <- comparison_dat%>%filter(ideophone=='y')
#report(cor.test(ids$guesses,ids$ratings))

prosaic <- comparison_dat%>%filter(ideophone=='n')
#report(cor.test(prosaic$guesses,prosaic$ratings))

m1 <- lm(data=comparison_dat,guesses~ratings*ideophone)
#summary(m1)

tab_model(m1,show.ci = FALSE,show.se = TRUE,show.stat = TRUE, dv.labels = c("Guesses"),  CSS = list(
    css.table = 'width: 90%;'
  ))

```

The model confirmed that ratings significantly predict guesses, with higher ratings leading to higher guesses. There was also a main effect of ideophone, and an interaction effect between ideophone and rating. The model is easiest to interpret by plotting the interaction, shown in Figure \@ref(fig:interaction).

```{r interaction,fig.cap="Interaction between ratings and ideophone when predicting guesses"}
ggpredict(m1,c("ratings","ideophone"))%>%plot()
```

The plot shows that higher ratings lead to better guessing accuracy for both ideophones and non-ideophones. The interaction effect appears because in the case of words with *low* iconicity ratings, guessing accuracy for ideophones is relatively poorer than for non-ideophones. At the top of the scale, highly rated ideophones also appear to be guessed slightly better than non-ideophones with comparable ratings. However, the difference here does not appear to be significant as the confidence intervals for the two lines overlap. We will return to this in the discussion.

For comparison, we also created a second model predicting ratings from guesses, shown in Table \@ref(tab:ratingsmodel).

<caption> (\#tab:ratingsmodel) Linear regression model predicting ratings from guesses, ideophone status, and the interaction between these two factors. </caption>
```{r ratingsmodel,fig.cap="Model predicting guesses from ratings and ideophone status"}
m3 <- lm(data=comparison_dat,ratings~guesses*ideophone)

tab_model(m3,show.ci = FALSE,show.se = TRUE,show.stat = TRUE, dv.labels = c("Ratings"),  CSS = list(
    css.table = 'width: 90%;'
  ))
```

The model shows that guesses significantly predict ratings, as does ideophone status, but that there was no interaction between these two predictors. This is shown in Figure \@ref(fig:ratingsinteraction). The lines for ideophones and non-ideophones are parallel, indicating that differences in guesses correspond to differences in ratings *in the same way* for both ideophones and non-ideophones. However, the line for the ideophones is directly *above* the line for the non-ideophones, indicating that ideophones are rated higher in iconicity than non-ideophones--even when guessed at the same accuracies.

```{r ratingsinteraction,fig.cap="Relationship between ideophone status, guessability, and predicted rating"}
ggpredict(m3,c("guesses","ideophone"))%>%plot()
```

Finally, the lower correlation between guesses and ratings obtained for non-ideophones compared to ideophones suggests that participants may not have been as consistent or reliable when rating non-ideophones compared to when rating ideophones. To further investigate this, we calculated the person-total correlation for the rating data [@curran_methods_2016; @motamedi_iconicity_2019], for ideophones and non-ideophones separately. Figure \@ref(fig:ratingconsistency) shows the agreement between raters (expressed as the correlation between each individual rating, and the by-item average) for ideophones and non-ideophones respectively. The dots indicate the mean while the lines indicate 95% confidence intervals. Again, since these ratings were from non-Japanese speaking participants, I have also added data from native Japanese speaking participants from Thompson et al. (2020) as a comparison.

```{r bootstrap function, eval=FALSE}
info <- read_csv("wordlist.csv")%>%select(form,ideophone)
# my ratings from English people
ratings%>%
  group_by(identifier)%>%
  mutate(mean_rating=mean(rating))%>%
  select(iconicityM=mean_rating,rating,prolificID)%>%
  mutate(task="current study")%>%
  mutate(form=str_split(identifier,"_")[[1]][1])%>%
  left_join(info,by="form")%>%
  ungroup()%>%
  unique()%>%
  select(-form,-identifier,-prolificID)->ratingdat

# Thompson's ratings from Japanese people

thompson%>%
  select(iconicityM,rating,task,ideophone)->thompson

datasets <- list(ratingdat,thompson)

# code from Motamedi et al. 2019

R <- 5000

# Bootstrap function, calculating the correlation coefficient for each bootstrapped sample
bootCor <- function(data, i){
  d <- data[i,]
  rDf <- correlate(d %>% select(-task))
  return(rDf[[2,2]])
}

# Split the data by halves of the rating scale, apply the above bootstrap function, and extract confidence intervals
corRatings <- function(data){

  # Separate the data into ideophones and non-ideophones
   negData <- data %>% filter(ideophone=="n")%>%select(-ideophone)
   posData <- data %>% filter(ideophone=="y")%>%select(-ideophone)

  #negData <- data %>% filter(rating<0)
  #posData <- data %>% filter(rating>0)

  # Bootstrap the correlation between each negative rating, and the by-item average
  negBoot <- boot(negData, bootCor, R=R)
  negCI <- boot.ci(negBoot, type="bca")
  rNeg <- negBoot$t0
  lowerNeg <- negCI$bca[[4]]
  upperNeg <- negCI$bca[[5]]

  # Bootstrap the correlation between each positive rating, and the by-item average
  posBoot <- boot(posData, bootCor, R=R)
  rPos <- posBoot$t0
  posCI <- boot.ci(posBoot, type="bca")
  lowerPos <- posCI$bca[[4]]
  upperPos <- posCI$bca[[5]]

  return(list(list(lowerPos,upperPos,rPos), list(lowerNeg,upperNeg,rNeg)))
}
```

```{r run bootstrap, cache=TRUE, message=FALSE, warning=FALSE, eval=FALSE}

# Initialize an empty dataframe to store values
cis <- data.frame(name=character(), sign=character(), r=numeric(), lower=numeric(), upper=numeric(), stringsAsFactors=FALSE)

# Iterate over datasets
for(dataset in datasets) {

  # Track the name of the current dataset
  name <- dataset$task[1]

  # For each dataset, apply the function corRatings described above
  c(c(posLower, posUpper, posR), c(negLower, negUpper, negR)) %<-% corRatings(dataset)

  # Append the results to the dataframe
  cis[nrow(cis) + 1,] = list(name, 'ideophone', posR, posLower, posUpper)
  cis[nrow(cis) + 1,] = list(name, 'non-ideophone', negR, negLower, negUpper)
}
```

```{r make person-total graph, eval=FALSE}
cis %>% 
  ggplot(aes(x=name,
             y=r,
             ymin=lower,
             ymax=upper,
             color=sign)) +
  geom_point(position=position_dodge(0.1)) +
  geom_errorbar(position=position_dodge(0.1),
                width=0.1) + 
  coord_flip() +ylim(0,0.6)+theme_classic()+labs(y="Correlation (r)",x="")->plot
plot
```

```{r ratingconsistency,fig.cap="Consistency between participants for iconicity ratings of ideophones versus non-ideophones",out.width="70%"}
knitr::include_graphics("images/persontotal.svg")
```

In both studies, participants appear to be more consistent with eachother when rating ideophones than when rating non-ideophones, though for Thompson et al. the overlap of the confidence intervals indicates that the difference was not significant. There does not appear to be any difference in the consistency of ratings *between* the English and the Japanese speakers, as both the ideophone lines and the non-ideophone lines overlap between the two groups.

# Discussion

## Relationship between ratings, guesses, ideophones, and iconicity {#maindiscussion}

For both ideophones and non-ideophones, we found that the guesses and ratings from non-speakers were strongly correlated in the *same way*. This suggests that the two measures are indeed tapping into *something* in common, which we suggest are form-meaning associations. It's notable that these associations are found in both ideophones *and* non-ideophones (even if they are more common in the former), and that there are also ideophones that participants had no strong associations with--highlighting that there is no straightforward relationship between ideophones and iconicity; variable levels of iconicity can be found in both ideophones and prosaic words [see also @dingemanse_what_2016; @brown_phonetic_1955; @kunihira_effects_1971].

However, ideophones were consistently rated *higher* in iconicity than non-ideophones—even when guessed at the same accuracies. We believe this is due to the majority of ideophones in the dataset being reduplicated. The two lowest rated ideophones–*sappari* and *syippori*–were among the few in the data that do not use a reduplicated template. Previous work has found a relationship between iconiticity ratings and structural markedness (Dingemanse and Thompson 2020). Ordinarily when we use words, the form of the words is not important--only their content. However, when iconicity is involved (and also funniness, as this paper found) the form of the words *is* important, and structural markedness may serve as a metacommunicative cue to signal this. The authors hypothesise that “Structural markedness confers a selective advantage on words intended to be iconic… as their recognisability would make them more fit to survive processes of cultural transmission in which the recognition of such intentions is functionally important” (Dingemanse and Thompson 2020: 218). The results from the rating task in this study suggest that structural markedness (in this case, reduplication) does indeed lead to the perception of iconicity. Interestingly, however, it does not seem to confer any advantage--over and above that provided by associations between form and meaning--in the guessing task. What the ratings seem to be picking up on is both form-meaning associations *and* structural markedness. If they were only picking up on structural markedness, then we would not expect the ratings to vary with the guesses in the same way for both ideophones and non-ideophones. However, if they were only picking up on form-meaning associations (like the guesses seem to), then we would not expect ideophones to consistently receive higher iconicity ratings, even when guessed at the same accuracies.

While ideophones and non-ideophones with high iconicity ratings were generally guessed equally well, there was an interaction effect such that ideophones with low iconicity ratings were guessed *worse* than non-ideophones with comparable ratings. Low iconicity ratings in non-ideophones generally correspond to chance guessing accuracy--reflecting a lack of associations--whereas equivalent ratings in ideophones correspond to *below chance* guessing accuracy--reflecting *negative associations* masked in the rating results by the tendency to inflate ratings for ideophones. The result highlights the subjective nature of form-meaning associations, and that by taking above-chance guessing accuracy as a measure of iconicity we are only picking up on those associations that happen to correspond--and crucially not to conflict--between (in this case) English and Japanese speakers.

Poor guessing accuracies could be explained by conflicting, non-resemblance based associations. For example, one person commented that *zarazara* as a word for ‘ROUGH’ sounds wrong to them because they associate the word *zara* with the clothing store ZARA, and clothes are soft. These could be masking either a lack of resemblance between form and meaning, or a resemblance between form and meaning that is ignored in the face of the conflicting association. Of course, conversely one could argue that high guessing accuracies could then *also* be explained by non-resemblance based associations. Fortunately, the chances of English speakers having the *same* form-meaning association as Japanese speakers based on something random (like the name of a clothing store) should be much smaller than the chances of them having a *different* association. Thus, if they do exist, we predict that the majority of non-resemblance based associations should be reflected in poorer rather than higher guessing accuracies.

That the poor guessing results also corresponded to lower ratings suggests that these ratings also likely reflect form-meaning *associations*, rather than form-meaning *resemblances* specifically. This is despite the instructions in the task specifically asking about resemblances. That participants in rating studies do not distinguish iconicity from indexicality or other kinds of associations is hardly surprising, given these are distinctions even seasoned semioticians can find a struggle. Nor is it necessarily problematic; whether the association is based on resemblance or other factors, the end result it the same--a bias. However, it is something researchers should be aware of, because it means that decisions about *whom* to collect iconicity measurements from are very important, since associations are much more dependent on world experience than resemblances [see also @motamedi_iconicity_2019: 17].

Even resemblance itself is not entirely objective, though this is often an assumption of rating and guessing studies. In the beginning of this study, we defined iconicity as involving *perceived* resemblances, reflecting a conception of iconicity not as an objective property of signs, but as a subjective process involving construal (Occhino et al. 2017; Occhino, Anible, and Morford 2020). Occhino et al. [-@occhino_role_2020: 117] provide an excellent illustration of this in the ASL sign for dance, which involves an inverted V-handshape. On its own, the meaning of this sign is unlikely to be transparent to non-signers. However, a signer will recognise the inverted-V handshape from a network of signs involving the construal of a pair of legs mapped to a pair of extended fingers--such as in the sign STAND, which is likely to be transparent to non-signers. Thus, iconicity can be both language-internal (as in the sign for DANCE) and/or language-external (as in the sign for STAND). However, guessing studies and rating tasks with non-speakers will only pick up on examples of language-external iconicity, while language-internal iconicity falls under the radar.

It is even possible that different construals could lead to non-speakers having exactly the *opposite* iconic mapping to the mapping in the language under study. This is perhaps more likely in spoken than in signed languages, particularly where phoneme inventories are small. The most famous example comes from vowel-size sound symbolism. The most common mapping relates high vowels--like /i/--to smallness, and low vowels--like /a/--to largeness [@ultan_size-sound_1978]. However, a few languages also show the *reverse* mapping--two examples are Korean and Bahnar [@shinohara_cross-linguistic_2010; @difflothibig_1994]. Different construals make it possible for both mappings to be perceived as iconic to speakers, and in fact this is likely since the reverse mappings are actually reported in ideophones--which speakers generally perceive as iconic [@thompson_iconicity_2020]. For example, a construal of the change from /i/ to /a/ as involving an *expansion* of the space in the oral cavity could lead to the /i/-small, /a/-large mapping. However, one could also construe the same event as involving the *contraction* of the space occupied by the tongue, resulting in an /i/-large, /a/-small mapping. Interestingly, despite the conflicting mapping in their own language, when evaluating non-words Korean speakers still show a preference for the /i/-small, /a/-big mapping [@shinohara_cross-linguistic_2010]. This is encouraging as it suggests that when judging unfamiliar stimuli, conflicting mappings in the participants own languages are unlikely to hide iconic effects in cases where the naturalness of the mapping is very strong [as in the /i/-small, /a/-big example; @ultan_size-sound_1978]

Finally, the comparison between guesses and ratings highlights a bias in the design of the rating task, as all the words in the data were in the end rated as "slightly" iconic (even by non-speakers), whereas the guessing results show that a good number of these were not guessed any better than chance. This is probably an artefact of the design of the rating task, in which "arbitrary" is only 1 of the 7 or 10 points on the scale--the rest indicating varying degrees of form-meaning resemblance. This is not so problematic, as the ratings still correlate with guessing accuracy, indicating that the relative differences in iconicity still hold. However, it highlights that interpretations of (particularly low) ratings as reflections of iconicity should be taken with a grain of salt.

To sum up, by directly comparing iconicity ratings and guessing accuracies for both ideophones and non-ideophones, we are able to better understand how these measures relate to each other and to iconicity. Differences between iconicity ratings of ideophones and non-ideophones--even when guessability is the same--highlight the role of structural markedness in enhancing perceived iconicity. Consistencies between guesses and ratings within these word types reassure us that, despite this, form-meaning association biases play a large role in explaining each measure. The unexpected result of ideophones also being poorly guessed reminds us that these biases are just that--subjective--and thus, while good guessing accuracies can be interpreted as positive evidence of language-external iconicity, average or poor guessing accuracies *cannot* be interpreted as negative evidence of iconicity of either kind (language-internal or external). Similarly, while high ratings are likely to be a good indication of iconicity, researchers should be cautious of taking lower ratings indicating "slight" iconicity at face value.

## Towards a synthesis of measures

Given the limitations of each measure discussed above, for a full picture of iconicity in the lexicon, a synthesis of measures is recommended. Iconicity ratings from native speakers can tell us which mappings are meaningful to them, while comparisons with guessability for non-speakers can establish which of these mappings are likely to be meaningful on their own, versus which *become* meaningful through experience with the rest of the lexicon (language-external versus language-internal iconicity). @occhino_role_2020 found differential effects of these two types of mappings in sign processing by signers of different proficiencies. They found that both types of iconicity were helpful to signers of a lower proficiency, but that for highly proficient signers only the most pervasive, language-external mappings made a difference to processing. Guessing and rating comparisons could also be useful to explore the influence of structural markedness on iconicity effects. Since structural markedness appears to boost ratings but not guessability, the two measures could be used together to tease apart the influence of structural markedness versus form-meaning resemblances in driving iconic effects. We tend to assume that iconic effects are driven by form-meaning resemblances, but since these often go together with structural markedness it would be useful to know the relative contribution of each factor in different situations and tasks. Since structural markedness is also subjective, the choice of participants used in the rating task should be theoretically justified and matched to the phenomenon the measures will be used to study. For example, if the measures will be used to study language processing in adults, then adult native speakers should be used. Finally, having guesses alongside ratings would allow researchers to make better decisions about the cut-off point between "high" and "low" iconicity ratings, as these could be motivated by correlations with guessing accuracy, rather than e.g. arbitrarily dividing the scale at the half-way point, or using percentiles tied to particular datasets.

Guesses and ratings could also be used to inform results from descriptive or data-driven measures, and vice-versa. For example, the psychological reality and relative *strength* of form-meaning mappings described in lexicons could be tested using guessing or rating tasks with nonwords [e.g. @kwon_empirically_2017]. Similarly, descriptive (semiotic) analysis, along with cross-linguistic comparisons where possible could be used to understand and explain why some mappings are stronger or more universal than others. Conversely, behavioural measures could be used to tease apart some of the possible explanations for cross-linguistic biases. The two main contenders for explaining these biases are form-meaning associations or communicative pressures [@blasi_soundmeaning_2016]. Since communicative pressures are unlikely to play a role in tasks where participants are simply judging or choosing words, behavioural measures could be used to distinguish these two hypotheses, thus allowing us to better understand the mechanisms behind results in these cross-linguistic studies.

## Methodological improvements and evaluation

We also sought to evaluate different rating and guessing paradigms, and were able to make some methodological improvements--particularly to the guessing design. We contrasted two different guessing paradigms--one where participants are given a word and have to match it to the correct meaning from two translations, and another where participants are given a meaning and have to match it to the correct word from two words. Content-wise, choosing between words is more comparable to the design of a rating task, as both give the meaning first and involve only one English translation. This is important as the use of translations leads to several complications in the experiment design. First, English-speaking participants can be expected to have more associations with English words than with unknown Japanese words, which could make the task more sensitive to the particular translations chosen. In addition, care has to be taken when choosing foils as well, as they should preferably be from the same semantic domain, of a similar length of characters, and not synonyms or antonyms of the correct translation. This makes the guessing between translations design more difficult to use, particularly in small semantic domains (e.g. taste). In contrast, a task in which participants guess between words is much easier to operationalise. This design can be easily adopted to any semantic domain or any kind of data, and the foils can be chosen either randomly from the other trials or selected based on specific criteria. In our case we chose foils that were phonologically as distinct as possible from the word being tested. The first reason for this was theoretical: in a task designed to pick up on form-meaning resemblance, words that sound very different should not be suited to that meaning, enhancing the effect of iconicity. The second was practical: our stimuli had artificially flat intonations, which has been shown to decrease performance in guessing studies [@kunihira_effects_1971; @dingemanse_what_2016]. By creating opposite sounding words, we tried to increase performance in the guessing task despite the degraded stimuli.

When comparing results from the two designs, choosing between words is again the more favourable of the two. First, as expected changing the translation or foil used led to less inconsistent results when choosing between words compared to when choosing between translations. Second, the range of guessing scores is much wider when choosing between words compared to choosing between translations, with more words guessed at high accuracy levels, and fewer words around chance level. This is especially true when the foils used are maximally phonologically distinct. However, for datasets that are relatively higher in iconicity to begin with--e.g. gestures or hand signs--using random foils will likely already produce good results. The better results in the choosing between words design can be easily explained, as the task was comparatively easier than in the choosing between translations design, where participants were restricted to choosing between two similar options (non-antonyms from the same semantic domain). The options in the choosing between words design are more distinct--even maximally so. In sum, the choosing between words design is both more robust, more sensitive to iconicity, and more discriminating between lesser and greater amounts of iconicity, so this is the design that we recommend and that we have implemented in `icotools`.

We also compared our iconicity ratings from non-speakers with iconicity ratings from native speakers in @thompson_iconicity_2020. We found that, although using non-speakers resulted in a lesser spread of measures (suggesting that native speakers are more confident in giving high and low ratings than non-native speakers), when evaluating the agreement between raters, ratings from non-speakers were just as reliable as ratings from native speakers--as well as being fairly robust to different choices of translation. Ratings from non-speakers were more reliable for ideophones than for non-ideophones--but this is not to say that the ratings for non-ideophones were unreliable. Rather, the ratings for ideophones were *particularly* reliable, probably because these words were more likely to be iconic in the first place, and so raters were more likely to have stronger intuitions about these words. The same pattern was seen in the ratings from native speakers, although it did not reach statistical significance. Since both types of ratings are fairly reliable, our recommendation would be to use whichever design is most theoretically justified (see discussion in Section \@ref(maindiscussion)).

## Towards a reproducible workflow

Finally, with `icotools` we introduce a reproducible workflow for conducting rating and guessing experiments. This will make it easier for researchers to run these tasks, while enhancing comparability between future studies. Researchers can use the same paradigms to confirm current results, ask new questions, and run new analyses that build on existing findings. For example, this study has examined iconicity in the sensory vocabulary of Japanese, and found that the majority of words tested were actually guessed slightly above chance. With `icotools`, future researchers could run the exact same guessing experiment with different languages and in different semantic domains, to establish whether this is also true in other languages, and in other areas of the lexicon.

# Conclusions

This study has asked how we can make existing measures of iconicity even better, by critically evaluating and comparing two of the most promising behavioural measures of iconicity--iconicity ratings and guessing tasks. In comparing the two measures, we were able to get a better sense of the relative strengths and weaknesses of each. Our main finding is that the two measures are more informative when used together than when used in isolation. In isolation, it is difficult to determine the degree to which high iconicity ratings are driven by form-meaning associations versus structural markedness, and to have an objective sense of which ratings are "low" or "high". In isolation, guesses provide only a narrow window into iconicity of a particular kind--strong, language-external associations. However, in *combination* ratings and guesses together can provide a picture of iconicity at different levels (both language internal and external), and in different degrees (low and high), while also uncovering how perceptions of iconicity are driven by both form-meaning associations and structural markedness. We have also made some methodological improvements to the guessing paradigm, improving on the robustness, sensitivity and discriminability of previous approaches. Finally, we introduce a reproducible workflow for creating rating and guessing tasks in the form of the Python package `icotools` (https://pypi.org/project/icotools/), so that future studies will be able to use these measures to build on current findings as well as asking new questions about what iconicity does in language, and how it does it.

# References

### 2022-01-26 paper.Rmd
done
working on paper

@@
 Iconicity in language is receiving increased attention from many fields, but our understanding of the roles of iconicity in language is only as good as the measures we use to quantify it.
-We conducted iconicity rating and guessing experiments with 300 Japanese ideophones and prosaic words with similar meanings, (e.g.
-*fuwafuwa* ‘fluffy’, *jawarakai* ‘soft’), and found that the two measures together presented a more complete picture of iconicity than either alone.
-For both groups of words, ratings and guesses were positively correlated—emphasising that both pick up on the same form-meaning associations.
+We conducted iconicity rating and guessing experiments with 304 Japanese ideophones and prosaic words with sensory meanings, e.g.
+*fuwafuwa* ‘fluffy’, *jawarakai* ‘soft’.
+For both word groups, ratings and guesses were positively correlated—suggesting the two measures pick up on the same associations.
 Ideophones were consistently associated with higher iconicity ratings, but not higher guessing accuracy.
-We suggest that the structural markedness of ideophones enhances their perceived iconicity in the rating task, but does not provide any advantage (over and above that provided by form-meaning associations) in the guessing task.
+We suggest that the structural markedness of ideophones enhances their perceived iconicity in the rating task, but does not provide any advantage (over and above form-meaning associations) in the guessing task.
 Thus, guesses and ratings could be used together to tease apart the relative contribution of structural markedness to iconic effects.
-Some ideophones were also guessed very poorly, highlighting that construals of iconicity can be language-specific.
-Combining guesses with ratings from native speakers is thus recommended for a fuller picture of language-external and language-internal mappings (Occhino et al.
-2017).
-
-We also critically evaluated different rating and guessing paradigms, and introduce a new guessing paradigm that improves on the robustness, sensitivity and discriminability of previous approaches.
-Finally, we introduce a reproducible workflow for creating rating and guessing experiments in the form of a Python package, `icotools`, which we hope will improve comparability between future studies, enabling others to confirm and build on current findings, and to ask new questions about the roles of iconicity in language.
+Some ideophones were also poorly guessed, highlighting that construals of iconicity can be language-specific.
+Finally, we present some methodological contributions, including a new guessing paradigm that improves on the robustness, sensitivity and discriminability of previous approaches, and a reproducible workflow for creating rating and guessing experiments with a Python package, `icotools`, which we hope will improve comparability between future studies.
 
@@
 However, they *do* rely on the existence of translation equivalents in multiple languages for the words under study.
-This can pose a particular challenge for highly iconic words, as these tend to also have highly specific meanings (@lupyan_language_2018; @akita_toward_2012).
-Thus, such approaches are less likely to be helpful for those with existing data for which iconicity measures are required.
+This can pose a particular challenge for highly iconic words, as these often also have highly specific meanings (@lupyan_language_2018; @akita_toward_2012).
+Thus, these approaches are less likely to be helpful for those with *specific* words for which iconicity measures are required.
 
@@
 @vinson_british_2008; @perry_iconicity_2015; @winter_which_2017; @occhino_iconicity_2017; @thompson_iconicity_2020; @punselie_iconicity_2020].
-Measurements from these studies are shown to correlate in meaningful ways with factors related to iconicity--e.g.
-encoding of sensory information [@winter_which_2017], semantic neighbourhood density [@sidhu_lonely_2018], age of acquisition [@vinson_british_2008; @perry_iconicity_2015], facilitated processing [@thompson_link_2009; @occhino_role_2020], word class [@perry_iconicity_2015; @thompson_iconicity_2020], semantic domain [@punselie_iconicity_2020], funniness and structural markedness [@dingemanse_playful_2020].
-However, ratings given are strongly influenced by the linguistic experience of participants (@occhino_iconicity_2017; @sevcikova_sehyr_perceived_2019), which could make comparing measurements between studies difficult.
+Measurements from these studies have been found to correlate in meaningful ways with factors related to iconicity--e.g.
+encoding of sensory information [@winter_which_2017], semantic domains [@punselie_iconicity_2020], semantic neighbourhood density [@sidhu_lonely_2018], word class [@perry_iconicity_2015; @thompson_iconicity_2020], age of acquisition [@vinson_british_2008; @perry_iconicity_2015], facilitated processing [@thompson_link_2009; @occhino_role_2020], funniness and structural markedness [@dingemanse_playful_2020].
+However, ratings given are influenced by the linguistic experience of participants (@occhino_iconicity_2017; @sevcikova_sehyr_perceived_2019), so some care is needed to ensure measures are taken from appropriate participant groups.
 
@@
 
-Despite these complications, behavioural measures of iconicity are particularly appealing for four reasons: (1) they can be applied to any kind of dataset, (2) they are highly scalable, being particularly amenable to online, crowd-sourced data collection, (3) they are tweakable, meaning that we can experiment with different experimental designs to figure out exactly what these measures are telling us, and (4) they are amenable to standardisation, making them a good option for reproducibility.
-In fact, they are the only measures of iconicity that we know of to combine all these things.
+While results from behavioural experiments often require some untangling, we believe that they are particularly valuable sources of iconicity measures for four reasons: (1) they can be applied to any kind of dataset, (2) they are highly scalable, being particularly amenable to online, crowd-sourced data collection, (3) they are tweakable, meaning that we can experiment with different experimental designs to figure out exactly what these measures are telling us, and (4) they are amenable to standardisation, making them a good option for reproducibility.
+In fact, they are the *only* measures of iconicity that we know of to combine all these things.
 Moreover, that the measures correlate with each other and with a variety of other meaningful phenomena speaks to their validity.
 
-In this study, we seek to better understand what these guesses and ratings are measuring by comparing and contrasting iconicity ratings and guesses for 300 Japanese words from the sensory vocabulary of Japanese.
-Sensory language was chosen as this is a domain high in iconicity, where iconicity offers clear advantages [@winter_which_2017].
+In this study, we seek to further our understanding of these measures and how they can be useful by comparing and contrasting iconicity ratings and guesses for 304 Japanese words from the sensory vocabulary of Japanese.
+Sensory language was chosen as this is a domain high in iconicity, and where iconicity offers clear advantages [@winter_which_2017].
 The data contained a mix of ideophones--depictive, eye-catching words like *fuwafuwa* 'soft' and *pikapika* 'sparkly' that "invite and afford the construal of iconic mappings between form and meaning" [@akita_ideophone_2019: 18]--along with prosaic lexical items, like *yawai* 'soft' and *hikaru* 'shine', which are not necessarily expected to be lacking in iconicity--especially given their sensory meanings--but which are less obvious about it.
@@
 
-To investigate how to get the most out of each measure, we compare and contrast different rating and guessing paradigms, and in particular introduce a new guessing paradigm that improves on the robustness, discriminability and sensitivity of previous approaches.
+To discover how to get the most out of each measure, we compare and contrast different rating and guessing paradigms, and in particular introduce a new guessing paradigm that improves on the robustness, discriminability and sensitivity of previous approaches.
 Finally, to promote the use of these new measures, we introduce a reproducible workflow for automatically generating rating and guessing experiments in a standardised format, via a python package `icotools` [(https://pypi.org/project/icotools/)](https://pypi.org/project/icotools/), with support for a variety of stimulus formats (audio, video, and images).
-This will make the collection of behavioural based iconicity measures quicker, easier, and more comparable between different studies.
-
-# Method
+This will make the collection of behavioural based iconicity measures quicker, easier, and more comparable between future studies.
+
+# Methods
+
+The data from the study, as well as the code used to produce the experiments and analyses can be found on the Open Science Framework, at https://osf.io/j57uc/?view_only=d59ffde4bc42467fafb71a904bef8d14.
 
@@
 
-The stimuli were 300 Japanese words from the domain of sensory perception, including both ideophones and prosaic lexical items.
+The stimuli were 304 Japanese words from the domain of sensory perception, including both ideophones and prosaic lexical items.
 For all tasks, the words were presented to participants as audio files.
@@
 Expressive prosody can enhance performance in guessing tasks [@kunihira_effects_1971; @dingemanse_what_2016], and so using a flat intonation was seen as the best way to ensure comparisons between the words were fair and not influenced by the prosody in a particular recording.
-^[We also considered synthesising all the words to have a marked intonation.
-However, different word lengths would make changes in pitch more dramatic in shorter words compared to longer words, affecting words of different lengths unequally.].
+We also considered synthesising all the words to have a marked intonation.
+However, different word lengths would make changes in pitch more dramatic in shorter words compared to longer words, affecting words of different lengths unequally.
 While flat, synthetic voices may be the best option for comparability, they are not a natural reflection of real-world experiences with iconicity--which involve not only segments but also prosody and even multimodal cues (e.g.
@@
 The participants were monolingual English speakers residing in England, with no prior knowledge of Japanese.
-Although rating tasks are often done with native speakers, we used English speakers in order to make the results as comparable as possible between the guessing and the rating tasks.
-
-The words were split across 12 different experiments, in such a way that each experiment had a balance of words that were expected to be iconic, versus words that were not expected to be iconic.
+Although rating tasks are often conducted with native speakers, we used English speakers in this study for two reasons: first, to make the results as comparable as possible between the guessing and rating tasks; and second, because our data contained a mix of Standard Japanese and non-standard Japanese words, and we were concerned that using Standard Japanese speakers would lead to a bias towards standard words [@occhino_iconicity_2017].
+
+The words were split across 11 different experiments, in such a way that each experiment had a balance of words that were expected to be iconic, versus words that were not expected to be iconic.
 In addition, two 'practice words' and three 'control words' were included in every experiment.
@@
 
-For the rating task, no data was excluded.
-There were some task descriptions where participants claimed to be rating based on whether the Japanese word sounded similar to its English translation, rather than whether they thought it was an appropriate word for that meaning.
-However, as their actual ratings did not seem to reflect this and were similar to those of other participants, their responses were not excluded.
-The vast majority of participants' task descriptions indicated that they had understood the task very well.
-
-For the first version of the guessing task, in which participants had to match a given form to its correct meaning, data from three participants was excluded.
+For the pilot version of the guessing task, in which participants had to match a given form to its correct meaning, data from 3 out of 132 participants was excluded.
 In one case, the participant indicated that they were choosing the translations based on whether they sounded similar to the Japanese word (rather than based on their meaning).
 In the other two cases, the participants did not provide a task description and performed poorly on the control items, so the data was excluded as it was not clear that they were paying attention/understood the task correctly.
-In the new version of the guessing task, in which participants had to match a given meaning to its correct form, no data was excluded.
-Participants' task descriptions indicated that they had understood the task very well and they also performed well on the control items.
-
-```{r identify and exclude outlying participants}
+In the new version of the guessing task, in which participants had to match a given meaning to its correct form, data from 3 out of 332 participants was excluded.
+In all three cases, the participants performed poorly on the control items and either did not provide a task description, or their task descriptions were irrelevant (they commented that the task was 'interesting' or 'difficult' instead of describing what they were doing in the task).
+[COME BACK TO THIS POINT IT'S GOOD THE NEW GUESSING TASK PEOPLE SEEM TO UNDERSTAND IT BETTER]
+
+```{r preprocessing guesses}
 # for guessing between translations
@@
   filter(word %in% control_items)%>%
-  select(Prolific.ID,word,answer,time_taken,Task.Description)%>%
+  select(Prolific.ID,word,answer,Task.Description)%>%
   group_by(Prolific.ID)%>%
@@
   select(-word,-answer)%>%
-  unique()%>%
-  # also look at whether they were particularly slow or fast to do the experiment
-  mutate(deviation_timetaken=time_taken-mean(.$time_taken))%>%
-  mutate(std_deviation=sd(.$time_taken))->examine_participants
+  unique()->examine_participants
 
@@
 # for guessing between words
-guesses_words<-read.csv('responses-guessingwords.csv')
+guesses_words<-read_csv('responses-guessingwords.csv')
 control_items <- c("pyoNpyoN","katai","hisohiso")
@@
 guesses_words%>%
-  filter(word %in% control_items)%>%
-  select(prolific_ID,word,answer,TimeTaken,TaskDesc)%>%
-  group_by(prolific_ID)%>%
+  filter(form %in% control_items)%>%
+  select(prolificID,form,answer,taskdesc)%>%
+  group_by(prolificID)%>%
   mutate(check_score=sum(answer=='correct')/sum(answer=='incorrect'|answer=='correct'))%>%
-  select(-word,-answer)%>%
-  unique()%>%
-  # also look at whether they were particularly slow or fast to do the experiment
-  mutate(deviation_timetaken=TimeTaken-mean(.$TimeTaken))%>%
-  mutate(std_deviation=sd(.$TimeTaken))->examine_participants
-
+  select(-form,-answer)%>%
+  unique()->examine_participants
+
+distribution_controlguesses <- ggplot(data=examine_participants,aes(x=check_score))+geom_histogram(bins=3)
+
+# results from the following participants were excluded
+exclude_participants <- c("5ad4d7de546e150001b695b0","5be44162fa676700011d80d7","613da3ad46281fe6d621a413")
+
+guesses_words <- guesses_words%>%filter(!(prolificID %in% exclude_participants))
+```
+
+For the rating task, data from 5 out of 225 participants was excluded.
+For the ratings, as well as looking at task descriptions and performance on the control items, we calculated the person-total correlation for each participant @curran_methods_2016.
+The person-total correlation is the correlation between an individual participant's ratings, and the mean ratings from every other participant.
+It provides a measure of how well a participant's responses agree with those of other participants in the task.
+The criteria for exclusion was two or more of either (a) strange or lacking task descriptions, (b) very low ratings for control items, or (c) low person-total correlations (<.2^[We chose .2 as the cut off point because it corresponded with a discontinuity in the lower end of the distribution of person-total correlations, see Figure 1 in the online Supplementary Material]).
+Criteria (a) was used for 4 exclusions.
+In two cases, the participants indicated that they were rating the words according to how much they sounded like their English translations, rather than how well they resembled their meanings.
+Criteria (b) was used in 3 exclusions, and criteria (c) was used in 4 exclusions.
+
+[OF THE THREE VERSIONS OF THE TASK, I THINK MATCHING THE WORD IS INTUITIVELY EASIEST FOR PARTICIPANTS TO UNDERSAND]
+[I LOOKED AT REACTION TIMES AS WELL BUT THERE WERE ONLY TWO TRUE OUTLIERS IN THE WHOLE DATASET AND THEY WERE FOR PRACTICE ITEMS SO I COULDN'T BE BOTHERED DOING IT]
+
+```{r preprocessing ratings}
 # for ratings
@@
 
+# control performance and task descriptions
 ratings%>%
-  filter(form=="pyoNpyoN"|form=="katai"|form=="hisohiso"|form=="yoroyoro"|form=="fuwafuwa")%>%
-  select(experiment,prolificID,form,rating,taskdesc)->ratings_examine
-
-#ratings_examine%>%kable()%>%kable_styling()
+  filter(form %in% control_items)%>%
+  select(prolificID,form,rating,taskdesc)%>%
+  group_by(prolificID)%>%
+  mutate(mean_rating=mean(rating))%>%
+  select(-form,-rating)%>%
+  unique()->examine_participants
+
+distribution_controlratings <- ggplot(data=examine_participants,aes(x=mean_rating))+geom_histogram()+scale_x_continuous(n.breaks=20)
+
+# person-total correlations
+participants <- unique(ratings$prolificID)
+correlations <- c()
+for(p in participants){
+  # get the mean ratings of everyone else
+  othersratings <- ratings%>%filter(prolificID!=p)%>%
+    group_by(identifier)%>%
+    mutate(mean_rating=mean(rating))%>%
+    select(identifier,mean_rating)%>%
+    unique()
+
+  # get the participants ratings
+  participantratings <- ratings%>%filter(prolificID==p)%>%select(identifier,rating)
+
+  # join them and compute the correlation
+  compare <- left_join(participantratings,othersratings,by="identifier")
+  corr <- cor(compare$rating,compare$mean_rating,use="pairwise.complete.obs")
+
+  correlations <- c(correlations,corr)
+}
+
+persontotals <- data.frame(participants,correlations)%>%rename(prolificID=participants,pt_corr=correlations)
+
+persontotal_dist <- ggplot(data=persontotals,aes(x=pt_corr))+geom_histogram()+scale_x_continuous(n.breaks=8)
+
+examine_participants <- left_join(examine_participants,persontotals,by="prolificID")
+
+exclude_participants <- c("60ccf2e72ef0587d5cc4e2cd","60ce01c71f2eaca4a5050416","5fd64479bf40a251701159d6","5c8026f0f399120012fa4238","5ca73fe6bcdcc2001291822d")
+
+ratings <- ratings%>%
+  filter(!(prolificID %in% exclude_participants))
 ```
@@
 Prolific's prescreening features were used to ensure that participants who had already participated in one experiment (regardless of whether it was a rating or guessing task) could not participate in any subsequent experiments.
-For each word, we collected 30 guesses and 30 ratings from different participants.
-
-## Guessing experiments -- guessing between translations
-
-In the first guessing experiments, participants were presented with a Japanese word and asked to guess its meaning from a choice of two possible translations.
+Excluding the practice and control items (which every participant guessed and rated), in the final dataset we had a median of 40 guesses per word (range: 15-129) in the pilot guessing experiment; a median of 30 guesses (range: 29-60) per word for the second guessing experiment; and a median of 15 ratings (range: 14-58) per word for the rating task (@motamedi_iconicity_2019 suggest a benchmark of 10 ratings per word is sufficient).
+
+```{r final data count}
+ratings%>%
+  select(identifier,prolificID)%>%
+  unique()%>%
+  group_by(identifier)%>%
+  count()%>%
+  filter(n<200)->no_ratings
+
+#median(no_ratings$n)
+
+guesses_words%>%
+  select(identifier,prolificID)%>%
+  unique()%>%
+  group_by(identifier)%>%
+  count()%>%
+  filter(n<200)->guess1
+
+# median(guess1$n)
+
+guesses_trans%>%
+  mutate(identifier=paste(word,concept))%>%
+  select(identifier,Prolific.ID)%>%
+  unique()%>%
+  group_by(identifier)%>%
+  count()%>%
+  filter(n<200)->guess2
+
+#median(guess2$n)  
+```
+
+## Pilot guessing experiments: guessing between translations
+
+We piloted some guessing experiments following previous studies [e.g.
+@dingemanse_what_2016], in which participants were presented with a Japanese word and asked to guess its meaning from a choice of two possible translations.
 Some of the ideophones in the data had very specific meanings, which were difficult to capture in a single English word.
@@
 
-While we could not do anything about the sound of the words (other than using multiple translations), we realised that we could eliminate at least some of the complications caused by other properties of the words if we flipped the design of the guessing experiments on its head, so that instead of choosing the correct English meaning for a given Japanese word, participants had to choose the correct Japanese word for a given English meaning.
+While we could not do anything about the sound of the words (other than using multiple translations), we realised that we could eliminate at least some of the complications caused by other properties of the words if we flipped the design of the guessing experiments on its head, so that instead of choosing the correct English meaning for a given Japanese word, participants chose the correct Japanese word for a given English meaning.
 In this way, there was only one English word involved in the task, and the options participants chose between were simply two Japanese words which they knew nothing about, other than how they sound.
@@
 
-## Guessing experiments -- guessing between words
+## Guessing experiments: guessing between words {#goodguesses}
 
@@
 
-The foil words were artificially generated to be as phonologically distinct as possible from the answer word, while still conforming to Japanese phonology.
+The incorrect 'foil' word in each item was a nonsense Japanese word artificially generated to be as phonologically distinct as possible from the correct word, while still conforming to Japanese phonology.
 For every word, three different foil words were generated by substituting each consonant with its top three most phonologically distant consonants in the Japanese sound system.
-Phonological distances were calculated using the Phonological Corpus Tools software [@hall_phonological_2019], with the feature system provided by Mielke [-@mielke_phonetically_2012].
-Vowels were substituted by rotating the vowel space 180 degrees, so that /a/ > /u/, /i/ > /a/, /u/ > /i/, /e/ > /o/, and /o/ > /e/.
-Finally, reduplicated words were ‘unreduplicated’ in their foil words.
-For example, the foils for *fuwafuwa* were *rizyu*, *gityu* and *nitsu* (not *rizyurizyu*, *gityugityu* and *nitsunitsu*).
-
-By using foil words that sound as different as possible to the target word, we hoped to improve the sensitivity of the measure to any potential iconicity in the target word, as if the target word *is* iconic for a concept, then a word that sounds very different to it should be a bad fit for that same concept--making the choice between the two easier.
-To test whether this was really the case, we ran one of the experiments a second time with foils that were randomly chosen from the other trials in the experiment, instead of using phonologically distinct foils.
-
-## Rating task
+Phonological distances were calculated using the feature matrix provided in PHOIBLE [@phoible], with the distance between two sounds being equal to the sum of the distances between each of their feature values.
+Distances were calculated as follows:
+
+> The distance between two feature values that are identical is 0.
+The distance between two opposing values (+/- or -/+) is 1—except if the feature involved is length or voicing, then the distance is 0.5, The distance between two feature values when one of them is 0 (= not applicable) is 0.25.
+
+Since /a/ is often the most phonologically distant vowel from many of the vowels in the Japanese sound system, to avoid the foil words all having similar vowels, a different approach was used for substituting vowels.
+Instead of using feature values, vowels were substituted with the vowel obtained by rotating the vowel space 180 clockwise or counterclockwise.
+So /u/ is substituted with either /a/ or /i/, and /a/ is substituted with either /i/ or /u/ (see Figure \@ref(fig:vowels)).
+
+```{r vowels,fig.cap="Vowel substitutions for the creation of foil words"}
+knitr::include_graphics("images/vowels.PNG")
+```
+
+Finally, reduplicated words were ‘unreduplicated’ when creating foil words. For example, the foils for *fuwafuwa* were *watʃi*, *nati* and *ridːu* (not *watʃiwatʃi*, *natinati* and *ridːuridːu*).
+
+By using foil words that sound as different as possible to the target word, we hoped to improve the sensitivity of the measure to any iconicity in the target word.
+Our logic was that if the target word *is* iconic for a concept, then a word that sounds very different to it should be a bad fit for that same concept--making the choice between the two easier.
+To test whether this was really the case, we ran one of the experiments a second time using foils that were randomly chosen from among the other trial items in the experiment, rather than phonologically distinct foils.
+
+## Rating task {#ratings}
 
@@
 
-Participants had to listen to the Japanese words and were told their meanings, then asked to rate the resemblance between the word and its meaning on a scale from 0 'No resemblance' to 6 'Strong resemblance'.
+Participants had to listen to the Japanese words and were told their meanings, then asked to rate the resemblance between the word and its meaning on a scale from 0 'No resemblance' to 6 'Strong resemblance' (see Figure \@ref(fig:ratingdemo)).
 Previous studies [@perry_iconicity_2015] also used a negative end of the scale (corresponding to a 'bad resemblance').
-However, follow-up analysis found that the negative end of the scale was both underused and inconsistently used, suggesting that anti-iconic relationships are difficult to assess [@motamedi_iconicity_2019].
+However, follow-up analyses found that the negative end of the scale was both underused and inconsistently used, suggesting that anti-iconic relationships are difficult to assess [@motamedi_iconicity_2019].
 For this reason, we decided to only use a positive scale in this study.
-A sample trial is shown in Figure \@ref(fig:ratingdemo).
 
@@
 
-# Results
+## Creation of Icotools
+
+To make the collection of guesses and ratings quicker and easier for future studies, while also improving comparability between studies, we created a python package, `icotools` [(https://pypi.org/project/icotools/)](https://pypi.org/project/icotools/), with functions that can be used to automatically generate rating and guessing experiments (using the meaning-to-word design from the second guessing experiments).
+The package has three functions: a rater function, a guesser function, and a foiler function.
+The rater and guesser functions create rating and guessing experiments as described in Sections \@ref(goodguesses) and \@ref(ratings).
+They take two csv files as input.
+The first is a wordlist containing the items in the experiment (including trials, practice items, control items, and sets of translations to use for them), while the second file is used for customisation (e.g.
+to specify how many items to include in each experiment, the location of media files, custom instructions and custom exit questions, etc.).
+
+For each experiment, the functions produce three files--a html file, a php file, and a csv file.
+These files can then be uploaded to a server, the link to the html files can be shared with participants, and as the participants complete the experiments their responses will be written to the csv file by the php file.
+The functions also produce a summary csv file with all the details of the experiments (i.e.
+the trials in each experiment, as well as the translations and, where applicable, foils used).
+An R script is provided to collate the responses for all experiments into one long tidy dataset after data collection is complete.
+
+The foiler function can be used to generate a list of opposite sounding foil words for each item in a guessing experiment, following the method described in Section \@ref(goodguesses).
+It is also possible to specify your own foil words, or to choose the foils randomly from among the other items in the experiment.
+For a full description of how to use icotools, please see the ReadMe at https://anonymous.4open.science/r/IcoTools-2CEA/README.md (this is an anonymised link to the github repository: it will later be replaced with the correct link).
+
+# Statistical analyses
+
+Statistical analyses were conducted using `R.Version()$version.string`.
 
@@
 We first investigated whether ratings and guesses were robust to different choices of translations (for ratings and guesses) and foils (for guesses only).
-For each word separately, we performed Fisher's Exact Tests on the guessing data, and anovas on the rating data, to determine whether guessing performance or ratings given differed significantly between different translations and foils.
+For each word separately, we performed Fisher's Exact Tests on the guessing data, and ANOVAs on the rating data, to determine whether the guessing performance or ratings given differed significantly between different translations and foils.
+As the ANOVAs are less robust to small amounts of data than the Fisher's Exact Tests, for the rating data we excluded translations with fewer than 10 ratings from this particular analysis.
 
@@
 
-guesses_words%>%
-  mutate(word_spec=paste(word,concept,sep="_"))->guesses_words
-
-words<-unique(guesses_words$word_spec)
+words<-unique(guesses_words$identifier)
 
@@
 for(w in words){
-  d<-subset(guesses_words,word_spec==w)
+  d<-subset(guesses_words,identifier==w)
   t<-table(d$trans,d$answer)
-  if (nrow(t)>1){
+  if (nrow(t)>1&ncol(t)>1){
     doubly_tested_words <- c(doubly_tested_words,w)
@@
 for(w in words){
-  d<-subset(guesses_words,word_spec==w)
+  d<-subset(guesses_words,identifier==w)
   t<-table(d$foil,d$answer)
-  if (nrow(t)>1){
+  if (nrow(t)>1 & ncol(t)>1){
     doubly_tested_words <- c(doubly_tested_words,w)
@@
 ratings%>%
+  select(identifier,trans,rating)%>%
   group_by(identifier)%>%
   add_count(trans)%>%
-  filter(n>=10)%>%
-  select(identifier,trans,rating)->data
+  filter(n>=10)->data
 
@@
 In the first pilot of the guessing task--where participants were guessing between English translations--11 out of the 45 words tested (=24%) showed significant differences in their guessability when either the translation and/or the foil was changed.
-In the second version of the guessing task--where participants were guessing between Japanese words--15 out of the 131 words tested (=11%) showed significant differences in their guessability when either the translation and/or the foil was changed.
-In the rating task, 12 out of 92 words tested (=13%) showed significant differences in their iconicity rating when the translation word was changed^[We excluded translations with fewer than 10 ratings from this analysis as the t-test is less robust against small sample sizes than the fisher test.].
+In the second version of the guessing task--where participants were guessing between Japanese words--39 out of 303 words tested (=13%) showed significant differences in their guessability when either the translation and/or the foil was changed.
+In the rating task, 11 out of 88 words tested (=13%) showed significant differences in their iconicity rating when the translation word was changed.
 
@@
 
-randomfoils <- read_csv("results-randomfoils.csv")
+randomfoils <- read_csv("responses-randomfoils.csv")
 
@@
   mutate(score=sum(result=="correct")/sum(result=="correct"|result=="incorrect"))%>%
-  select(identifier,score)->randomres
+  select(form,score)%>%unique()->randomres
+
+words <- randomres$identifier
+replace(words,words=="zoNzoN_SHIVERING","zoNzoN_(SPINE) TINGLING")
+replace(words,words=="genki_LIVELY","geNki_LIVELY (ENERGETIC)")
+
+zyiNzyiN_POUNDING (HEAD)
 
 guesses_words%>%
-  group_by(word_spec)%>%
+  group_by(identifier)%>%
   mutate(score=sum(answer=="correct")/sum(answer=="correct"|answer=="incorrect"))%>%
-  select(identifier=word_spec,score)->oppres
+  select(form,score)%>%unique()->oppres
 
@@
 
-#table(comparison$design,comparison$`above chance`)
+table(comparison$design,comparison$`above chance`)
 #chisq.test(table(comparison$design,comparison$`above chance`))
@@
 
+# Data Availability Statement
+
+The data from the study, as well as the code used to produce the experiments and analyses can be found on the Open Science Framework, at https://osf.io/j57uc/?view_only=d59ffde4bc42467fafb71a904bef8d14.
+
 # References

### 2022-01-26 paper.Rmd
finished first draft

@@
 output:
-  bookdown::word_document2:
-    reference_docx: wordstyles.docx
+  bookdown::html_document2:
+   # reference_docx: wordstyles.docx
     toc: true
@@
     css: custom.css
+    code_folding: hide
 always_allow_html: true
@@
 library(ggeffects)
-knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message = FALSE)
+library(gridExtra)
+knitr::opts_chunk$set(echo = TRUE,warning=FALSE,message = FALSE)
 ```
@@
 
+**Keywords:** iconicity, ideophones, lexical norms, iconicity ratings, guessability
+
 # Introduction
@@
 To discover how to get the most out of each measure, we compare and contrast different rating and guessing paradigms, and in particular introduce a new guessing paradigm that improves on the robustness, discriminability and sensitivity of previous approaches.
-Finally, to promote the use of these new measures, we introduce a reproducible workflow for automatically generating rating and guessing experiments in a standardised format, via a python package `icotools` [(https://pypi.org/project/icotools/)](https://pypi.org/project/icotools/), with support for a variety of stimulus formats (audio, video, and images).
+Finally, to promote the use of these new measures, we introduce a reproducible workflow for automatically generating rating and guessing experiments in a standardised format, via a python package `icotools`, with support for a variety of stimulus formats (audio, video, and images).
 This will make the collection of behavioural based iconicity measures quicker, easier, and more comparable between future studies.
@@
 In all three cases, the participants performed poorly on the control items and either did not provide a task description, or their task descriptions were irrelevant (they commented that the task was 'interesting' or 'difficult' instead of describing what they were doing in the task).
-[COME BACK TO THIS POINT IT'S GOOD THE NEW GUESSING TASK PEOPLE SEEM TO UNDERSTAND IT BETTER]
 
@@
 Criteria (b) was used in 3 exclusions, and criteria (c) was used in 4 exclusions.
-
-[OF THE THREE VERSIONS OF THE TASK, I THINK MATCHING THE WORD IS INTUITIVELY EASIEST FOR PARTICIPANTS TO UNDERSAND]
-[I LOOKED AT REACTION TIMES AS WELL BUT THERE WERE ONLY TWO TRUE OUTLIERS IN THE WHOLE DATASET AND THEY WERE FOR PRACTICE ITEMS SO I COULDN'T BE BOTHERED DOING IT]
 
@@
 
-```{r guessingtrans, fig.cap="Guessing task - guessing between translations"}
+```{r guessingtrans, fig.cap="Guessing task - guessing between translations",echo=FALSE}
 knitr::include_graphics("images/guessingtransdemo.PNG")
@@
 Finally, the length of the sentences was also kept consistent (to a difference of no more than 5 characters) between pairings of translations and foils.
-
 To test the robustness of the guessing procedure to different choices of translation and foil words, the same words were tested multiple times with different translations and foils.
@@
 
-```{r weirdcases}
+```{r weirdcases,echo=FALSE}
 guesses_trans%>%
@@
 
-```{r guessingwords, fig.cap="Guessing task - guessing between words"}
+```{r guessingwords, fig.cap="Guessing task - guessing between words",echo=FALSE}
 knitr::include_graphics("images/guessingwords.PNG")
@@
 
-```{r guessingwordsspec, fig.cap="Guessing task - guessing between words"}
+```{r guessingwordsspec, fig.cap="Guessing task - guessing between words",echo=FALSE}
 knitr::include_graphics("images/guessingwordsspec.PNG")
@@
 So /u/ is substituted with either /a/ or /i/, and /a/ is substituted with either /i/ or /u/ (see Figure \@ref(fig:vowels)).
-
-```{r vowels,fig.cap="Vowel substitutions for the creation of foil words"}
+Finally, reduplicated words were ‘unreduplicated’ when creating foil words.
+For example, the foils for *fuwafuwa* were *watʃi*, *nati* and *ridːu* (not *watʃiwatʃi*, *natinati* and *ridːuridːu*).
+
+```{r vowels,fig.cap="Vowel substitutions for the creation of foil words",echo=FALSE}
 knitr::include_graphics("images/vowels.PNG")
 ```
-
-Finally, reduplicated words were ‘unreduplicated’ when creating foil words. For example, the foils for *fuwafuwa* were *watʃi*, *nati* and *ridːu* (not *watʃiwatʃi*, *natinati* and *ridːuridːu*).
 
@@
 
-```{r ratingdemo, fig.cap="Rating task"}
+```{r ratingdemo, fig.cap="Rating task",echo=FALSE}
 knitr::include_graphics("images/ratingdemo.PNG")
@@
 
-# Statistical analyses
-
-Statistical analyses were conducted using `R.Version()$version.string`.
+# Results
+
+Statistical analyses were conducted using `r R.Version()$version.string`.
 
@@
 #binom.test(21,30,p=.5)
-
 randomfoils <- read_csv("responses-randomfoils.csv")
@@
 
+# fix up some naming differences
 words <- randomres$identifier
-replace(words,words=="zoNzoN_SHIVERING","zoNzoN_(SPINE) TINGLING")
-replace(words,words=="genki_LIVELY","geNki_LIVELY (ENERGETIC)")
-
-zyiNzyiN_POUNDING (HEAD)
+words <- replace(words,words=="zoNzoN_SHIVERING","zoNzoN_(SPINE) TINGLING")
+words <- replace(words,words=="geNki_LIVELY","geNki_LIVELY (ENERGETIC)")
 
 guesses_words%>%
+  filter(identifier %in% words|form=="zyiNzyiN")%>%
   group_by(identifier)%>%
   mutate(score=sum(answer=="correct")/sum(answer=="correct"|answer=="incorrect"))%>%
+  ungroup()%>%
   select(form,score)%>%unique()->oppres
 
-comparison <- left_join(randomres,oppres,by="identifier")%>%
+comparison <- left_join(randomres%>%select(-identifier),oppres,by="form")%>%
   rename(random_foils=score.x,opp_foils=score.y)%>%unique()
@@
 
-table(comparison$design,comparison$`above chance`)
+#table(comparison$design,comparison$`above chance`)
 #chisq.test(table(comparison$design,comparison$`above chance`))
@@
 Thompson et al.'s study included both words from the Yamato stratum, as well as Sino-Japanese and foreign words.
-This study only included Yamato words, and predominantly these were verbs, adverbs and adjectives.
+This study only included Yamato words, mainly verbs, adverbs and adjectives.
 Both the data in this study and in Thompson et al.
@@
 ```{r discriminability,fig.cap="Discriminability of different measures"}
-oppres%>%
-  mutate(method="guesses between words")%>%
-  unique()->oppres
+guesses_words%>%
+  group_by(identifier)%>%
+  mutate(score=sum(answer=="correct")/sum(answer=="correct"|answer=="incorrect"))%>%
+  select(identifier,score)%>%
+  unique()%>%
+  mutate(method="guesses between words")->oppres
 
@@
 was more varied, with proportionally less ideophones.
-Thus, this could well be simply a reflection of the differences between the two datasets rather than relating to the methods used.
+Thus, this could simply be a reflection of the differences between the two datasets rather than relating to the methods used.
 
@@
 However, at the bottom of the scale something strange happens.
-While in the ratings, the bottom of the scale is dominated by non-ideophones (as expected), in the guesses, the bottom of the scale is actually dominated by *ideophones*.
+While for the ratings, the bottom of the scale is dominated by non-ideophones (as expected), for the guesses, the bottom of the scale is actually dominated by *ideophones*.
 That is, ideophones are simultaneously guessed *better* and *worse* than non-ideophones.
@@
 # get info on ideophones
-words <- read_csv("wordlist.csv")
+words <- read_csv("ideophone_list.csv")
 words%>%
@@
 
-library(gridExtra)
 comparison_dat%>%
@@
 For both ideophones and non-ideophones, there was a strong correlation between the ratings and the guesses.
-This correspondence was slightly better for the ideophones (r = 0.65, 95% CI [0.44, 0.79], t(43) = 5.57, p < .001) than for the non-ideophones (r = 0.43, 95% CI [0.23, 0.60], t(71) = 4.06, p < .001).
+This correspondence was slightly better for the ideophones (r = 0.66, 95% CI [0.44, 0.79], 95% CI [0.53, 0.76], t(99) = 8.68, p < .001) than for the non-ideophones (r = 0.41, 95% CI [0.29, 0.52], t(201) = 6.45, p < .001).
 To explore this relationship further, we created two linear regression models: one predicting guesses from ratings, ideophone status, and the interaction between these two factors, and a second model predicting ratings from guesses, ideophone status, and the interaction between these two factors.
 Both models again used the z-scores rather than the raw ratings and guesses.
+The models were created using the R package `lmerTest` (version `r packageVersion("lmerTest")`) [@lmertest].
 
@@
 
-```{r bootstrap function, eval=FALSE}
-info <- read_csv("wordlist.csv")%>%select(form,ideophone)
+```{r bootstrap function,cache=TRUE,eval=FALSE}
 # my ratings from English people
@@
 
-```{r run bootstrap, cache=TRUE, message=FALSE, warning=FALSE, eval=FALSE}
+```{r run bootstrap, cache=TRUE, message=FALSE, warning=FALSE,eval=FALSE}
 
@@
 
-```{r make person-total graph, eval=FALSE}
+```{r make person-total graph,eval=FALSE}
 cis %>% 
@@
 
-```{r ratingconsistency,fig.cap="Consistency between participants for iconicity ratings of ideophones versus non-ideophones",out.width="70%"}
-knitr::include_graphics("images/persontotal.svg")
+```{r ratingconsistency,fig.cap="Consistency between participants for iconicity ratings of ideophones versus non-ideophones",out.width="70%",echo=FALSE}
+knitr::include_graphics("images/bootstrapping.png")
 ```
@@
 The result highlights the subjective nature of form-meaning associations, and that by taking above-chance guessing accuracy as a measure of iconicity we are only picking up on those associations that happen to correspond--and crucially not to conflict--between (in this case) English and Japanese speakers.
-
-Poor guessing accuracies could be explained by conflicting, non-resemblance based associations.
+This is something researchers should be aware of, because it means that decisions about *whom* to collect iconicity measurements from are very important.
+
+Poor guessing accuracies could be explained by conflicting associations.
 For example, one person commented that *zarazara* as a word for ‘ROUGH’ sounds wrong to them because they associate the word *zara* with the clothing store ZARA, and clothes are soft.
@@
 Thus, if they do exist, we predict that the majority of non-resemblance based associations should be reflected in poorer rather than higher guessing accuracies.
-
-That the poor guessing results also corresponded to lower ratings suggests that these ratings also likely reflect form-meaning *associations*, rather than form-meaning *resemblances* specifically.
-This is despite the instructions in the task specifically asking about resemblances.
-That participants in rating studies do not distinguish iconicity from indexicality or other kinds of associations is hardly surprising, given these are distinctions even seasoned semioticians can find a struggle.
-Nor is it necessarily problematic; whether the association is based on resemblance or other factors, the end result it the same--a bias.
-However, it is something researchers should be aware of, because it means that decisions about *whom* to collect iconicity measurements from are very important, since associations are much more dependent on world experience than resemblances [see also @motamedi_iconicity_2019: 17].
-
-Even resemblance itself is not entirely objective, though this is often an assumption of rating and guessing studies.
-In the beginning of this study, we defined iconicity as involving *perceived* resemblances, reflecting a conception of iconicity not as an objective property of signs, but as a subjective process involving construal (Occhino et al.
-2017; Occhino, Anible, and Morford 2020).
-Occhino et al.
-[-@occhino_role_2020: 117] provide an excellent illustration of this in the ASL sign for dance, which involves an inverted V-handshape.
-On its own, the meaning of this sign is unlikely to be transparent to non-signers.
-However, a signer will recognise the inverted-V handshape from a network of signs involving the construal of a pair of legs mapped to a pair of extended fingers--such as in the sign STAND, which is likely to be transparent to non-signers.
-Thus, iconicity can be both language-internal (as in the sign for DANCE) and/or language-external (as in the sign for STAND).
-However, guessing studies and rating tasks with non-speakers will only pick up on examples of language-external iconicity, while language-internal iconicity falls under the radar.
-
-It is even possible that different construals could lead to non-speakers having exactly the *opposite* iconic mapping to the mapping in the language under study.
-This is perhaps more likely in spoken than in signed languages, particularly where phoneme inventories are small.
-The most famous example comes from vowel-size sound symbolism.
-The most common mapping relates high vowels--like /i/--to smallness, and low vowels--like /a/--to largeness [@ultan_size-sound_1978].
-However, a few languages also show the *reverse* mapping--two examples are Korean and Bahnar [@shinohara_cross-linguistic_2010; @difflothibig_1994].
-Different construals make it possible for both mappings to be perceived as iconic to speakers, and in fact this is likely since the reverse mappings are actually reported in ideophones--which speakers generally perceive as iconic [@thompson_iconicity_2020].
-For example, a construal of the change from /i/ to /a/ as involving an *expansion* of the space in the oral cavity could lead to the /i/-small, /a/-large mapping.
-However, one could also construe the same event as involving the *contraction* of the space occupied by the tongue, resulting in an /i/-large, /a/-small mapping.
-Interestingly, despite the conflicting mapping in their own language, when evaluating non-words Korean speakers still show a preference for the /i/-small, /a/-big mapping [@shinohara_cross-linguistic_2010].
-This is encouraging as it suggests that when judging unfamiliar stimuli, conflicting mappings in the participants own languages are unlikely to hide iconic effects in cases where the naturalness of the mapping is very strong [as in the /i/-small, /a/-big example; @ultan_size-sound_1978]
+It is interesting that conflicting associations appear to have a stronger effect in ideophones (some of which were guessed at accuracies significantly below chance) than in non-ideophones (which were guessed below chance only rarely).
+Perhaps because participants are more likely to view form-meaning relationships in ideophones as meaningful (due to their structural markedness), they are more likely to attach conflicting associations to ideophones, leading to a stronger sense that the ideophone should correspond to the *opposite* of the given meaning.
 
@@
 This is not so problematic, as the ratings still correlate with guessing accuracy, indicating that the relative differences in iconicity still hold.
-However, it highlights that interpretations of (particularly low) ratings as reflections of iconicity should be taken with a grain of salt.
+However, it highlights that interpretations of particularly *low* iconicity ratings as reflections of iconicity should be viewed with caution.
 
@@
 They found that both types of iconicity were helpful to signers of a lower proficiency, but that for highly proficient signers only the most pervasive, language-external mappings made a difference to processing.
-Guessing and rating comparisons could also be useful to explore the influence of structural markedness on iconicity effects.
-Since structural markedness appears to boost ratings but not guessability, the two measures could be used together to tease apart the influence of structural markedness versus form-meaning resemblances in driving iconic effects.
-We tend to assume that iconic effects are driven by form-meaning resemblances, but since these often go together with structural markedness it would be useful to know the relative contribution of each factor in different situations and tasks.
-Since structural markedness is also subjective, the choice of participants used in the rating task should be theoretically justified and matched to the phenomenon the measures will be used to study.
-For example, if the measures will be used to study language processing in adults, then adult native speakers should be used.
+
+Since structural markedness appears to boost ratings but not guessability, the two measures could also be used together to tease apart the influence of structural markedness versus form-meaning resemblances in driving iconic effects.
+Iconic effects are generally assumed to be driven by form-meaning resemblances, but since these often go together with structural markedness it would be useful to know the relative contribution of each factor in different situations and tasks.
+Since structural markedness is also subjective, the choice of participants used in the rating task will be important.
 Finally, having guesses alongside ratings would allow researchers to make better decisions about the cut-off point between "high" and "low" iconicity ratings, as these could be motivated by correlations with guessing accuracy, rather than e.g.
@@
 taste).
+
 In contrast, a task in which participants guess between words is much easier to operationalise.
@@
 
-We also compared our iconicity ratings from non-speakers with iconicity ratings from native speakers in @thompson_iconicity_2020.
+We also compared our iconicity ratings from non-speakers with iconicity ratings from native speakers in Thompson et al.
+[-@thompson_iconicity_2020].
 We found that, although using non-speakers resulted in a lesser spread of measures (suggesting that native speakers are more confident in giving high and low ratings than non-native speakers), when evaluating the agreement between raters, ratings from non-speakers were just as reliable as ratings from native speakers--as well as being fairly robust to different choices of translation.
 Ratings from non-speakers were more reliable for ideophones than for non-ideophones--but this is not to say that the ratings for non-ideophones were unreliable.
-Rather, the ratings for ideophones were *particularly* reliable, probably because these words were more likely to be iconic in the first place, and so raters were more likely to have stronger intuitions about these words.
+Rather, the ratings for ideophones were *particularly* reliable, probably because raters were more likely to have stronger intuitions about these words due to their structural markedness, and because they are more likely to be iconic in the first place.
 The same pattern was seen in the ratings from native speakers, although it did not reach statistical significance.
-Since both types of ratings are fairly reliable, our recommendation would be to use whichever design is most theoretically justified (see discussion in Section \@ref(maindiscussion)).
+Since both types of ratings are fairly reliable, our recommendation would be to choose participants for rating tasks according to how the ratings are going to be used.
+For example, to predict language processing in adult native speakers of a language, it would make sense to collect ratings from other adult native speakers of the same language.
 

### 2022-01-27 paper.Rmd
adding stuff

@@
 
-Iconicity--defined here as a perceived resemblance between aspects of form and meaning--is now increasingly recognised as a *design feature of language* [see e.g.
-@perniss_iconicity_2010; @perniss_bridge_2014; @dingemanse_arbitrariness_2015 for a review], raising important questions about where iconic mappings come from, and what they do.
+Iconicity--defined here as a perceived resemblance between aspects of form and meaning--is now increasingly recognised as a *key property of language* [see e.g.
+@perniss_iconicity_2010; @perniss_bridge_2014; @dingemanse_arbitrariness_2015 for a review], raising questions about where iconic mappings come from, and what they do.
 To answer these questions, we first need to be able to *identify* iconicity in language and, ideally, to *measure* it.
@@
 However, ratings given are influenced by the linguistic experience of participants (@occhino_iconicity_2017; @sevcikova_sehyr_perceived_2019), so some care is needed to ensure measures are taken from appropriate participant groups.
+Further, ratings from native speakers may also capture non-iconic regularities like semantic transparency and indexicality [@dingemanse_playful_2020; @winter_iconicity_2021], so cannot be taken as direct reflections of degree of iconicity.
 
@@
 
-While results from behavioural experiments often require some untangling, we believe that they are particularly valuable sources of iconicity measures for four reasons: (1) they can be applied to any kind of dataset, (2) they are highly scalable, being particularly amenable to online, crowd-sourced data collection, (3) they are tweakable, meaning that we can experiment with different experimental designs to figure out exactly what these measures are telling us, and (4) they are amenable to standardisation, making them a good option for reproducibility.
+While results from behavioural experiments often require some untangling, we believe that they are particularly valuable sources of iconicity measures for four reasons: (1) they can be applied to any kind of dataset, (2) they are scalable, being particularly amenable to online, crowd-sourced data collection, (3) they are tweakable, meaning that we can experiment with different experimental designs to figure out exactly what these measures are telling us, and (4) they are amenable to standardisation, making them a good option for reproducibility.
 In fact, they are the *only* measures of iconicity that we know of to combine all these things.
@@
 
-The stimuli were 304 Japanese words from the domain of sensory perception, including both ideophones and prosaic lexical items.
+The stimuli were 304 words taken from the *Japonic Sensory Lexicon* database (ANONYMISED CITATION), which is a collection of words for 110 sensory concepts in 49 Japonic varities.
+
+```{r}
+# semantic domains of concepts, plus numbers of ideophones and non-ideophones
+concepts <- read_tsv("https://raw.githubusercontent.com/BonnieMcLean/JaponicSensoryLex/main/concepts.tsv")%>%
+  rowwise()%>%
+  mutate(concept=str_split(concept,"-")[[1]][1])%>%
+  select(concept,domain)
+
+words <- read_csv("responses-guessingwords.csv")%>%
+  select(form,identifier)%>%
+  mutate(identifier=str_replace_all(identifier,"FUZZY","CLEAR"))%>%
+  rowwise()%>%
+  mutate(concept=str_split(identifier,"_")[[1]][2])%>%
+  unique()%>%
+  left_join(concepts,by="concept")
+
+words <- read_csv("ideophone_list.csv")%>%
+  select(form,ideophone)%>%
+  right_join(words,by="form")
+
+# plus the practise and control items which arent in the Japonic sensory lexicon
+words$domain[words$form == "yoroyoro"] <- "action"
+words$domain[words$form == "fuwafuwa"] <- "texture"
+words$domain[words$form == "hisohiso"] <- "sound"
+words$domain[words$form == "pyoNpyoN"] <- "action"
+
+```
+
+```{r}
+dat <- read_csv("https://raw.githubusercontent.com/BonnieMcLean/JaponicSensoryLex/main/dat.csv")
+info <- 
+words <- read_csv("responses-guessingwords.csv")%>%
+  select(identifier)%>%
+  mutate(identifier=str_replace_all(identifier,"FUZZY","CLEAR"))%>%
+  unique()
+
+cognates <- read_csv("cognatecodes.csv")%>%
+  mutate(identifier=paste(test_form,eng_trans,sep="_"))%>%select(cognate,identifier)
+
+words <- words%>%left_join(cognates,by="identifier")
+```
+
+The stimuli were 304 words from the Yamato stratum of the Japanese lexicon, in the semantic domain of sensory perception.
+The words were taken from the *Japonic Sensory Lexicon* (ANONYMISED CITATION), a dataset containing words in
+
+from the domain of sensory perception, including both ideophones and prosaic lexical items.
 For all tasks, the words were presented to participants as audio files.

### 2022-01-29 exclusions.Rmd
fixed up discussion

--- 2022-01-26 paper.Rmd
@@
 ---
-title: "Two measures are better than one: Combining iconicity ratings and guessing experiments for a more nuanced picture of iconicity in the lexicon"
+title: "Exclusions"
 output: 
     bookdown::html_document2:
-   # reference_docx: wordstyles.docx
       toc: true
@@
       code_folding: hide
-always_allow_html: true
 bibliography: sources.bib
@@
 ```{r packages, include=FALSE}
+library(bookdown)
 library(tidyverse)
-library(kableExtra)
-library(bookdown)
-library(report)
-library(lmerTest)
-library(plotly)
-library(corrr)
-library(boot)
-library(zeallot)
-library(pander)
-library(sjPlot)
-library(ggeffects)
-library(gridExtra)
 knitr::opts_chunk$set(echo = TRUE,warning=FALSE,message = FALSE)
 ```
-
-**Abstract**
-
-Iconicity in language is receiving increased attention from many fields, but our understanding of the roles of iconicity in language is only as good as the measures we use to quantify it.
-We conducted iconicity rating and guessing experiments with 304 Japanese ideophones and prosaic words with sensory meanings, e.g.
-*fuwafuwa* ‘fluffy’, *jawarakai* ‘soft’.
-For both word groups, ratings and guesses were positively correlated—suggesting the two measures pick up on the same associations.
-Ideophones were consistently associated with higher iconicity ratings, but not higher guessing accuracy.
-We suggest that the structural markedness of ideophones enhances their perceived iconicity in the rating task, but does not provide any advantage (over and above form-meaning associations) in the guessing task.
-Thus, guesses and ratings could be used together to tease apart the relative contribution of structural markedness to iconic effects.
-Some ideophones were also poorly guessed, highlighting that construals of iconicity can be language-specific.
-Finally, we present some methodological contributions, including a new guessing paradigm that improves on the robustness, sensitivity and discriminability of previous approaches, and a reproducible workflow for creating rating and guessing experiments with a Python package, `icotools`, which we hope will improve comparability between future studies.
-
-**Keywords:** iconicity, ideophones, lexical norms, iconicity ratings, guessability
-
-# Introduction
-
-What does it mean when we say that something is a "good word for" a concept?
-Certain words, like *klutz*, *schmooze*, and *smush*, seem to "suit" their meanings.
-We may have a sense that the French *belle* is a more appropriate word for BEAUTY than the Swedish *vacker*.
-Such intuitions are likely to be somewhat subjective, and influenced by our own linguistic experiences, but we all have them.
-The idea that certain forms can be particularly suited to certain meanings is known as *iconicity*.
-
-Iconicity--defined here as a perceived resemblance between aspects of form and meaning--is now increasingly recognised as a *design feature of language* [see e.g.
-@perniss_iconicity_2010; @perniss_bridge_2014; @dingemanse_arbitrariness_2015 for a review], raising important questions about where iconic mappings come from, and what they do.
-To answer these questions, we first need to be able to *identify* iconicity in language and, ideally, to *measure* it.
-
-Approaches to measuring iconicity can be divided into descriptive, data-driven, and behavioural methods [@motamedi_iconicity_2019].
-Of these, only descriptive approaches target *iconicity* directly, with other methods simply identifying form-meaning association *biases*--whether these be based on resemblance (as in iconicity), co-occurrence (indexicality), statistically driven associations (systematicity), functional advantages, or other factors.
-
-With descriptive approaches, iconicity as a theoretical concept is coded for directly (e.g.
-@pietrandrea_iconicity_2002; @hwang_body_2017; @ostling_visual_2018; @thompson_defining_2019; @voronin_osnovy_2006; @flaksman2020stanislav).
-This is more common and straightforward for sign languages than for spoken languages [@thompson_defining_2019].
-It is usually done manually, but Östling et al.
--@ostling_visual_2018 have shown for sign languages that (for some mappings at least) this can also be automated.
-Such studies usually involve cross-linguistic data, and aim to uncover universalities in how different languages map sound to meaning--that is, *where* iconicity comes from.
-
-A wider variety of approaches target iconicity *indirectly* through related phenomena.
-For example, data-driven approaches (e.g.
-@wichmann_sound_2010; @blasi_soundmeaning_2016; @joo_phonosemantic_2019; @johansson_typology_2020; @winter_trilledr) use comparisons across unrelated languages to identify form-meaning correspondences that occur at rates higher than chance.
-This requires large amounts of parallel data from distinct phyla, and existing studies usually focus on basic vocabulary--where such data is most readily available.
-Like descriptive approaches, data-driven approaches identify *specific* form-meaning associations involved in iconic effects, but with the added advantage of not needing to rely on the intuitions and manual labour of individual researchers.
-However, they *do* rely on the existence of translation equivalents in multiple languages for the words under study.
-This can pose a particular challenge for highly iconic words, as these often also have highly specific meanings (@lupyan_language_2018; @akita_toward_2012).
-Thus, these approaches are less likely to be helpful for those with *specific* words for which iconicity measures are required.
-
-Another body of work which capitalises on big data involves the study of *affective iconicity* [e.g.
-@ullrich_phonological_2016; @aryani_why_2018].
-These studies use large datasets of affective norms to identify phonological segments loaded with affective meaning (by taking average affectiveness values across all words containing those segments, and identifying segments with values deviating from the global neutral mean).
-Although limited to associations involving affect, this approach has been successfully used to investigate iconic effects in language processing [@schmidtke_effects_2018; Ullrich in prep; @aryani_affective_2018], and has even been used to explain the affective meaning of poems [@ullrich_relation_2017].
-
-Behavioural approaches involve the collection of data from naive experimental participants, which can reveal something about the iconicity of given form-meaning pairings.
-The only requirement is the human participants for the study, and the largest amount of iconicity measurements from the widest variety of languages have been collected using these methods.
-There are two main approaches: iconicity rating tasks and guessing experiments.
-
-In iconicity rating tasks, the concept of iconicity is explained to participants, and participants are asked to rate the iconicity of given form-meaning pairs directly [e.g.
-@vinson_british_2008; @perry_iconicity_2015; @winter_which_2017; @occhino_iconicity_2017; @thompson_iconicity_2020; @punselie_iconicity_2020].
-Measurements from these studies have been found to correlate in meaningful ways with factors related to iconicity--e.g.
-encoding of sensory information [@winter_which_2017], semantic domains [@punselie_iconicity_2020], semantic neighbourhood density [@sidhu_lonely_2018], word class [@perry_iconicity_2015; @thompson_iconicity_2020], age of acquisition [@vinson_british_2008; @perry_iconicity_2015], facilitated processing [@thompson_link_2009; @occhino_role_2020], funniness and structural markedness [@dingemanse_playful_2020].
-However, ratings given are influenced by the linguistic experience of participants (@occhino_iconicity_2017; @sevcikova_sehyr_perceived_2019), so some care is needed to ensure measures are taken from appropriate participant groups.
-
-In guessing experiments, participants are asked to guess the meaning of foreign/novel signs from a choice of two or more alternatives [e.g.
-@kohler_gestalt_1929; @tsuru_problem_1933; @brown_phonetic_1955; @kunihira_effects_1971; @ramachandran_synaesthesia_2001; @dingemanse_what_2016; @tzeng_specificity_2017; @perlman_iconicity_2015; @perlman_people_2018; @lockwood_sound-symbolism_2016].
-Signs whose meanings are correctly guessed at rates higher than chance are considered iconic.
-The guessability of signs has also been linked to facilitated processing [@ormel_role_2009] and learnability [@perlman_people_2018; @lockwood_sound-symbolism_2016], and correlated with iconicity ratings [@punselie_iconicity_2020].
-However, some signs that were given low iconicity ratings were actually highly guessable, while there were also a few signs that, despite receiving high ratings, were not easily guessed  [@punselie_iconicity_2020: 23].
-This suggests that guessing and rating tasks may tap into slightly different constructs, or be sensitive to experimental design constraints.
-
-While results from behavioural experiments often require some untangling, we believe that they are particularly valuable sources of iconicity measures for four reasons: (1) they can be applied to any kind of dataset, (2) they are highly scalable, being particularly amenable to online, crowd-sourced data collection, (3) they are tweakable, meaning that we can experiment with different experimental designs to figure out exactly what these measures are telling us, and (4) they are amenable to standardisation, making them a good option for reproducibility.
-In fact, they are the *only* measures of iconicity that we know of to combine all these things.
-Moreover, that the measures correlate with each other and with a variety of other meaningful phenomena speaks to their validity.
-
-In this study, we seek to further our understanding of these measures and how they can be useful by comparing and contrasting iconicity ratings and guesses for 304 Japanese words from the sensory vocabulary of Japanese.
-Sensory language was chosen as this is a domain high in iconicity, and where iconicity offers clear advantages [@winter_which_2017].
-The data contained a mix of ideophones--depictive, eye-catching words like *fuwafuwa* 'soft' and *pikapika* 'sparkly' that "invite and afford the construal of iconic mappings between form and meaning" [@akita_ideophone_2019: 18]--along with prosaic lexical items, like *yawai* 'soft' and *hikaru* 'shine', which are not necessarily expected to be lacking in iconicity--especially given their sensory meanings--but which are less obvious about it.
-We were particularly interested in how the iconicity measures for these words would compare between the rating studies--where participants are asked to make a conscious decision about the iconicity of the words--and the guessing studies--which tap into more unconscious biases.
-We find that when used together, the two methods shed light on each other, as well as raising pertinent questions about where iconicity effects come from.
-Our conclusion is that, for many of the questions that we have about iconicity in language, two measures may be better than one.
-
-To discover how to get the most out of each measure, we compare and contrast different rating and guessing paradigms, and in particular introduce a new guessing paradigm that improves on the robustness, discriminability and sensitivity of previous approaches.
-Finally, to promote the use of these new measures, we introduce a reproducible workflow for automatically generating rating and guessing experiments in a standardised format, via a python package `icotools`, with support for a variety of stimulus formats (audio, video, and images).
-This will make the collection of behavioural based iconicity measures quicker, easier, and more comparable between future studies.
-
-# Methods
-
-The data from the study, as well as the code used to produce the experiments and analyses can be found on the Open Science Framework, at https://osf.io/j57uc/?view_only=d59ffde4bc42467fafb71a904bef8d14.
-
-## Stimuli
-
-The stimuli were 304 Japanese words from the domain of sensory perception, including both ideophones and prosaic lexical items.
-For all tasks, the words were presented to participants as audio files.
-The audio files were synthesised using the Google Cloud Text-to-Speech API [(https://cloud.google.com/text-to-speech)](https://cloud.google.com/text-to-speech), with the female Japanese Wavenet voice ja-JP-Wavenet-B.
-They were then edited using Praat [@boersma_praat_2020] to have a flat pitch of 200Hz.
-Expressive prosody can enhance performance in guessing tasks [@kunihira_effects_1971; @dingemanse_what_2016], and so using a flat intonation was seen as the best way to ensure comparisons between the words were fair and not influenced by the prosody in a particular recording.
-We also considered synthesising all the words to have a marked intonation.
-However, different word lengths would make changes in pitch more dramatic in shorter words compared to longer words, affecting words of different lengths unequally.
-While flat, synthetic voices may be the best option for comparability, they are not a natural reflection of real-world experiences with iconicity--which involve not only segments but also prosody and even multimodal cues (e.g.
-accompanying gesture).
-Thus, if anything the results in this and similar studies likely *underestimate* iconicity in language.
-
-In all studies, participants were instructed to use headphones throughout the experiment, and could not procede to the experiment without first passing a listening test designed to require the use of headphones @woods_headphone_2017.
-The response buttons in each trial also did not appear until *after* the audio files had finished playing.
-This ensured that participants could not respond without first listening to the audio files.
-
-## Data collection
-
-All studies were conducted online, with participants recruited through the crowd sourcing service Prolific (www.prolific.co).
-The participants were monolingual English speakers residing in England, with no prior knowledge of Japanese.
-Although rating tasks are often conducted with native speakers, we used English speakers in this study for two reasons: first, to make the results as comparable as possible between the guessing and rating tasks; and second, because our data contained a mix of Standard Japanese and non-standard Japanese words, and we were concerned that using Standard Japanese speakers would lead to a bias towards standard words [@occhino_iconicity_2017].
-
-The words were split across 11 different experiments, in such a way that each experiment had a balance of words that were expected to be iconic, versus words that were not expected to be iconic.
-In addition, two 'practice words' and three 'control words' were included in every experiment.
-The practice items were used to give participants time to familiarise themselves with the experiment design, and were not included in the results.
-The control items were chosen from words found to be very iconic/highly guessable in previous studies, and were included as a check to identify participants who were perhaps not performing the task as intended.
-The first two trials in every experiment were the two 'practice words', while the order of the rest of the words in the experiment, including the control words, was randomly varied between participants.
-After finishing the experiment, participants were asked to describe the task they were performing during the experiment.
-This was used as an attention check, and to identify participants who had misunderstood the experiment instructions.
-Strange or lacking task descriptions, particularly when coupled with poor performance on the control items, were used to identify and exclude results from participants who were likely not performing the task as intended.
 
@@
 For the rating task, data from 5 out of 225 participants was excluded.
-For the ratings, as well as looking at task descriptions and performance on the control items, we calculated the person-total correlation for each participant @curran_methods_2016.
+For the ratings, as well as looking at task descriptions and performance on the control items, we calculated the person-total correlation for each participant [@curran_methods_2016].
 The person-total correlation is the correlation between an individual participant's ratings, and the mean ratings from every other participant.
 It provides a measure of how well a participant's responses agree with those of other participants in the task.
-The criteria for exclusion was two or more of either (a) strange or lacking task descriptions, (b) very low ratings for control items, or (c) low person-total correlations (<.2^[We chose .2 as the cut off point because it corresponded with a discontinuity in the lower end of the distribution of person-total correlations, see Figure 1 in the online Supplementary Material]).
+The criteria for exclusion was two or more of either (a) strange or lacking task descriptions, (b) very low ratings for control items, or (c) low person-total correlations.
 Criteria (a) was used for 4 exclusions.
@@
 Criteria (b) was used in 3 exclusions, and criteria (c) was used in 4 exclusions.
+A person-total correlation below .2 was considered a 'low' correlation, based on the distribution of person-total correlations shown in Figure \@ref(fig:ratingsprocess).
 
-```{r preprocessing ratings}
+```{r ratingsprocess,fig.cap="Distribution of person-total correlations in rating task"}
 # for ratings
@@
 
-persontotal_dist <- ggplot(data=persontotals,aes(x=pt_corr))+geom_histogram()+scale_x_continuous(n.breaks=8)
+persontotal_dist <- ggplot(data=persontotals,aes(x=pt_corr))+geom_histogram()+scale_x_continuous(n.breaks=8)+labs(x="Person-total correlation")
+persontotal_dist
 
@@
 
-Each experiment took a median of 6 minutes to complete, and participants were paid £0.75 for their participation (based on Prolific's 'good' hourly rate of £7.50).
-Prolific's prescreening features were used to ensure that participants who had already participated in one experiment (regardless of whether it was a rating or guessing task) could not participate in any subsequent experiments.
-Excluding the practice and control items (which every participant guessed and rated), in the final dataset we had a median of 40 guesses per word (range: 15-129) in the pilot guessing experiment; a median of 30 guesses (range: 29-60) per word for the second guessing experiment; and a median of 15 ratings (range: 14-58) per word for the rating task (@motamedi_iconicity_2019 suggest a benchmark of 10 ratings per word is sufficient).
-
-```{r final data count}
-ratings%>%
-  select(identifier,prolificID)%>%
-  unique()%>%
-  group_by(identifier)%>%
-  count()%>%
-  filter(n<200)->no_ratings
-
-#median(no_ratings$n)
-
-guesses_words%>%
-  select(identifier,prolificID)%>%
-  unique()%>%
-  group_by(identifier)%>%
-  count()%>%
-  filter(n<200)->guess1
-
-# median(guess1$n)
-
-guesses_trans%>%
-  mutate(identifier=paste(word,concept))%>%
-  select(identifier,Prolific.ID)%>%
-  unique()%>%
-  group_by(identifier)%>%
-  count()%>%
-  filter(n<200)->guess2
-
-#median(guess2$n)  
-```
-
-## Pilot guessing experiments: guessing between translations
-
-We piloted some guessing experiments following previous studies [e.g.
-@dingemanse_what_2016], in which participants were presented with a Japanese word and asked to guess its meaning from a choice of two possible translations.
-Some of the ideophones in the data had very specific meanings, which were difficult to capture in a single English word.
-To provide more context, the translations were given in sentence frames, with the translation word in capitals.
-The instructions were as follows:
-
-> We are interested in how well people can guess the meanings of words in foreign languages. In this experiment, we are interested in your intuitions about the meanings of JAPANESE words.
-You will hear 25 Japanese words.
-After listening to each word, try to guess its meaning from a choice of two possible English translations.
-For context, meanings are given in a sentence, with the intended meaning in CAPITALS.
-For example, if you think the word could mean BRIGHT in the sentence 'The sun is BRIGHT', choose that sentence.
-If you think it could mean ROUND in the sentence, 'The sun is ROUND', choose that sentence.
-Trust your gut, and good luck!
-
-A sample trial is shown in Figure \@ref(fig:guessingtrans).
-
-```{r guessingtrans, fig.cap="Guessing task - guessing between translations",echo=FALSE}
-knitr::include_graphics("images/guessingtransdemo.PNG")
-```
-
-The same formulaic structure, "After X, Y", was used for all the sentences--where Y is the target perception and X is the event that causes it.
-As some sensory modalities (e.g.
-sound) may better lend themselves to the construal of iconicity than others (e.g.
-taste), correct translations were always paired with foil translations from the same modality (e.g.
-sound translations were only paired with other sound translations, and taste translations with other taste translations, etc.).
-To make the difficulty of the task comparable between different trials, only words that were neither synonyms nor antonyms of the correct translation were chosen as foils.
-Finally, the length of the sentences was also kept consistent (to a difference of no more than 5 characters) between pairings of translations and foils.
-To test the robustness of the guessing procedure to different choices of translation and foil words, the same words were tested multiple times with different translations and foils.
-We were concerned that participants could choose particular translations because of how they sound (particularly if they sounded similar to the Japanese word), rather than based on their meanings as we intended.
-So, to minimise any potential effects from this, as much as possible phonologically distinct synonyms were chosen as alternative translations (e.g.
-SMALL|TINY, BIG|LARGE).
-
-Pilot results showed that in several cases the guessability of a word did differ considerably depending on the translation or foil word used. Some examples are shown in Table \@ref(tab:weirdcases).
-
-```{r weirdcases,echo=FALSE}
-guesses_trans%>%
-  mutate(word_spec=paste(word,concept,sep="_"))->guesses_trans
-
-guesses_trans%>%
-  filter(word_spec=="piiN_LONG"|word_spec=="hakkiri_CLEAR-HEADED")%>%
-  filter(!(grepl("SHARP",answer_sen)))%>%
-  select(answer_sen,foil_sen,answer)%>%
-  group_by(answer_sen,foil_sen)%>%
-  count(answer)%>%
-  pivot_wider(names_from=answer,values_from=n, values_fill=0)%>%
-  knitr::kable(col.names = c("Answer sentence", "Foil sentence","correct","incorrect"),caption="Effect of different foils and translations on guessing results for hakkiri 'CLEAR HEADED' and piiN 'LONG'")%>%
-  kable_styling()
-
-```
-
-We hypothesised that, as well as considering the meaning of the translations and foils, participants may be driven to one option over another because of the way the words sound (particularly if they sounded similar to the Japanese word being tested), or because of lexical features of the words like frequency, valence, arousal, or any other associations they may have with these words.
-
-While we could not do anything about the sound of the words (other than using multiple translations), we realised that we could eliminate at least some of the complications caused by other properties of the words if we flipped the design of the guessing experiments on its head, so that instead of choosing the correct English meaning for a given Japanese word, participants chose the correct Japanese word for a given English meaning.
-In this way, there was only one English word involved in the task, and the options participants chose between were simply two Japanese words which they knew nothing about, other than how they sound.
-This design was also more comparable to the rating task--where participants are also given the meaning of the word first.
-We therefore decided to use this new design for the rest of the guessing experiments.
-
-## Guessing experiments: guessing between words {#goodguesses}
-
-For the new version of the guessing experiments, we minimised the amount of English words involved in the task by having participants match a single English translation to the corresponding word in Japanese, choosing between two possible Japanese words.
-The instructions used were as follows:
-
-> We are interested in how well people can guess words in foreign languages.
-In this experiment, you will be asked to match the English translation with the corresponding word in JAPANESE, guessing from a choice of two Japanese words.
-
-A sample trial is shown in Figure \@ref(fig:guessingwords).
-
-```{r guessingwords, fig.cap="Guessing task - guessing between words",echo=FALSE}
-knitr::include_graphics("images/guessingwords.PNG")
-```
-
-This time, instead of using sentence frames for context, we kept the amount of English to a minimum by using only single-word translations where possible, and where more context was needed this was provided in brackets, as in Figure \@ref(fig:guessingwordsspec).
-
-```{r guessingwordsspec, fig.cap="Guessing task - guessing between words",echo=FALSE}
-knitr::include_graphics("images/guessingwordsspec.PNG")
-```
-
-The incorrect 'foil' word in each item was a nonsense Japanese word artificially generated to be as phonologically distinct as possible from the correct word, while still conforming to Japanese phonology.
-For every word, three different foil words were generated by substituting each consonant with its top three most phonologically distant consonants in the Japanese sound system.
-Phonological distances were calculated using the feature matrix provided in PHOIBLE [@phoible], with the distance between two sounds being equal to the sum of the distances between each of their feature values.
-Distances were calculated as follows:
-
-> The distance between two feature values that are identical is 0.
-The distance between two opposing values (+/- or -/+) is 1—except if the feature involved is length or voicing, then the distance is 0.5, The distance between two feature values when one of them is 0 (= not applicable) is 0.25.
-
-Since /a/ is often the most phonologically distant vowel from many of the vowels in the Japanese sound system, to avoid the foil words all having similar vowels, a different approach was used for substituting vowels.
-Instead of using feature values, vowels were substituted with the vowel obtained by rotating the vowel space 180 clockwise or counterclockwise.
-So /u/ is substituted with either /a/ or /i/, and /a/ is substituted with either /i/ or /u/ (see Figure \@ref(fig:vowels)).
-Finally, reduplicated words were ‘unreduplicated’ when creating foil words.
-For example, the foils for *fuwafuwa* were *watʃi*, *nati* and *ridːu* (not *watʃiwatʃi*, *natinati* and *ridːuridːu*).
-
-```{r vowels,fig.cap="Vowel substitutions for the creation of foil words",echo=FALSE}
-knitr::include_graphics("images/vowels.PNG")
-```
-
-By using foil words that sound as different as possible to the target word, we hoped to improve the sensitivity of the measure to any iconicity in the target word.
-Our logic was that if the target word *is* iconic for a concept, then a word that sounds very different to it should be a bad fit for that same concept--making the choice between the two easier.
-To test whether this was really the case, we ran one of the experiments a second time using foils that were randomly chosen from among the other trial items in the experiment, rather than phonologically distinct foils.
-
-## Rating task {#ratings}
-
-We also conducted an iconicity rating task with the same words.
-In the rating task, the concept of iconicity was defined to participants as "when a word and its meaning resemble one another", using the English examples *wiggle*, *jiggle*, and *wriggle*.
-The instructions stated that "Even people who do not speak any English can get a sense of the meaning of these words", and contrasted them with words like *walk* and *run* whose meanings are "not so intuitive".
-The full instructions given were as follows:
-
-> Some words seem to 'fit' their meanings. For example, consider the English words wiggle, jiggle, and wriggle.  
-We have an intuitive sense of the meanings of these words, because there is a resemblance between the words and their meanings.  
-Even people who do not speak any English can get a sense of the meaning of these words.  
-Words like walk and run on the other hand are not so intuitive; people who do not know any English would not be able to guess what these words mean.  
-In this task, you will listen to some Japanese words, and we will tell you their meanings. You will then be asked to judge whether there is a resemblance between the word and its meaning.
-
-Participants had to listen to the Japanese words and were told their meanings, then asked to rate the resemblance between the word and its meaning on a scale from 0 'No resemblance' to 6 'Strong resemblance' (see Figure \@ref(fig:ratingdemo)).
-Previous studies [@perry_iconicity_2015] also used a negative end of the scale (corresponding to a 'bad resemblance').
-However, follow-up analyses found that the negative end of the scale was both underused and inconsistently used, suggesting that anti-iconic relationships are difficult to assess [@motamedi_iconicity_2019].
-For this reason, we decided to only use a positive scale in this study.
-
-```{r ratingdemo, fig.cap="Rating task",echo=FALSE}
-knitr::include_graphics("images/ratingdemo.PNG")
-```
-
-As with the guessing experiments, the translation shown for each participant was varied randomly between a set of (wherever possible) phonologically distinct synonyms.
-
-## Creation of Icotools
-
-To make the collection of guesses and ratings quicker and easier for future studies, while also improving comparability between studies, we created a python package, `icotools` [(https://pypi.org/project/icotools/)](https://pypi.org/project/icotools/), with functions that can be used to automatically generate rating and guessing experiments (using the meaning-to-word design from the second guessing experiments).
-The package has three functions: a rater function, a guesser function, and a foiler function.
-The rater and guesser functions create rating and guessing experiments as described in Sections \@ref(goodguesses) and \@ref(ratings).
-They take two csv files as input.
-The first is a wordlist containing the items in the experiment (including trials, practice items, control items, and sets of translations to use for them), while the second file is used for customisation (e.g.
-to specify how many items to include in each experiment, the location of media files, custom instructions and custom exit questions, etc.).
-
-For each experiment, the functions produce three files--a html file, a php file, and a csv file.
-These files can then be uploaded to a server, the link to the html files can be shared with participants, and as the participants complete the experiments their responses will be written to the csv file by the php file.
-The functions also produce a summary csv file with all the details of the experiments (i.e.
-the trials in each experiment, as well as the translations and, where applicable, foils used).
-An R script is provided to collate the responses for all experiments into one long tidy dataset after data collection is complete.
-
-The foiler function can be used to generate a list of opposite sounding foil words for each item in a guessing experiment, following the method described in Section \@ref(goodguesses).
-It is also possible to specify your own foil words, or to choose the foils randomly from among the other items in the experiment.
-For a full description of how to use icotools, please see the ReadMe at https://anonymous.4open.science/r/IcoTools-2CEA/README.md (this is an anonymised link to the github repository: it will later be replaced with the correct link).
-
-# Results
-
-Statistical analyses were conducted using `r R.Version()$version.string`.
-
-## Robustness to different choices of translations and foils
-
-We first investigated whether ratings and guesses were robust to different choices of translations (for ratings and guesses) and foils (for guesses only).
-For each word separately, we performed Fisher's Exact Tests on the guessing data, and ANOVAs on the rating data, to determine whether the guessing performance or ratings given differed significantly between different translations and foils.
-As the ANOVAs are less robust to small amounts of data than the Fisher's Exact Tests, for the rating data we excluded translations with fewer than 10 ratings from this particular analysis.
-
-```{r test robustness guessing experiments}
-# for guessing between translations
-words<-unique(guesses_trans$word_spec)
-
-# see whether the responses differed significantly depending on the answer sentence given
-n=0
-doubly_tested_words <- c()
-weird_words<-c()
-for(w in words){
-  d<-subset(guesses_trans,word_spec==w)
-  t<-table(d$answer_sen,d$answer)
-  # not all words were tested with more than one translation as for some concepts there was only one English word for the concept
-  if (nrow(t)>1){
-    doubly_tested_words <- c(doubly_tested_words,w)
-    n=n+1
-    p_val<-fisher.test(t)$p
-    if (p_val<0.05){
-      weird_words<-c(weird_words,w)}
-}
-}
-
-# see whether the responses different signficantly depending on the foil sentence given
-for(w in words){
-  d<-subset(guesses_trans,word_spec==w)
-  t<-table(d$foil_sen,d$answer)
-  if (nrow(t)>1){
-    doubly_tested_words <- c(doubly_tested_words,w)
-    n=n+1
-    p_val<-fisher.test(t)$p
-    if (p_val<0.05){
-      weird_words<-c(weird_words,w)}
-}
-}
-
-weird_res_trans <- length(unique(weird_words))/length(unique(doubly_tested_words))
-
-# for guessing between words
-
-words<-unique(guesses_words$identifier)
-
-# see whether the responses differed significantly depending on the answer sentence given
-n=0
-doubly_tested_words <- c()
-weird_words<-c()
-for(w in words){
-  d<-subset(guesses_words,identifier==w)
-  t<-table(d$trans,d$answer)
-  if (nrow(t)>1&ncol(t)>1){
-    doubly_tested_words <- c(doubly_tested_words,w)
-    n=n+1
-    p_val<-fisher.test(t)$p
-    if (p_val<0.05){
-      weird_words<-c(weird_words,w)}
-}
-}
-
-# see whether the responses different signficantly depending on the foil sentence given
-for(w in words){
-  d<-subset(guesses_words,identifier==w)
-  t<-table(d$foil,d$answer)
-  if (nrow(t)>1 & ncol(t)>1){
-    doubly_tested_words <- c(doubly_tested_words,w)
-    n=n+1
-    p_val<-fisher.test(t)$p
-    if (p_val<0.05){
-      weird_words<-c(weird_words,w)}
-}
-}
-
-weird_res_words <- length(unique(weird_words))/length(unique(doubly_tested_words))
-```
-
-```{r ratings robustness}
-# for the ratings we are using anovas which are not as robust to small amounts of data as the fisher test
-
-# therefore I only looked at data where we had at least ten ratings per translation
-ratings%>%
-  select(identifier,trans,rating)%>%
-  group_by(identifier)%>%
-  add_count(trans)%>%
-  filter(n>=10)->data
-
-# then within this, we need to get the data where we have at least two translations per word
-data%>%
-  select(identifier,trans)%>%
-  unique()%>%
-  group_by(identifier)%>%
-  mutate(count=n())%>%
-  arrange(identifier)%>%
-  filter(count>1)%>%
-  pull(identifier) -> test
-
-data <- subset(data,identifier %in% test)
-
-words <- unique(data$identifier)
-weird_res <- c()
-for(w in words){
-  d <- subset(data,identifier==w)
-  n_trans <- length(unique(d$trans))
-
-  if(n_trans==2){
-  t <- t.test(d$rating~d$trans)
-  p <- t$p.value
-  }
-  else{
-    t <- summary(aov(d$rating~d$trans))
-    p <- t[[1]][[5]][1]
-  }
-
-  if(p<0.05){weird_res <- c(weird_res,w)}
-}
-
-weird_res_ratings <- length(weird_res)/length(words)
-```
-
-In the first pilot of the guessing task--where participants were guessing between English translations--11 out of the 45 words tested (=24%) showed significant differences in their guessability when either the translation and/or the foil was changed.
-In the second version of the guessing task--where participants were guessing between Japanese words--39 out of 303 words tested (=13%) showed significant differences in their guessability when either the translation and/or the foil was changed.
-In the rating task, 11 out of 88 words tested (=13%) showed significant differences in their iconicity rating when the translation word was changed.
-
-## Sensitivity and discriminability
-
-To test whether using phonologically distinct foils in the guessing experiments improved their sensitivity to iconicity, a subset of 30 words were tested twice--once with phonologically distinct "opposite" foils, and once with random foils.
-
-The number of these words which were guessed significantly above chance (with a sample of 30 guesses per word, an accuracy greater than 2/3 is needed to be sure the true accuracy is above 0.5) was higher in the experiment with opposite foils than in the experiment with random foils.
-Using opposite foils, half of the words in the sample (15/30) were guessed significantly above chance, whereas with the random foils this number fell to just 1 in 5 words (6/30).
-Only two words were guessed significantly above chance in the random foil condition, but not in the opposite foil condition.
-However, both were guessed numerically above chance in the opposite foil condition as well (with accuracies of 52% and 57%).
-The differences between the two conditions are shown in Figure \@ref(fig:sensitivitycheck).
-A chi-squared test confirmed the differences to be significant (χ2(1)=4.69,p=.03).
-
-```{r sensitivitycheck,fig.cap="Words guessed significantly above chance using opposite versus random foils"}
-
-# we used this binomial test to figure out how many correct guesses (out of 30) were needed to have a result significantly different from chance--it's 21
-#binom.test(21,30,p=.5)
-randomfoils <- read_csv("responses-randomfoils.csv")
-
-randomfoils%>%
-  group_by(identifier)%>%
-  mutate(score=sum(result=="correct")/sum(result=="correct"|result=="incorrect"))%>%
-  select(form,score)%>%unique()->randomres
-
-# fix up some naming differences
-words <- randomres$identifier
-words <- replace(words,words=="zoNzoN_SHIVERING","zoNzoN_(SPINE) TINGLING")
-words <- replace(words,words=="geNki_LIVELY","geNki_LIVELY (ENERGETIC)")
-
-guesses_words%>%
-  filter(identifier %in% words|form=="zyiNzyiN")%>%
-  group_by(identifier)%>%
-  mutate(score=sum(answer=="correct")/sum(answer=="correct"|answer=="incorrect"))%>%
-  ungroup()%>%
-  select(form,score)%>%unique()->oppres
-
-comparison <- left_join(randomres%>%select(-identifier),oppres,by="form")%>%
-  rename(random_foils=score.x,opp_foils=score.y)%>%unique()
-
-comparison%>%
-  rename(`random foils`=random_foils,`opposite foils`=opp_foils)%>%
-  pivot_longer(c("random foils","opposite foils"),names_to="design",values_to="accuracy")%>%
-  mutate(`guessing accuracy`=ifelse(accuracy>2/3,"significantly above chance","at chance"))%>%
-  ungroup()%>%
-  select(design,`guessing accuracy`)%>%
-  group_by(design)%>%
-  count(`guessing accuracy`)%>%
-  ggplot(aes(x=design,y=n,fill=`guessing accuracy`))+geom_col()+theme_classic()+labs(x="Design",y="Number of words")+scale_fill_manual(values=c("#CCCCCC","#000000"))
-```
-
-```{r chi square}
-comparison%>%
-  rename(`random foils`=random_foils,`opposite foils`=opp_foils)%>%
-  pivot_longer(c("random foils","opposite foils"),names_to="design",values_to="accuracy")%>%
-  mutate(`above chance`=ifelse(accuracy>2/3,"y","n"))->comparison
-
-#table(comparison$design,comparison$`above chance`)
-#chisq.test(table(comparison$design,comparison$`above chance`))
-```
-
-We also compared the distributions of guessing accuracies and mean iconicity ratings between the different methods.
-Since the iconicity ratings in this study were collected from naive participants who did not speak any Japanese, whereas rating studies more commonly use native speaker participants, I added one more plot to the figure showing the distribution of iconicity ratings in a separate study by Thompson et al.
-[-@thompson_iconicity_2020].
-Thompson et al.
-collected iconicity ratings for Japanese words from native Japanese speaking participants.
-Their dataset contained a wider variety of words than the current dataset, and they also used a different scale.
-Their scale went from -5 'antiiconic' to 5 'iconic', with 0 being labelled as 'arbitrary'.
-The scale in this study started at 0 (also labelled as 'arbitrary', or "no resemblance between the word and its meaning"), and went up to 6 for "strong resemblance between the word and meaning".
-To make the data more comparable between the two studies, and because previous studies have found the negative ratings unreliable [@motamedi_iconicity_2019], I have filtered the data from Thompson et al.
-to only contain responses using the part of the scale between 0 and 5.
-I have also filtered the words to only contain verbs, adverbs, and adjectives from the Yamato stratum.
-The Yamato stratum refers to the native lexicon of Japanese.
-Thompson et al.'s study included both words from the Yamato stratum, as well as Sino-Japanese and foreign words.
-This study only included Yamato words, mainly verbs, adverbs and adjectives.
-Both the data in this study and in Thompson et al.
-2020 contains a mix of ideophones and non-ideophones within the Yamato stratum.
-Finally, ratings from both studies were transformed so that they varied between 0 and 1, to match with the guessing accuracies.
-The resulting distributions are shown in Figure \@ref(fig:discriminability)
-
-```{r discriminability,fig.cap="Discriminability of different measures"}
-guesses_words%>%
-  group_by(identifier)%>%
-  mutate(score=sum(answer=="correct")/sum(answer=="correct"|answer=="incorrect"))%>%
-  select(identifier,score)%>%
-  unique()%>%
-  mutate(method="guesses between words")->oppres
-
-guesses_trans%>%
-  group_by(word_spec)%>%
-  mutate(score=sum(answer=="correct")/sum(answer=="correct"|answer=="incorrect"))%>%
-  select(identifier=word_spec,score)%>%
-  unique()%>%
-  mutate(method="guesses between translations")->transres
-
-ratings%>%
-  group_by(identifier)%>%
-  mutate(mean_rating=mean(rating))%>%
-  mutate(norm_rating=mean_rating/6)%>%
-  select(identifier,score=norm_rating)%>%
-  unique()%>%
-  mutate(method="iconicity ratings")->ratingres
-
-# also compare with ratings from native speakers
-
-japratings <- read_csv("https://osf.io/2praq/download")
-
-japratings%>%
-  filter(stratum=="Yamato"|stratum=="Ideophonic")%>%
-  filter(category=="verb"|category=="adverb"|category=="adjective"|category=="ideophone")%>%
-  filter(rating>=0)%>%
-  group_by(wordCode)%>%
-  mutate(iconicityM=mean(rating))%>%
-  ungroup()%>%
-  mutate(task="Thompson et al. 2020")%>%
-  mutate(ideophone=ifelse(category=="ideophone","y","n"))%>%
-  select(wordCode,iconicityM,rating,task,ideophone)->thompson
-
-thompson%>%
-  select(-rating,-ideophone)%>%
-  unique()%>%
-  mutate(score=iconicityM/5)%>%
-  mutate(method="native iconicity ratings\n(Thompson et al. 2020)")%>%
-  select(identifier=wordCode,score,method)->japres
-
-everything <- rbind(oppres,transres,ratingres,japres)
-#everything$method <- as.factor(everything$method)
-#levels(everything$method) <- c("guessing between words (n=131)","guessing between translations (n=77)","iconicity ratings (n=118)")
-
-everything%>%
-  ggplot(aes(x=method,y=score))+geom_violin()+theme_classic()+labs(x="Method",y="Guessing accuracy / Iconicity rating")+scale_x_discrete(limits=c("guesses between translations","guesses between words","iconicity ratings","native iconicity ratings\n(Thompson et al.
-2020)"))+theme(axis.text.x = element_text(angle=15,vjust=0.6))+scale_y_continuous(breaks=c(0,1))
-```
-
-Focusing first on the data from the current study, we can see that a greater spread of measures is provided by the guesses compared to the ratings, and that within the guesses, the method of guessing between words provides a better spread of measures than guessing between translations--both at the very high end of the scale (highly guessable words) and at the very low end of the scale (poorly guessable words).
-However, if we look at the ratings from native Japanese speakers, these have a pretty equivalent spread to the guesses between words.
-Their distribution is slightly narrower at the very top end of the scale.
-However, the data from the current study was chosen from a domain known to be high in iconicity, whereas the data from Thompson et al.
-was more varied, with proportionally less ideophones.
-Thus, this could simply be a reflection of the differences between the two datasets rather than relating to the methods used.
-
-## Agreement
-
-Figure \@ref(fig:comparison) compares the guessing accuracies and mean iconicity ratings, for both ideophones and non-ideophones.
-The words in the pilot study where participants were guessing between translations were different to the words in the subsequent guessing and rating studies, so here only the results from the later guessing study (where participants guessed between words) are shown.
-At the top end of the scale, the two measures agree--ideophones score higher than non-ideophones for both measures.
-However, at the bottom of the scale something strange happens.
-While for the ratings, the bottom of the scale is dominated by non-ideophones (as expected), for the guesses, the bottom of the scale is actually dominated by *ideophones*.
-That is, ideophones are simultaneously guessed *better* and *worse* than non-ideophones.
-We will return to this in the discussion.
-
-```{r comparison,fig.cap="Comparison of guesses and ratings, for ideophones and non-ideophones"}
-# get info on ideophones
-words <- read_csv("ideophone_list.csv")
-words%>%
-  select(form,ideophone)->info
-
-# combine data
-comparison <- rbind(oppres,ratingres)
-
-comparison%>%
-  mutate(method=str_replace(method,"guess.*","guesses"))%>%
-  mutate(method=str_replace(method,".* ratings.*","ratings"))%>%
-  group_by(method)%>%
-  mutate(z_score=(score-mean(score))/sd(score))%>%
-  # only look at words where you have both ratings and guesses
-  filter(identifier %in% intersect(oppres$identifier,ratingres$identifier))%>%
-  rowwise()%>%
-  mutate(form=str_split(identifier,"_")[[1]][1])%>%
-  left_join(info)%>%
-  unique()%>%
-  select(identifier,ideophone,method,z_score,score)->comparison_dat
-
-comparison_dat%>%
-  filter(method=="ratings")%>%
-  mutate(mean_rating=6*score)%>%
-  mutate(word_type=ifelse(ideophone=="y","ideophones","non-ideophones"))%>%
-  ggplot(aes(x=word_type,y=mean_rating))+geom_violin()+theme_classic()+ylim(0,6)+labs(x="Word type",y="Mean rating")->plot1
-
-comparison_dat%>%
-  filter(method=="guesses")%>%
-    mutate(word_type=ifelse(ideophone=="y","ideophones","non-ideophones"))%>%
-    ggplot(aes(x=word_type,y=score))+geom_violin()+theme_classic()+ylim(0,1)+labs(x="Word type",y="Guessing accuracy")->plot2
-
-#comparison_dat%>%
- # filter(method=="guesses between translations")%>%
-#  filter(score>1/3)%>%
-  #  ggplot(aes(x=ideophone,y=score))+geom_violin()+theme_classic()+ylim(0,1)->plot3
-grid.arrange(plot1,plot2,ncol=2)
-```
-
-Setting aside the strange distribution of guesses for the ideophones, it's notable that both measures suggest that the sensory lexicon of Japanese is for the most part *iconic*, rather than arbitrary.
-In the guesses, this translates to the majority of the words being guessed slightly *above*, rather than at or below chance.
-In the ratings, this translates to the words receiving mean ratings higher than zero (the arbitrary point on the scale)--though some of these 'iconic' ratings are likely an overstatement, since all of the words received positive iconicity ratings and yet from the guessing results we can see that many of these were not guessed any differently to chance.
-
-To test how well the measures agree on the iconicity of individual words, iconicity ratings and guessability scores for the same words were transformed to z-scores so that they could be directly compared.
-Figure \@ref(fig:agreement) plots matching z-scores for the guesses and ratings against eachother, to show the agreement between the two measures.
-In the figure, ideophones are represented by blue dots, and non-ideophones by red dots.
-
-```{r agreement,fig.cap="Agreement between guesses and ratings"}
-comparison_dat%>%
-  select(-score)%>%
-  pivot_wider(names_from = "method",values_from="z_score")->comparison_dat
-comparison_dat%>%
-  ggplot(aes(x=guesses,y=ratings,colour=ideophone,label=identifier))+geom_point()+theme_classic()+geom_smooth(method="lm")->plot
-
-plot
-# If you want to see which words are which dots -- ggplotly will let you hover over them
-#ggplotly(plot)
-```
-
-For both ideophones and non-ideophones, there was a strong correlation between the ratings and the guesses.
-This correspondence was slightly better for the ideophones (r = 0.66, 95% CI [0.44, 0.79], 95% CI [0.53, 0.76], t(99) = 8.68, p < .001) than for the non-ideophones (r = 0.41, 95% CI [0.29, 0.52], t(201) = 6.45, p < .001).
-To explore this relationship further, we created two linear regression models: one predicting guesses from ratings, ideophone status, and the interaction between these two factors, and a second model predicting ratings from guesses, ideophone status, and the interaction between these two factors.
-Both models again used the z-scores rather than the raw ratings and guesses.
-The models were created using the R package `lmerTest` (version `r packageVersion("lmerTest")`) [@lmertest].
-
-The output of the first model (predicting guesses from ratings) is shown in Table \@ref(tab:guessesmodel).
-
-<caption> (\#tab:guessesmodel) Linear regression model predicting guesses from ratings, ideophone status, and the interaction between these two factors. </caption>
-```{r correlations and first regression}
-ids <- comparison_dat%>%filter(ideophone=='y')
-#report(cor.test(ids$guesses,ids$ratings))
-
-prosaic <- comparison_dat%>%filter(ideophone=='n')
-#report(cor.test(prosaic$guesses,prosaic$ratings))
-
-m1 <- lm(data=comparison_dat,guesses~ratings*ideophone)
-#summary(m1)
-
-tab_model(m1,show.ci = FALSE,show.se = TRUE,show.stat = TRUE, dv.labels = c("Guesses"),  CSS = list(
-    css.table = 'width: 90%;'
-  ))
-
-```
-
-The model confirmed that ratings significantly predict guesses, with higher ratings leading to higher guesses.
-There was also a main effect of ideophone, and an interaction effect between ideophone and rating.
-The model is easiest to interpret by plotting the interaction, shown in Figure \@ref(fig:interaction).
-
-```{r interaction,fig.cap="Interaction between ratings and ideophone when predicting guesses"}
-ggpredict(m1,c("ratings","ideophone"))%>%plot()
-```
-
-The plot shows that higher ratings lead to better guessing accuracy for both ideophones and non-ideophones.
-The interaction effect appears because in the case of words with *low* iconicity ratings, guessing accuracy for ideophones is relatively poorer than for non-ideophones.
-At the top of the scale, highly rated ideophones also appear to be guessed slightly better than non-ideophones with comparable ratings.
-However, the difference here does not appear to be significant as the confidence intervals for the two lines overlap.
-We will return to this in the discussion.
-
-For comparison, we also created a second model predicting ratings from guesses, shown in Table \@ref(tab:ratingsmodel).
-
-<caption> (\#tab:ratingsmodel) Linear regression model predicting ratings from guesses, ideophone status, and the interaction between these two factors. </caption>
-```{r ratingsmodel,fig.cap="Model predicting guesses from ratings and ideophone status"}
-m3 <- lm(data=comparison_dat,ratings~guesses*ideophone)
-
-tab_model(m3,show.ci = FALSE,show.se = TRUE,show.stat = TRUE, dv.labels = c("Ratings"),  CSS = list(
-    css.table = 'width: 90%;'
-  ))
-```
-
-The model shows that guesses significantly predict ratings, as does ideophone status, but that there was no interaction between these two predictors.
-This is shown in Figure \@ref(fig:ratingsinteraction).
-The lines for ideophones and non-ideophones are parallel, indicating that differences in guesses correspond to differences in ratings *in the same way* for both ideophones and non-ideophones.
-However, the line for the ideophones is directly *above* the line for the non-ideophones, indicating that ideophones are rated higher in iconicity than non-ideophones--even when guessed at the same accuracies.
-
-```{r ratingsinteraction,fig.cap="Relationship between ideophone status, guessability, and predicted rating"}
-ggpredict(m3,c("guesses","ideophone"))%>%plot()
-```
-
-Finally, the lower correlation between guesses and ratings obtained for non-ideophones compared to ideophones suggests that participants may not have been as consistent or reliable when rating non-ideophones compared to when rating ideophones.
-To further investigate this, we calculated the person-total correlation for the rating data [@curran_methods_2016; @motamedi_iconicity_2019], for ideophones and non-ideophones separately.
-Figure \@ref(fig:ratingconsistency) shows the agreement between raters (expressed as the correlation between each individual rating, and the by-item average) for ideophones and non-ideophones respectively.
-The dots indicate the mean while the lines indicate 95% confidence intervals.
-Again, since these ratings were from non-Japanese speaking participants, I have also added data from native Japanese speaking participants from Thompson et al.
-(2020) as a comparison.
-
-```{r bootstrap function,cache=TRUE,eval=FALSE}
-# my ratings from English people
-ratings%>%
-  group_by(identifier)%>%
-  mutate(mean_rating=mean(rating))%>%
-  select(iconicityM=mean_rating,rating,prolificID)%>%
-  mutate(task="current study")%>%
-  mutate(form=str_split(identifier,"_")[[1]][1])%>%
-  left_join(info,by="form")%>%
-  ungroup()%>%
-  unique()%>%
-  select(-form,-identifier,-prolificID)->ratingdat
-
-# Thompson's ratings from Japanese people
-
-thompson%>%
-  select(iconicityM,rating,task,ideophone)->thompson
-
-datasets <- list(ratingdat,thompson)
-
-# code from Motamedi et al. 2019
-
-R <- 5000
-
-# Bootstrap function, calculating the correlation coefficient for each bootstrapped sample
-bootCor <- function(data, i){
-  d <- data[i,]
-  rDf <- correlate(d %>% select(-task))
-  return(rDf[[2,2]])
-}
-
-# Split the data by halves of the rating scale, apply the above bootstrap function, and extract confidence intervals
-corRatings <- function(data){
-
-  # Separate the data into ideophones and non-ideophones
-   negData <- data %>% filter(ideophone=="n")%>%select(-ideophone)
-   posData <- data %>% filter(ideophone=="y")%>%select(-ideophone)
-
-  #negData <- data %>% filter(rating<0)
-  #posData <- data %>% filter(rating>0)
-
-  # Bootstrap the correlation between each negative rating, and the by-item average
-  negBoot <- boot(negData, bootCor, R=R)
-  negCI <- boot.ci(negBoot, type="bca")
-  rNeg <- negBoot$t0
-  lowerNeg <- negCI$bca[[4]]
-  upperNeg <- negCI$bca[[5]]
-
-  # Bootstrap the correlation between each positive rating, and the by-item average
-  posBoot <- boot(posData, bootCor, R=R)
-  rPos <- posBoot$t0
-  posCI <- boot.ci(posBoot, type="bca")
-  lowerPos <- posCI$bca[[4]]
-  upperPos <- posCI$bca[[5]]
-
-  return(list(list(lowerPos,upperPos,rPos), list(lowerNeg,upperNeg,rNeg)))
-}
-```
-
-```{r run bootstrap, cache=TRUE, message=FALSE, warning=FALSE,eval=FALSE}
-
-# Initialize an empty dataframe to store values
-cis <- data.frame(name=character(), sign=character(), r=numeric(), lower=numeric(), upper=numeric(), stringsAsFactors=FALSE)
-
-# Iterate over datasets
-for(dataset in datasets) {
-
-  # Track the name of the current dataset
-  name <- dataset$task[1]
-
-  # For each dataset, apply the function corRatings described above
-  c(c(posLower, posUpper, posR), c(negLower, negUpper, negR)) %<-% corRatings(dataset)
-
-  # Append the results to the dataframe
-  cis[nrow(cis) + 1,] = list(name, 'ideophone', posR, posLower, posUpper)
-  cis[nrow(cis) + 1,] = list(name, 'non-ideophone', negR, negLower, negUpper)
-}
-```
-
-```{r make person-total graph,eval=FALSE}
-cis %>% 
-  ggplot(aes(x=name,
-             y=r,
-             ymin=lower,
-             ymax=upper,
-             color=sign)) +
-  geom_point(position=position_dodge(0.1)) +
-  geom_errorbar(position=position_dodge(0.1),
-                width=0.1) + 
-  coord_flip() +ylim(0,0.6)+theme_classic()+labs(y="Correlation (r)",x="")->plot
-plot
-```
-
-```{r ratingconsistency,fig.cap="Consistency between participants for iconicity ratings of ideophones versus non-ideophones",out.width="70%",echo=FALSE}
-knitr::include_graphics("images/bootstrapping.png")
-```
-
-In both studies, participants appear to be more consistent with eachother when rating ideophones than when rating non-ideophones, though for Thompson et al.
-the overlap of the confidence intervals indicates that the difference was not significant.
-There does not appear to be any difference in the consistency of ratings *between* the English and the Japanese speakers, as both the ideophone lines and the non-ideophone lines overlap between the two groups.
-
-# Discussion
-
-## Relationship between ratings, guesses, ideophones, and iconicity {#maindiscussion}
-
-For both ideophones and non-ideophones, we found that the guesses and ratings from non-speakers were strongly correlated in the *same way*.
-This suggests that the two measures are indeed tapping into *something* in common, which we suggest are form-meaning associations.
-It's notable that these associations are found in both ideophones *and* non-ideophones (even if they are more common in the former), and that there are also ideophones that participants had no strong associations with--highlighting that there is no straightforward relationship between ideophones and iconicity; variable levels of iconicity can be found in both ideophones and prosaic words [see also @dingemanse_what_2016; @brown_phonetic_1955; @kunihira_effects_1971].
-
-However, ideophones were consistently rated *higher* in iconicity than non-ideophones—even when guessed at the same accuracies.
-We believe this is due to the majority of ideophones in the dataset being reduplicated.
-The two lowest rated ideophones–*sappari* and *syippori*–were among the few in the data that do not use a reduplicated template.
-Previous work has found a relationship between iconiticity ratings and structural markedness (Dingemanse and Thompson 2020).
-Ordinarily when we use words, the form of the words is not important--only their content.
-However, when iconicity is involved (and also funniness, as this paper found) the form of the words *is* important, and structural markedness may serve as a metacommunicative cue to signal this.
-The authors hypothesise that “Structural markedness confers a selective advantage on words intended to be iconic… as their recognisability would make them more fit to survive processes of cultural transmission in which the recognition of such intentions is functionally important” (Dingemanse and Thompson 2020: 218).
-The results from the rating task in this study suggest that structural markedness (in this case, reduplication) does indeed lead to the perception of iconicity.
-Interestingly, however, it does not seem to confer any advantage--over and above that provided by associations between form and meaning--in the guessing task.
-What the ratings seem to be picking up on is both form-meaning associations *and* structural markedness.
-If they were only picking up on structural markedness, then we would not expect the ratings to vary with the guesses in the same way for both ideophones and non-ideophones.
-However, if they were only picking up on form-meaning associations (like the guesses seem to), then we would not expect ideophones to consistently receive higher iconicity ratings, even when guessed at the same accuracies.
-
-While ideophones and non-ideophones with high iconicity ratings were generally guessed equally well, there was an interaction effect such that ideophones with low iconicity ratings were guessed *worse* than non-ideophones with comparable ratings.
-Low iconicity ratings in non-ideophones generally correspond to chance guessing accuracy--reflecting a lack of associations--whereas equivalent ratings in ideophones correspond to *below chance* guessing accuracy--reflecting *negative associations* masked in the rating results by the tendency to inflate ratings for ideophones.
-The result highlights the subjective nature of form-meaning associations, and that by taking above-chance guessing accuracy as a measure of iconicity we are only picking up on those associations that happen to correspond--and crucially not to conflict--between (in this case) English and Japanese speakers.
-This is something researchers should be aware of, because it means that decisions about *whom* to collect iconicity measurements from are very important.
-
-Poor guessing accuracies could be explained by conflicting associations.
-For example, one person commented that *zarazara* as a word for ‘ROUGH’ sounds wrong to them because they associate the word *zara* with the clothing store ZARA, and clothes are soft.
-These could be masking either a lack of resemblance between form and meaning, or a resemblance between form and meaning that is ignored in the face of the conflicting association.
-Of course, conversely one could argue that high guessing accuracies could then *also* be explained by non-resemblance based associations.
-Fortunately, the chances of English speakers having the *same* form-meaning association as Japanese speakers based on something random (like the name of a clothing store) should be much smaller than the chances of them having a *different* association.
-Thus, if they do exist, we predict that the majority of non-resemblance based associations should be reflected in poorer rather than higher guessing accuracies.
-It is interesting that conflicting associations appear to have a stronger effect in ideophones (some of which were guessed at accuracies significantly below chance) than in non-ideophones (which were guessed below chance only rarely).
-Perhaps because participants are more likely to view form-meaning relationships in ideophones as meaningful (due to their structural markedness), they are more likely to attach conflicting associations to ideophones, leading to a stronger sense that the ideophone should correspond to the *opposite* of the given meaning.
-
-Finally, the comparison between guesses and ratings highlights a bias in the design of the rating task, as all the words in the data were in the end rated as "slightly" iconic (even by non-speakers), whereas the guessing results show that a good number of these were not guessed any better than chance.
-This is probably an artefact of the design of the rating task, in which "arbitrary" is only 1 of the 7 or 10 points on the scale--the rest indicating varying degrees of form-meaning resemblance.
-This is not so problematic, as the ratings still correlate with guessing accuracy, indicating that the relative differences in iconicity still hold.
-However, it highlights that interpretations of particularly *low* iconicity ratings as reflections of iconicity should be viewed with caution.
-
-To sum up, by directly comparing iconicity ratings and guessing accuracies for both ideophones and non-ideophones, we are able to better understand how these measures relate to each other and to iconicity.
-Differences between iconicity ratings of ideophones and non-ideophones--even when guessability is the same--highlight the role of structural markedness in enhancing perceived iconicity.
-Consistencies between guesses and ratings within these word types reassure us that, despite this, form-meaning association biases play a large role in explaining each measure.
-The unexpected result of ideophones also being poorly guessed reminds us that these biases are just that--subjective--and thus, while good guessing accuracies can be interpreted as positive evidence of language-external iconicity, average or poor guessing accuracies *cannot* be interpreted as negative evidence of iconicity of either kind (language-internal or external).
-Similarly, while high ratings are likely to be a good indication of iconicity, researchers should be cautious of taking lower ratings indicating "slight" iconicity at face value.
-
-## Towards a synthesis of measures
-
-Given the limitations of each measure discussed above, for a full picture of iconicity in the lexicon, a synthesis of measures is recommended.
-Iconicity ratings from native speakers can tell us which mappings are meaningful to them, while comparisons with guessability for non-speakers can establish which of these mappings are likely to be meaningful on their own, versus which *become* meaningful through experience with the rest of the lexicon (language-external versus language-internal iconicity).
-@occhino_role_2020 found differential effects of these two types of mappings in sign processing by signers of different proficiencies.
-They found that both types of iconicity were helpful to signers of a lower proficiency, but that for highly proficient signers only the most pervasive, language-external mappings made a difference to processing.
-
-Since structural markedness appears to boost ratings but not guessability, the two measures could also be used together to tease apart the influence of structural markedness versus form-meaning resemblances in driving iconic effects.
-Iconic effects are generally assumed to be driven by form-meaning resemblances, but since these often go together with structural markedness it would be useful to know the relative contribution of each factor in different situations and tasks.
-Since structural markedness is also subjective, the choice of participants used in the rating task will be important.
-Finally, having guesses alongside ratings would allow researchers to make better decisions about the cut-off point between "high" and "low" iconicity ratings, as these could be motivated by correlations with guessing accuracy, rather than e.g.
-arbitrarily dividing the scale at the half-way point, or using percentiles tied to particular datasets.
-
-Guesses and ratings could also be used to inform results from descriptive or data-driven measures, and vice-versa.
-For example, the psychological reality and relative *strength* of form-meaning mappings described in lexicons could be tested using guessing or rating tasks with nonwords [e.g.
-@kwon_empirically_2017].
-Similarly, descriptive (semiotic) analysis, along with cross-linguistic comparisons where possible could be used to understand and explain why some mappings are stronger or more universal than others.
-Conversely, behavioural measures could be used to tease apart some of the possible explanations for cross-linguistic biases.
-The two main contenders for explaining these biases are form-meaning associations or communicative pressures [@blasi_soundmeaning_2016].
-Since communicative pressures are unlikely to play a role in tasks where participants are simply judging or choosing words, behavioural measures could be used to distinguish these two hypotheses, thus allowing us to better understand the mechanisms behind results in these cross-linguistic studies.
-
-## Methodological improvements and evaluation
-
-We also sought to evaluate different rating and guessing paradigms, and were able to make some methodological improvements--particularly to the guessing design.
-We contrasted two different guessing paradigms--one where participants are given a word and have to match it to the correct meaning from two translations, and another where participants are given a meaning and have to match it to the correct word from two words.
-Content-wise, choosing between words is more comparable to the design of a rating task, as both give the meaning first and involve only one English translation.
-This is important as the use of translations leads to several complications in the experiment design.
-First, English-speaking participants can be expected to have more associations with English words than with unknown Japanese words, which could make the task more sensitive to the particular translations chosen.
-In addition, care has to be taken when choosing foils as well, as they should preferably be from the same semantic domain, of a similar length of characters, and not synonyms or antonyms of the correct translation.
-This makes the guessing between translations design more difficult to use, particularly in small semantic domains (e.g.
-taste).
-
-In contrast, a task in which participants guess between words is much easier to operationalise.
-This design can be easily adopted to any semantic domain or any kind of data, and the foils can be chosen either randomly from the other trials or selected based on specific criteria.
-In our case we chose foils that were phonologically as distinct as possible from the word being tested.
-The first reason for this was theoretical: in a task designed to pick up on form-meaning resemblance, words that sound very different should not be suited to that meaning, enhancing the effect of iconicity.
-The second was practical: our stimuli had artificially flat intonations, which has been shown to decrease performance in guessing studies [@kunihira_effects_1971; @dingemanse_what_2016].
-By creating opposite sounding words, we tried to increase performance in the guessing task despite the degraded stimuli.
-
-When comparing results from the two designs, choosing between words is again the more favourable of the two.
-First, as expected changing the translation or foil used led to less inconsistent results when choosing between words compared to when choosing between translations.
-Second, the range of guessing scores is much wider when choosing between words compared to choosing between translations, with more words guessed at high accuracy levels, and fewer words around chance level.
-This is especially true when the foils used are maximally phonologically distinct.
-However, for datasets that are relatively higher in iconicity to begin with--e.g.
-gestures or hand signs--using random foils will likely already produce good results.
-The better results in the choosing between words design can be easily explained, as the task was comparatively easier than in the choosing between translations design, where participants were restricted to choosing between two similar options (non-antonyms from the same semantic domain).
-The options in the choosing between words design are more distinct--even maximally so.
-In sum, the choosing between words design is both more robust, more sensitive to iconicity, and more discriminating between lesser and greater amounts of iconicity, so this is the design that we recommend and that we have implemented in `icotools`.
-
-We also compared our iconicity ratings from non-speakers with iconicity ratings from native speakers in Thompson et al.
-[-@thompson_iconicity_2020].
-We found that, although using non-speakers resulted in a lesser spread of measures (suggesting that native speakers are more confident in giving high and low ratings than non-native speakers), when evaluating the agreement between raters, ratings from non-speakers were just as reliable as ratings from native speakers--as well as being fairly robust to different choices of translation.
-Ratings from non-speakers were more reliable for ideophones than for non-ideophones--but this is not to say that the ratings for non-ideophones were unreliable.
-Rather, the ratings for ideophones were *particularly* reliable, probably because raters were more likely to have stronger intuitions about these words due to their structural markedness, and because they are more likely to be iconic in the first place.
-The same pattern was seen in the ratings from native speakers, although it did not reach statistical significance.
-Since both types of ratings are fairly reliable, our recommendation would be to choose participants for rating tasks according to how the ratings are going to be used.
-For example, to predict language processing in adult native speakers of a language, it would make sense to collect ratings from other adult native speakers of the same language.
-
-## Towards a reproducible workflow
-
-Finally, with `icotools` we introduce a reproducible workflow for conducting rating and guessing experiments.
-This will make it easier for researchers to run these tasks, while enhancing comparability between future studies.
-Researchers can use the same paradigms to confirm current results, ask new questions, and run new analyses that build on existing findings.
-For example, this study has examined iconicity in the sensory vocabulary of Japanese, and found that the majority of words tested were actually guessed slightly above chance.
-With `icotools`, future researchers could run the exact same guessing experiment with different languages and in different semantic domains, to establish whether this is also true in other languages, and in other areas of the lexicon.
-
-# Conclusions
-
-This study has asked how we can make existing measures of iconicity even better, by critically evaluating and comparing two of the most promising behavioural measures of iconicity--iconicity ratings and guessing tasks.
-In comparing the two measures, we were able to get a better sense of the relative strengths and weaknesses of each.
-Our main finding is that the two measures are more informative when used together than when used in isolation.
-In isolation, it is difficult to determine the degree to which high iconicity ratings are driven by form-meaning associations versus structural markedness, and to have an objective sense of which ratings are "low" or "high".
-In isolation, guesses provide only a narrow window into iconicity of a particular kind--strong, language-external associations.
-However, in *combination* ratings and guesses together can provide a picture of iconicity at different levels (both language internal and external), and in different degrees (low and high), while also uncovering how perceptions of iconicity are driven by both form-meaning associations and structural markedness.
-We have also made some methodological improvements to the guessing paradigm, improving on the robustness, sensitivity and discriminability of previous approaches.
-Finally, we introduce a reproducible workflow for creating rating and guessing tasks in the form of the Python package `icotools` (https://pypi.org/project/icotools/), so that future studies will be able to use these measures to build on current findings as well as asking new questions about what iconicity does in language, and how it does it.
-
-# Data Availability Statement
-
-The data from the study, as well as the code used to produce the experiments and analyses can be found on the Open Science Framework, at https://osf.io/j57uc/?view_only=d59ffde4bc42467fafb71a904bef8d14.
-
 # References

### 2022-01-29 paper.Rmd
fixed up discussion

@@
 output:
-  bookdown::html_document2:
-   # reference_docx: wordstyles.docx
+  bookdown::word_document2:
+    reference_docx: wordstyles.docx
     toc: true
@@
     css: custom.css
-    code_folding: hide
+  #  code_folding: hide
 always_allow_html: true
@@
 
-```{r packages, include=FALSE}
+```{r setup, include=FALSE}
 library(tidyverse)
@@
 library(gridExtra)
-knitr::opts_chunk$set(echo = TRUE,warning=FALSE,message = FALSE)
+library(gghalves)
+knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message = FALSE)
 ```
@@
 
-The stimuli were 304 words taken from the *Japonic Sensory Lexicon* database (ANONYMISED CITATION), which is a collection of words for 110 sensory concepts in 49 Japonic varities.
-
-```{r}
+The stimuli were 304 words taken from the *Japonic Sensory Lexicon* database [@McLean_JaponicSensoryLex_2022], which is a collection of words for 110 sensory concepts in 49 Japonic varities.
+The words in the database were collated from three different sources: Sanada and Tomosada [-@sanada_kenbetsu_2015; -@sanada_kenbetsu_2018], and Hirayama [-@hirayama_gendai_1992].
+Any available concepts related to the senses were included.
+For all three sources, words for each concept were collected from speakers of different Japonic varieties by asking the speakers to translate sentences from the standard variety into their local variety.
+Further description of the concepts and the sentences used to elicit them can be found in the Supplementary Materials
+
+The words used in this study come from the Yamato stratum of the Japanese lexicon, meaning that they are native Japanese words.
+The Yamato stratum can be further subdivided into prosaic words and ideophones [or mimetics, see e.g.
+@kageyama_handbook_2016].
+Both types of words are found in the data from Sanada and Tomosada, whereas the data from Hirayama mainly consists of prosaic words.
+Figure \@ref(fig:stimuli) shows the words used in this study, including their semantic domains and membership of different lexical strata.
+A complete wordlist is provided in the Supplementary Materials.
+
+```{r stimuli,fig.cap="Word used in the study, by semantic domain and lexical stratum",echo=FALSE}
 # semantic domains of concepts, plus numbers of ideophones and non-ideophones
@@
 words$domain[words$form == "pyoNpyoN"] <- "action"
-
-```
-
-```{r}
-dat <- read_csv("https://raw.githubusercontent.com/BonnieMcLean/JaponicSensoryLex/main/dat.csv")
-info <- 
-words <- read_csv("responses-guessingwords.csv")%>%
-  select(identifier)%>%
-  mutate(identifier=str_replace_all(identifier,"FUZZY","CLEAR"))%>%
-  unique()
-
-cognates <- read_csv("cognatecodes.csv")%>%
-  mutate(identifier=paste(test_form,eng_trans,sep="_"))%>%select(cognate,identifier)
-
-words <- words%>%left_join(cognates,by="identifier")
-```
-
-The stimuli were 304 words from the Yamato stratum of the Japanese lexicon, in the semantic domain of sensory perception.
-The words were taken from the *Japonic Sensory Lexicon* (ANONYMISED CITATION), a dataset containing words in
-
-from the domain of sensory perception, including both ideophones and prosaic lexical items.
+words$domain[words$form == "zyiNzyiN"] <- "pain"
+words$domain[words$form == "gaNgaN"] <- "pain"
+
+words%>%
+  unique()%>%
+  group_by(domain)%>%
+  count(ideophone)%>%
+  mutate(stratum=ifelse(ideophone=="y","ideophone","prosaic"))->graph
+
+graph$domain <- as.factor(graph$domain)
+
+graph%>%
+  mutate(domain=fct_relevel(domain,c("sound","action","shape & size","appearance","texture","temperature","taste","pain","bodily feeling","emotion")))%>%
+  ggplot(aes(x=domain,y=n,fill=stratum))+geom_col()+theme_minimal()+labs(x="Semantic domain",fill="Lexical stratum")+theme(axis.text.x = element_text(angle=15))+scale_fill_manual(values=c("darkgrey","black"))+ coord_fixed(ratio = 0.1)->plot
+```
+
 For all tasks, the words were presented to participants as audio files.
@@
 
-In all studies, participants were instructed to use headphones throughout the experiment, and could not procede to the experiment without first passing a listening test designed to require the use of headphones @woods_headphone_2017.
+In all studies, participants were instructed to use headphones throughout the experiment, and could not procede to the experiment without first passing a listening test designed to require the use of headphones [@woods_headphone_2017].
 The response buttons in each trial also did not appear until *after* the audio files had finished playing.
@@
 The words were split across 11 different experiments, in such a way that each experiment had a balance of words that were expected to be iconic, versus words that were not expected to be iconic.
+This was so that each participant would only have to rate or guess around 34 words.
 In addition, two 'practice words' and three 'control words' were included in every experiment.
@@
 Strange or lacking task descriptions, particularly when coupled with poor performance on the control items, were used to identify and exclude results from participants who were likely not performing the task as intended.
-
-For the pilot version of the guessing task, in which participants had to match a given form to its correct meaning, data from 3 out of 132 participants was excluded.
-In one case, the participant indicated that they were choosing the translations based on whether they sounded similar to the Japanese word (rather than based on their meaning).
-In the other two cases, the participants did not provide a task description and performed poorly on the control items, so the data was excluded as it was not clear that they were paying attention/understood the task correctly.
-In the new version of the guessing task, in which participants had to match a given meaning to its correct form, data from 3 out of 332 participants was excluded.
-In all three cases, the participants performed poorly on the control items and either did not provide a task description, or their task descriptions were irrelevant (they commented that the task was 'interesting' or 'difficult' instead of describing what they were doing in the task).
+For the rating experiments, we also calculated the person-total correlation for each participant as an additional measure to identify participants whose response patterns differed from those of other participants in the same experiment [following @curran_methods_2016].
+Based on these criteria, data from 11 out of 689 participants was excluded across the different guessing and rating tasks.
+Further information on these exclusions is provided in Section 1 of the Supplementary Materials.
 
@@
 ```
-
-For the rating task, data from 5 out of 225 participants was excluded.
-For the ratings, as well as looking at task descriptions and performance on the control items, we calculated the person-total correlation for each participant @curran_methods_2016.
-The person-total correlation is the correlation between an individual participant's ratings, and the mean ratings from every other participant.
-It provides a measure of how well a participant's responses agree with those of other participants in the task.
-The criteria for exclusion was two or more of either (a) strange or lacking task descriptions, (b) very low ratings for control items, or (c) low person-total correlations (<.2^[We chose .2 as the cut off point because it corresponded with a discontinuity in the lower end of the distribution of person-total correlations, see Figure 1 in the online Supplementary Material]).
-Criteria (a) was used for 4 exclusions.
-In two cases, the participants indicated that they were rating the words according to how much they sounded like their English translations, rather than how well they resembled their meanings.
-Criteria (b) was used in 3 exclusions, and criteria (c) was used in 4 exclusions.
 
@@
 Finally, the length of the sentences was also kept consistent (to a difference of no more than 5 characters) between pairings of translations and foils.
+
 To test the robustness of the guessing procedure to different choices of translation and foil words, the same words were tested multiple times with different translations and foils.
@@
 As with the guessing experiments, the translation shown for each participant was varied randomly between a set of (wherever possible) phonologically distinct synonyms.
-
-## Creation of Icotools
-
-To make the collection of guesses and ratings quicker and easier for future studies, while also improving comparability between studies, we created a python package, `icotools` [(https://pypi.org/project/icotools/)](https://pypi.org/project/icotools/), with functions that can be used to automatically generate rating and guessing experiments (using the meaning-to-word design from the second guessing experiments).
-The package has three functions: a rater function, a guesser function, and a foiler function.
-The rater and guesser functions create rating and guessing experiments as described in Sections \@ref(goodguesses) and \@ref(ratings).
-They take two csv files as input.
-The first is a wordlist containing the items in the experiment (including trials, practice items, control items, and sets of translations to use for them), while the second file is used for customisation (e.g.
-to specify how many items to include in each experiment, the location of media files, custom instructions and custom exit questions, etc.).
-
-For each experiment, the functions produce three files--a html file, a php file, and a csv file.
-These files can then be uploaded to a server, the link to the html files can be shared with participants, and as the participants complete the experiments their responses will be written to the csv file by the php file.
-The functions also produce a summary csv file with all the details of the experiments (i.e.
-the trials in each experiment, as well as the translations and, where applicable, foils used).
-An R script is provided to collate the responses for all experiments into one long tidy dataset after data collection is complete.
-
-The foiler function can be used to generate a list of opposite sounding foil words for each item in a guessing experiment, following the method described in Section \@ref(goodguesses).
-It is also possible to specify your own foil words, or to choose the foils randomly from among the other items in the experiment.
-For a full description of how to use icotools, please see the ReadMe at https://anonymous.4open.science/r/IcoTools-2CEA/README.md (this is an anonymised link to the github repository: it will later be replaced with the correct link).
 
@@
 
-To test whether using phonologically distinct foils in the guessing experiments improved their sensitivity to iconicity, a subset of 30 words were tested twice--once with phonologically distinct "opposite" foils, and once with random foils.
+To test whether using phonologically distinct foils in the guessing experiments improved sensitivity to iconicity, a subset of 30 words were tested twice--once with phonologically distinct "opposite" foils, and once with random foils.
 
@@
 We also compared the distributions of guessing accuracies and mean iconicity ratings between the different methods.
-Since the iconicity ratings in this study were collected from naive participants who did not speak any Japanese, whereas rating studies more commonly use native speaker participants, I added one more plot to the figure showing the distribution of iconicity ratings in a separate study by Thompson et al.
+Since the iconicity ratings in this study were collected from naive participants who did not speak any Japanese, whereas rating studies more commonly use native speaker participants, we added one more plot to the figure showing the distribution of iconicity ratings in a separate study by Thompson et al.
 [-@thompson_iconicity_2020].
@@
 The scale in this study started at 0 (also labelled as 'arbitrary', or "no resemblance between the word and its meaning"), and went up to 6 for "strong resemblance between the word and meaning".
-To make the data more comparable between the two studies, and because previous studies have found the negative ratings unreliable [@motamedi_iconicity_2019], I have filtered the data from Thompson et al.
+To make the data more comparable between the two studies, and because previous studies have found the negative ratings unreliable [@motamedi_iconicity_2019], we have filtered the data from Thompson et al.
 to only contain responses using the part of the scale between 0 and 5.
-I have also filtered the words to only contain verbs, adverbs, and adjectives from the Yamato stratum.
-The Yamato stratum refers to the native lexicon of Japanese.
-Thompson et al.'s study included both words from the Yamato stratum, as well as Sino-Japanese and foreign words.
-This study only included Yamato words, mainly verbs, adverbs and adjectives.
-Both the data in this study and in Thompson et al.
-2020 contains a mix of ideophones and non-ideophones within the Yamato stratum.
+We have also filtered the data to only include native Yamato words (both ideophones and prosaic words), again to increase comparability with the current study.
 Finally, ratings from both studies were transformed so that they varied between 0 and 1, to match with the guessing accuracies.
@@
 everything%>%
-  ggplot(aes(x=method,y=score))+geom_violin()+theme_classic()+labs(x="Method",y="Guessing accuracy / Iconicity rating")+scale_x_discrete(limits=c("guesses between translations","guesses between words","iconicity ratings","native iconicity ratings\n(Thompson et al.
-2020)"))+theme(axis.text.x = element_text(angle=15,vjust=0.6))+scale_y_continuous(breaks=c(0,1))
-```
-
-Focusing first on the data from the current study, we can see that a greater spread of measures is provided by the guesses compared to the ratings, and that within the guesses, the method of guessing between words provides a better spread of measures than guessing between translations--both at the very high end of the scale (highly guessable words) and at the very low end of the scale (poorly guessable words).
-However, if we look at the ratings from native Japanese speakers, these have a pretty equivalent spread to the guesses between words.
+  ggplot(aes(x=method,y=score))+geom_half_violin()+geom_half_point()+theme_classic()+labs(x="Method",y="Guessing accuracy / Iconicity rating")+scale_x_discrete(limits=c("guesses between translations","guesses between words","iconicity ratings","native iconicity ratings\n(Thompson et al.
+2020)"))+theme(axis.text.x = element_text(angle=15,vjust=0.6))+ylim(0,1)
+```
+
+Focusing first on the data from the current study, we can see that the guesses provide a more even spread of measures compared to the ratings.
+Between the two guessing methods, the method of guessing between words provides a wider spread of measures than guessing between translations--both at the very high end of the scale (highly guessable words) and at the very low end of the scale (poorly guessable words).
+If we look at the ratings from native Japanese speakers, these have a pretty equivalent spread to the guesses between words.
 Their distribution is slightly narrower at the very top end of the scale.
@@
 was more varied, with proportionally less ideophones.
-Thus, this could simply be a reflection of the differences between the two datasets rather than relating to the methods used.
+So, this could simply be a reflection of the differences between the two datasets rather than relating to the methods used.
 
@@
 
-Figure \@ref(fig:comparison) compares the guessing accuracies and mean iconicity ratings, for both ideophones and non-ideophones.
+Figure \@ref(fig:comparison) compares the guessing accuracies and mean iconicity ratings, for both ideophones and prosaic words.
 The words in the pilot study where participants were guessing between translations were different to the words in the subsequent guessing and rating studies, so here only the results from the later guessing study (where participants guessed between words) are shown.
-At the top end of the scale, the two measures agree--ideophones score higher than non-ideophones for both measures.
+At the top end of the scale, the two measures agree--ideophones score higher than prosaic words for both measures.
 However, at the bottom of the scale something strange happens.
-While for the ratings, the bottom of the scale is dominated by non-ideophones (as expected), for the guesses, the bottom of the scale is actually dominated by *ideophones*.
-That is, ideophones are simultaneously guessed *better* and *worse* than non-ideophones.
+While for the ratings, the bottom of the scale is dominated by prosaic words (as expected), for the guesses, the bottom of the scale is actually dominated by *ideophones*.
+That is, ideophones are simultaneously guessed *better* and *worse* than prosaic words.
 We will return to this in the discussion.
 
-```{r comparison,fig.cap="Comparison of guesses and ratings, for ideophones and non-ideophones"}
+```{r comparison,fig.cap="Comparison of guesses and ratings, for ideophones and prosaic words"}
 # get info on ideophones
@@
   mutate(mean_rating=6*score)%>%
-  mutate(word_type=ifelse(ideophone=="y","ideophones","non-ideophones"))%>%
-  ggplot(aes(x=word_type,y=mean_rating))+geom_violin()+theme_classic()+ylim(0,6)+labs(x="Word type",y="Mean rating")->plot1
+  mutate(word_type=ifelse(ideophone=="y","ideophone","prosaic"))%>%
+  ggplot(aes(x=word_type,y=mean_rating))+geom_half_violin()+geom_half_point()+theme_classic()+ylim(0,6)+labs(x="Lexical stratum",y="Mean rating")->plot1
 
@@
   filter(method=="guesses")%>%
-    mutate(word_type=ifelse(ideophone=="y","ideophones","non-ideophones"))%>%
-    ggplot(aes(x=word_type,y=score))+geom_violin()+theme_classic()+ylim(0,1)+labs(x="Word type",y="Guessing accuracy")->plot2
+    mutate(word_type=ifelse(ideophone=="y","ideophone","prosaic"))%>%
+    ggplot(aes(x=word_type,y=score))+geom_half_violin()+geom_half_point()+theme_classic()+ylim(0,1)+labs(x="Lexical stratum",y="Guessing accuracy")->plot2
 
@@
 
-Setting aside the strange distribution of guesses for the ideophones, it's notable that both measures suggest that the sensory lexicon of Japanese is for the most part *iconic*, rather than arbitrary.
+Setting aside the question of the distribution of guesses for ideophones, it's notable that both measures suggest that the sensory lexicon of Japanese is for the most part *iconic*, rather than arbitrary.
 In the guesses, this translates to the majority of the words being guessed slightly *above*, rather than at or below chance.
-In the ratings, this translates to the words receiving mean ratings higher than zero (the arbitrary point on the scale)--though some of these 'iconic' ratings are likely an overstatement, since all of the words received positive iconicity ratings and yet from the guessing results we can see that many of these were not guessed any differently to chance.
+In the ratings, this translates to the words receiving mean ratings higher than zero (the arbitrary point on the scale).
+Although, some of these 'iconic' ratings are likely overstated, since all the words received positive iconicity ratings, yet from the guessing results we can see that many of these were not guessed any differently to chance.
 
@@
 Figure \@ref(fig:agreement) plots matching z-scores for the guesses and ratings against eachother, to show the agreement between the two measures.
-In the figure, ideophones are represented by blue dots, and non-ideophones by red dots.
+In the figure, ideophones are represented by blue dots, and prosaic words by red dots.
 
@@
   pivot_wider(names_from = "method",values_from="z_score")->comparison_dat
+
 comparison_dat%>%
-  ggplot(aes(x=guesses,y=ratings,colour=ideophone,label=identifier))+geom_point()+theme_classic()+geom_smooth(method="lm")->plot
+  mutate(word_type=ifelse(ideophone=="y","ideophone","prosaic"))%>%
+  ggplot(aes(x=guesses,y=ratings,colour=word_type,label=identifier))+geom_point()+theme_classic()+geom_smooth(method="lm")+labs(colour="Lexical stratum")->plot
 
@@
 
-For both ideophones and non-ideophones, there was a strong correlation between the ratings and the guesses.
-This correspondence was slightly better for the ideophones (r = 0.66, 95% CI [0.44, 0.79], 95% CI [0.53, 0.76], t(99) = 8.68, p < .001) than for the non-ideophones (r = 0.41, 95% CI [0.29, 0.52], t(201) = 6.45, p < .001).
-To explore this relationship further, we created two linear regression models: one predicting guesses from ratings, ideophone status, and the interaction between these two factors, and a second model predicting ratings from guesses, ideophone status, and the interaction between these two factors.
-Both models again used the z-scores rather than the raw ratings and guesses.
+For both ideophones and prosaic words, there was a strong correlation between the ratings and the guesses.
+This correspondence was slightly better for ideophones (r = 0.66, 95% CI [0.44, 0.79], 95% CI [0.53, 0.76], t(99) = 8.68, p < .001) compared to prosaic words (r = 0.41, 95% CI [0.29, 0.52], t(201) = 6.45, p < .001).
+To explore this relationship further, we created two linear regression models: one predicting guesses from ratings, lexical stratum, and the interaction between these two factors, and a second model predicting ratings from guesses, lexical stratum, and the interaction between these two factors.
+Both models again used z-scores rather than raw ratings and guesses.
 The models were created using the R package `lmerTest` (version `r packageVersion("lmerTest")`) [@lmertest].
-
 The output of the first model (predicting guesses from ratings) is shown in Table \@ref(tab:guessesmodel).
 
-<caption> (\#tab:guessesmodel) Linear regression model predicting guesses from ratings, ideophone status, and the interaction between these two factors. </caption>
+<caption> (\#tab:guessesmodel) Linear regression model predicting guesses from ratings, lexical stratum, and the interaction between these two factors. </caption>
 ```{r correlations and first regression}
@@
 
-m1 <- lm(data=comparison_dat,guesses~ratings*ideophone)
+comparison_dat%>%
+  mutate(stratum=ifelse(ideophone=="y","ideophone","prosaic"))->comparison_dat
+
+m1 <- lm(data=comparison_dat,guesses~ratings*stratum)
 #summary(m1)
@@
 The model confirmed that ratings significantly predict guesses, with higher ratings leading to higher guesses.
-There was also a main effect of ideophone, and an interaction effect between ideophone and rating.
+There was also a main effect of lexical stratum, and an interaction effect between stratum and rating.
 The model is easiest to interpret by plotting the interaction, shown in Figure \@ref(fig:interaction).
 
-```{r interaction,fig.cap="Interaction between ratings and ideophone when predicting guesses"}
-ggpredict(m1,c("ratings","ideophone"))%>%plot()
-```
-
-The plot shows that higher ratings lead to better guessing accuracy for both ideophones and non-ideophones.
-The interaction effect appears because in the case of words with *low* iconicity ratings, guessing accuracy for ideophones is relatively poorer than for non-ideophones.
-At the top of the scale, highly rated ideophones also appear to be guessed slightly better than non-ideophones with comparable ratings.
-However, the difference here does not appear to be significant as the confidence intervals for the two lines overlap.
+```{r interaction,fig.cap="Interaction between ratings and lexical stratum when predicting guesses"}
+ggpredict(m1,c("ratings","stratum"))%>%plot()
+```
+
+The plot shows that higher ratings lead to better guessing accuracy for both ideophones and prosaic words.
+The interaction effect appears because for words with *low* iconicity ratings, guessing accuracy for ideophones is relatively poorer than for prosaic words.
 We will return to this in the discussion.
@@
 
-<caption> (\#tab:ratingsmodel) Linear regression model predicting ratings from guesses, ideophone status, and the interaction between these two factors. </caption>
+<caption> (\#tab:ratingsmodel) Linear regression model predicting ratings from guesses, lexical stratum, and the interaction between these two factors. </caption>
 ```{r ratingsmodel,fig.cap="Model predicting guesses from ratings and ideophone status"}
-m3 <- lm(data=comparison_dat,ratings~guesses*ideophone)
+m3 <- lm(data=comparison_dat,ratings~guesses*stratum)
 
@@
 
-The model shows that guesses significantly predict ratings, as does ideophone status, but that there was no interaction between these two predictors.
+The model shows that guesses significantly predict ratings, as does lexical stratum, but that there was no interaction between these two predictors.
 This is shown in Figure \@ref(fig:ratingsinteraction).
-The lines for ideophones and non-ideophones are parallel, indicating that differences in guesses correspond to differences in ratings *in the same way* for both ideophones and non-ideophones.
-However, the line for the ideophones is directly *above* the line for the non-ideophones, indicating that ideophones are rated higher in iconicity than non-ideophones--even when guessed at the same accuracies.
+The lines for ideophones and prosaic words are parallel, indicating that differences in guesses correspond to differences in ratings *in the same way* for both ideophones and prosaic words.
+However, the line for the ideophones is directly *above* the line for prosaic words, indicating that ideophones are rated higher in iconicity than prosaic words--even when guessed at the same accuracies.
 
 ```{r ratingsinteraction,fig.cap="Relationship between ideophone status, guessability, and predicted rating"}
-ggpredict(m3,c("guesses","ideophone"))%>%plot()
-```
-
-Finally, the lower correlation between guesses and ratings obtained for non-ideophones compared to ideophones suggests that participants may not have been as consistent or reliable when rating non-ideophones compared to when rating ideophones.
-To further investigate this, we calculated the person-total correlation for the rating data [@curran_methods_2016; @motamedi_iconicity_2019], for ideophones and non-ideophones separately.
-Figure \@ref(fig:ratingconsistency) shows the agreement between raters (expressed as the correlation between each individual rating, and the by-item average) for ideophones and non-ideophones respectively.
+ggpredict(m3,c("guesses","stratum"))%>%plot()
+```
+
+Finally, the lower correlation between guesses and ratings obtained for prosaic words compared to ideophones suggests that participants may not have been as consistent or reliable when rating prosaic words compared to when rating ideophones.
+To further investigate this, we calculated the person-total correlation for the rating data [@curran_methods_2016; @motamedi_iconicity_2019], for ideophones and prosaic words separately.
+Figure \@ref(fig:ratingconsistency) shows the agreement between raters (expressed as the correlation between each individual rating, and the by-item average) for ideophones and prosaic words respectively.
 The dots indicate the mean while the lines indicate 95% confidence intervals.
-Again, since these ratings were from non-Japanese speaking participants, I have also added data from native Japanese speaking participants from Thompson et al.
+Again, since these ratings were from non-Japanese speakers, we added data from Japanese speakers from Thompson et al.
 (2020) as a comparison.
@@
   cis[nrow(cis) + 1,] = list(name, 'ideophone', posR, posLower, posUpper)
-  cis[nrow(cis) + 1,] = list(name, 'non-ideophone', negR, negLower, negUpper)
+  cis[nrow(cis) + 1,] = list(name, 'prosaic', negR, negLower, negUpper)
 }
@@
   geom_errorbar(position=position_dodge(0.1),
-                width=0.1) + 
-  coord_flip() +ylim(0,0.6)+theme_classic()+labs(y="Correlation (r)",x="")->plot
+                width=0.1) +ylim(0,0.6)+theme_classic()+labs(y="Correlation (r)",x="",color="word type")->plot
 plot
@@
 
-```{r ratingconsistency,fig.cap="Consistency between participants for iconicity ratings of ideophones versus non-ideophones",out.width="70%",echo=FALSE}
-knitr::include_graphics("images/bootstrapping.png")
-```
-
-In both studies, participants appear to be more consistent with eachother when rating ideophones than when rating non-ideophones, though for Thompson et al.
+```{r ratingconsistency,fig.cap="Consistency between participants for iconicity ratings of ideophones versus prosaic words",out.width="70%",echo=FALSE}
+knitr::include_graphics("images/bootstrap.png")
+```
+
+In both studies, participants appear to be more consistent with each other when rating ideophones than when rating prosaic words, though for Thompson et al.
 the overlap of the confidence intervals indicates that the difference was not significant.
@@
 
-For both ideophones and non-ideophones, we found that the guesses and ratings from non-speakers were strongly correlated in the *same way*.
+For both ideophones and prosaic words, we found that the guesses and ratings from non-speakers were strongly correlated in the *same way*.
 This suggests that the two measures are indeed tapping into *something* in common, which we suggest are form-meaning associations.
-It's notable that these associations are found in both ideophones *and* non-ideophones (even if they are more common in the former), and that there are also ideophones that participants had no strong associations with--highlighting that there is no straightforward relationship between ideophones and iconicity; variable levels of iconicity can be found in both ideophones and prosaic words [see also @dingemanse_what_2016; @brown_phonetic_1955; @kunihira_effects_1971].
+It's notable that these associations are found acr
+
+in both ideophones *and* prosaic words (even if they are more common in the former), and that there are also ideophones that participants had no strong associations with--highlighting that there is no straightforward relationship between ideophones and iconicity; variable levels of iconicity can be found in both ideophones and prosaic words [see also @dingemanse_what_2016; @brown_phonetic_1955; @kunihira_effects_1971].
 
@@
 However, when iconicity is involved (and also funniness, as this paper found) the form of the words *is* important, and structural markedness may serve as a metacommunicative cue to signal this.
-The authors hypothesise that “Structural markedness confers a selective advantage on words intended to be iconic… as their recognisability would make them more fit to survive processes of cultural transmission in which the recognition of such intentions is functionally important” (Dingemanse and Thompson 2020: 218).
 The results from the rating task in this study suggest that structural markedness (in this case, reduplication) does indeed lead to the perception of iconicity.
@@
 Low iconicity ratings in non-ideophones generally correspond to chance guessing accuracy--reflecting a lack of associations--whereas equivalent ratings in ideophones correspond to *below chance* guessing accuracy--reflecting *negative associations* masked in the rating results by the tendency to inflate ratings for ideophones.
-The result highlights the subjective nature of form-meaning associations, and that by taking above-chance guessing accuracy as a measure of iconicity we are only picking up on those associations that happen to correspond--and crucially not to conflict--between (in this case) English and Japanese speakers.
+The result highlights the subjective nature of form-meaning associations [@occhino_iconicity_2017], and suggest that by taking above-chance guessing accuracy as a measure of iconicity we are only picking up on those associations that happen to correspond--and crucially not to conflict--between (in this case) English and Japanese speakers.
 This is something researchers should be aware of, because it means that decisions about *whom* to collect iconicity measurements from are very important.
@@
 Iconic effects are generally assumed to be driven by form-meaning resemblances, but since these often go together with structural markedness it would be useful to know the relative contribution of each factor in different situations and tasks.
-Since structural markedness is also subjective, the choice of participants used in the rating task will be important.
+Since structural markedness is also subjective and language-relative, the choice of participants used in the rating task will be important.
 Finally, having guesses alongside ratings would allow researchers to make better decisions about the cut-off point between "high" and "low" iconicity ratings, as these could be motivated by correlations with guessing accuracy, rather than e.g.
@@
 Similarly, descriptive (semiotic) analysis, along with cross-linguistic comparisons where possible could be used to understand and explain why some mappings are stronger or more universal than others.
-Conversely, behavioural measures could be used to tease apart some of the possible explanations for cross-linguistic biases.
-The two main contenders for explaining these biases are form-meaning associations or communicative pressures [@blasi_soundmeaning_2016].
-Since communicative pressures are unlikely to play a role in tasks where participants are simply judging or choosing words, behavioural measures could be used to distinguish these two hypotheses, thus allowing us to better understand the mechanisms behind results in these cross-linguistic studies.
 
@@
 
-## Towards a reproducible workflow
-
-Finally, with `icotools` we introduce a reproducible workflow for conducting rating and guessing experiments.
-This will make it easier for researchers to run these tasks, while enhancing comparability between future studies.
-Researchers can use the same paradigms to confirm current results, ask new questions, and run new analyses that build on existing findings.
-For example, this study has examined iconicity in the sensory vocabulary of Japanese, and found that the majority of words tested were actually guessed slightly above chance.
-With `icotools`, future researchers could run the exact same guessing experiment with different languages and in different semantic domains, to establish whether this is also true in other languages, and in other areas of the lexicon.
-
 # Conclusions
@@
 However, in *combination* ratings and guesses together can provide a picture of iconicity at different levels (both language internal and external), and in different degrees (low and high), while also uncovering how perceptions of iconicity are driven by both form-meaning associations and structural markedness.
-We have also made some methodological improvements to the guessing paradigm, improving on the robustness, sensitivity and discriminability of previous approaches.
-Finally, we introduce a reproducible workflow for creating rating and guessing tasks in the form of the Python package `icotools` (https://pypi.org/project/icotools/), so that future studies will be able to use these measures to build on current findings as well as asking new questions about what iconicity does in language, and how it does it.
+As the empirical study of ideophones and iconicity is coming of age, it is critical to couple descriptive and theoretical work with quantification and reproducible methods.
+We hope the methods and findings presented here provide a foundation for future work to build on, as well as a pointer towards asking new questions about what iconicity does in language, and how it does it.
 

### 2022-01-29 paper.Rmd
finished working

@@
 output:
-  bookdown::word_document2:
-    reference_docx: wordstyles.docx
+  bookdown::html_document2:
+ #   reference_docx: wordstyles.docx
     toc: true
@@
     css: custom.css
-  #  code_folding: hide
+    code_folding: hide
 always_allow_html: true
 bibliography: sources.bib
+csl: apa.csl
 
@@
 library(gghalves)
-knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message = FALSE)
+knitr::opts_chunk$set(echo = TRUE,warning=FALSE,message = FALSE)
 ```
@@
 Iconicity--defined here as a perceived resemblance between aspects of form and meaning--is now increasingly recognised as a *key property of language* [see e.g.
-@perniss_iconicity_2010; @perniss_bridge_2014; @dingemanse_arbitrariness_2015 for a review], raising questions about where iconic mappings come from, and what they do.
+@dingemanse_arbitrariness_2015; @perniss_iconicity_2010; @perniss_bridge_2014 for a review], raising questions about where iconic mappings come from, and what they do.
 To answer these questions, we first need to be able to *identify* iconicity in language and, ideally, to *measure* it.
@@
 
-With descriptive approaches, iconicity as a theoretical concept is coded for directly (e.g.
-@pietrandrea_iconicity_2002; @hwang_body_2017; @ostling_visual_2018; @thompson_defining_2019; @voronin_osnovy_2006; @flaksman2020stanislav).
+With descriptive approaches, iconicity as a theoretical concept is coded for directly [e.g.
+@pietrandrea_iconicity_2002; @hwang_body_2017; @ostling_visual_2018; @thompson_defining_2019; @voronin_osnovy_2006; @flaksman2020stanislav].
 This is more common and straightforward for sign languages than for spoken languages [@thompson_defining_2019].
 It is usually done manually, but Östling et al.
--@ostling_visual_2018 have shown for sign languages that (for some mappings at least) this can also be automated.
+[-@ostling_visual_2018] have shown for sign languages that (for some mappings at least) this can also be automated.
 Such studies usually involve cross-linguistic data, and aim to uncover universalities in how different languages map sound to meaning--that is, *where* iconicity comes from.
@@
 A wider variety of approaches target iconicity *indirectly* through related phenomena.
-For example, data-driven approaches (e.g.
-@wichmann_sound_2010; @blasi_soundmeaning_2016; @joo_phonosemantic_2019; @johansson_typology_2020; @winter_trilledr) use comparisons across unrelated languages to identify form-meaning correspondences that occur at rates higher than chance.
+For example, data-driven approaches [e.g.
+@wichmann_sound_2010; @blasi_soundmeaning_2016; @joo_phonosemantic_2020; @johansson_typology_2020; @winter_trilledr] use comparisons across unrelated languages to identify form-meaning correspondences that occur at rates higher than chance.
 This requires large amounts of parallel data from distinct phyla, and existing studies usually focus on basic vocabulary--where such data is most readily available.
@@
 However, they *do* rely on the existence of translation equivalents in multiple languages for the words under study.
-This can pose a particular challenge for highly iconic words, as these often also have highly specific meanings (@lupyan_language_2018; @akita_toward_2012).
+This can pose a particular challenge for highly iconic words, as these often also have highly specific meanings [@lupyan_language_2018; @akita_toward_2012].
 Thus, these approaches are less likely to be helpful for those with *specific* words for which iconicity measures are required.
@@
 These studies use large datasets of affective norms to identify phonological segments loaded with affective meaning (by taking average affectiveness values across all words containing those segments, and identifying segments with values deviating from the global neutral mean).
-Although limited to associations involving affect, this approach has been successfully used to investigate iconic effects in language processing [@schmidtke_effects_2018; Ullrich in prep; @aryani_affective_2018], and has even been used to explain the affective meaning of poems [@ullrich_relation_2017].
+Although limited to associations involving affect, this approach has been successfully used to investigate iconic effects in language processing [@schmidtke_effects_2018; @aryani_affective_2018], and has even been used to explain the affective meaning of poems [@ullrich_relation_2017].
 
@@
 encoding of sensory information [@winter_which_2017], semantic domains [@punselie_iconicity_2020], semantic neighbourhood density [@sidhu_lonely_2018], word class [@perry_iconicity_2015; @thompson_iconicity_2020], age of acquisition [@vinson_british_2008; @perry_iconicity_2015], facilitated processing [@thompson_link_2009; @occhino_role_2020], funniness and structural markedness [@dingemanse_playful_2020].
-However, ratings given are influenced by the linguistic experience of participants (@occhino_iconicity_2017; @sevcikova_sehyr_perceived_2019), so some care is needed to ensure measures are taken from appropriate participant groups.
+However, ratings given are influenced by the linguistic experience of participants [@occhino_iconicity_2017; @sevcikova_sehyr_perceived_2019], so some care is needed to ensure measures are taken from appropriate participant groups.
 Further, ratings from native speakers may also capture non-iconic regularities like semantic transparency and indexicality [@dingemanse_playful_2020; @winter_iconicity_2021], so cannot be taken as direct reflections of degree of iconicity.
@@
 In guessing experiments, participants are asked to guess the meaning of foreign/novel signs from a choice of two or more alternatives [e.g.
-@kohler_gestalt_1929; @tsuru_problem_1933; @brown_phonetic_1955; @kunihira_effects_1971; @ramachandran_synaesthesia_2001; @dingemanse_what_2016; @tzeng_specificity_2017; @perlman_iconicity_2015; @perlman_people_2018; @lockwood_sound-symbolism_2016].
+@kohler_gestalt_1929; @tsuru_problem_1933; @brown_phonetic_1955; @kunihira_effects_1971; @ramachandran_synaesthesia_2001; @dingemanse_what_2016; @tzeng_specificity_2017; @perlman_iconicity_2015; @perlman_people_2018; @lockwood_sound2016].
 Signs whose meanings are correctly guessed at rates higher than chance are considered iconic.
-The guessability of signs has also been linked to facilitated processing [@ormel_role_2009] and learnability [@perlman_people_2018; @lockwood_sound-symbolism_2016], and correlated with iconicity ratings [@punselie_iconicity_2020].
+The guessability of signs has also been linked to facilitated processing [@ormel_role_2009] and learnability [@perlman_people_2018; @lockwood_sound2016], and correlated with iconicity ratings [@punselie_iconicity_2020].
 However, some signs that were given low iconicity ratings were actually highly guessable, while there were also a few signs that, despite receiving high ratings, were not easily guessed  [@punselie_iconicity_2020: 23].
@@
 
-The data from the study, as well as the code used to produce the experiments and analyses can be found on the Open Science Framework, at https://osf.io/j57uc/?view_only=d59ffde4bc42467fafb71a904bef8d14.
+The data from the study, as well as the code used to produce the experiments and analyses can be found on the Open Science Framework, at https://osf.io/j57uc/?view_only=0f15b81806434bc99c29566d68f3f715.
 
@@
 
-The stimuli were 304 words taken from the *Japonic Sensory Lexicon* database [@McLean_JaponicSensoryLex_2022], which is a collection of words for 110 sensory concepts in 49 Japonic varities.
+The stimuli were 304 words taken from the *Japonic Sensory Lexicon* database [AUTHOR 2022], which is a collection of words for 110 sensory concepts in 49 Japonic varities.
 The words in the database were collated from three different sources: Sanada and Tomosada [-@sanada_kenbetsu_2015; -@sanada_kenbetsu_2018], and Hirayama [-@hirayama_gendai_1992].
@@
 For all three sources, words for each concept were collected from speakers of different Japonic varieties by asking the speakers to translate sentences from the standard variety into their local variety.
-Further description of the concepts and the sentences used to elicit them can be found in the Supplementary Materials
+Further description of the concepts and the sentences used to elicit them can be found in the Supplementary Materials.
 
@@
   mutate(domain=fct_relevel(domain,c("sound","action","shape & size","appearance","texture","temperature","taste","pain","bodily feeling","emotion")))%>%
-  ggplot(aes(x=domain,y=n,fill=stratum))+geom_col()+theme_minimal()+labs(x="Semantic domain",fill="Lexical stratum")+theme(axis.text.x = element_text(angle=15))+scale_fill_manual(values=c("darkgrey","black"))+ coord_fixed(ratio = 0.1)->plot
+  ggplot(aes(x=domain,y=n,fill=stratum))+geom_col()+theme_minimal()+labs(x="Semantic domain",fill="Lexical stratum")+theme(axis.text.x = element_text(angle=15))+scale_fill_manual(values=c("darkgrey","black"))+ coord_fixed(ratio = 0.1)
 ```
@@
 The differences between the two conditions are shown in Figure \@ref(fig:sensitivitycheck).
-A chi-squared test confirmed the differences to be significant (χ2(1)=4.69,p=.03).
+A chi-squared test confirmed the differences to be significant (*χ2(1)=4.69,p=.03*).
 
@@
 For both ideophones and prosaic words, there was a strong correlation between the ratings and the guesses.
-This correspondence was slightly better for ideophones (r = 0.66, 95% CI [0.44, 0.79], 95% CI [0.53, 0.76], t(99) = 8.68, p < .001) compared to prosaic words (r = 0.41, 95% CI [0.29, 0.52], t(201) = 6.45, p < .001).
+This correspondence was slightly better for ideophones (*r = 0.66, 95% CI [0.44, 0.79], 95% CI [0.53, 0.76], t(99) = 8.68, p < .001*) compared to prosaic words (*r = 0.41, 95% CI [0.29, 0.52], t(201) = 6.45, p < .001*).
 To explore this relationship further, we created two linear regression models: one predicting guesses from ratings, lexical stratum, and the interaction between these two factors, and a second model predicting ratings from guesses, lexical stratum, and the interaction between these two factors.
@@
 This suggests that the two measures are indeed tapping into *something* in common, which we suggest are form-meaning associations.
-It's notable that these associations are found acr
-
-in both ideophones *and* prosaic words (even if they are more common in the former), and that there are also ideophones that participants had no strong associations with--highlighting that there is no straightforward relationship between ideophones and iconicity; variable levels of iconicity can be found in both ideophones and prosaic words [see also @dingemanse_what_2016; @brown_phonetic_1955; @kunihira_effects_1971].
-
-However, ideophones were consistently rated *higher* in iconicity than non-ideophones—even when guessed at the same accuracies.
+It’s notable that these associations are found in varying amounts across both strata of the lexicon, highlighting that there is no straightforward relationship between ideophones and iconicity; variable levels of iconicity can be found in both ideophones and prosaic words [see also @dingemanse_what_2016; @kunihira_effects_1971].
+
+However, ideophones were consistently rated *higher* in iconicity than prosaic words—even when guessed at the same accuracies.
 We believe this is due to the majority of ideophones in the dataset being reduplicated.
-The two lowest rated ideophones–*sappari* and *syippori*–were among the few in the data that do not use a reduplicated template.
-Previous work has found a relationship between iconiticity ratings and structural markedness (Dingemanse and Thompson 2020).
-Ordinarily when we use words, the form of the words is not important--only their content.
-However, when iconicity is involved (and also funniness, as this paper found) the form of the words *is* important, and structural markedness may serve as a metacommunicative cue to signal this.
-The results from the rating task in this study suggest that structural markedness (in this case, reduplication) does indeed lead to the perception of iconicity.
-Interestingly, however, it does not seem to confer any advantage--over and above that provided by associations between form and meaning--in the guessing task.
+The two lowest rated ideophones–*sappari* ‘clean’ and *guttari ‘*exhausted*’*–were among the few in the data that do not use a reduplicated template.
+Previous work has found a relationship between iconicity ratings and structural markedness [@dingemanse_playful_2020].
+Ordinarily when we use words, the form of the words is not important–only their content.
+However, when iconicity is involved the form of the words *is* important, and structural markedness may serve as a metacommunicative cue to signal this.
+The results from the rating task suggest that structural markedness (in this case, reduplication) leads to the perception of iconicity.
+Interestingly, however, it does not seem to confer an advantage–over and above that provided by associations between form and meaning–in the guessing task.
 What the ratings seem to be picking up on is both form-meaning associations *and* structural markedness.
-If they were only picking up on structural markedness, then we would not expect the ratings to vary with the guesses in the same way for both ideophones and non-ideophones.
+If they were only picking up on structural markedness, then we would not expect the ratings to vary with the guesses in the same way for both ideophones and prosaic words.
 However, if they were only picking up on form-meaning associations (like the guesses seem to), then we would not expect ideophones to consistently receive higher iconicity ratings, even when guessed at the same accuracies.
 
-While ideophones and non-ideophones with high iconicity ratings were generally guessed equally well, there was an interaction effect such that ideophones with low iconicity ratings were guessed *worse* than non-ideophones with comparable ratings.
-Low iconicity ratings in non-ideophones generally correspond to chance guessing accuracy--reflecting a lack of associations--whereas equivalent ratings in ideophones correspond to *below chance* guessing accuracy--reflecting *negative associations* masked in the rating results by the tendency to inflate ratings for ideophones.
-The result highlights the subjective nature of form-meaning associations [@occhino_iconicity_2017], and suggest that by taking above-chance guessing accuracy as a measure of iconicity we are only picking up on those associations that happen to correspond--and crucially not to conflict--between (in this case) English and Japanese speakers.
+While ideophones and prosaic words with high iconicity ratings were generally guessed equally well, there was an interaction effect such that ideophones with low iconicity ratings were guessed *worse* than prosaic words with comparable ratings.
+Low iconicity ratings in prosaic words generally correspond to chance guessing accuracy–reflecting a lack of associations–whereas equivalent ratings in ideophones correspond to *below chance* guessing accuracy–reflecting *negative associations* masked in the rating results by the tendency to inflate ratings for ideophones.
+The result highlights the subjective nature of form-meaning associations [@occhino_iconicity_2017], and suggests that by taking above-chance guessing accuracy as a measure of iconicity we are only picking up on those associations that happen to correspond–and crucially not to conflict–between (in this case) English and Japanese speakers.
 This is something researchers should be aware of, because it means that decisions about *whom* to collect iconicity measurements from are very important.
@@
 For example, one person commented that *zarazara* as a word for ‘ROUGH’ sounds wrong to them because they associate the word *zara* with the clothing store ZARA, and clothes are soft.
-These could be masking either a lack of resemblance between form and meaning, or a resemblance between form and meaning that is ignored in the face of the conflicting association.
+These could be masking either a lack of resemblance between form and meaning, or a resemblance between form and meaning that is missed in the face of the conflicting association.
 Of course, conversely one could argue that high guessing accuracies could then *also* be explained by non-resemblance based associations.
@@
 Thus, if they do exist, we predict that the majority of non-resemblance based associations should be reflected in poorer rather than higher guessing accuracies.
-It is interesting that conflicting associations appear to have a stronger effect in ideophones (some of which were guessed at accuracies significantly below chance) than in non-ideophones (which were guessed below chance only rarely).
-Perhaps because participants are more likely to view form-meaning relationships in ideophones as meaningful (due to their structural markedness), they are more likely to attach conflicting associations to ideophones, leading to a stronger sense that the ideophone should correspond to the *opposite* of the given meaning.
-
-Finally, the comparison between guesses and ratings highlights a bias in the design of the rating task, as all the words in the data were in the end rated as "slightly" iconic (even by non-speakers), whereas the guessing results show that a good number of these were not guessed any better than chance.
-This is probably an artefact of the design of the rating task, in which "arbitrary" is only 1 of the 7 or 10 points on the scale--the rest indicating varying degrees of form-meaning resemblance.
+
+It is interesting that conflicting associations appear to have a stronger effect in ideophones (some of which were guessed at accuracies significantly below chance) than in prosaic words (which were guessed below chance only rarely).
+Perhaps because participants are more likely to view form-meaning relationships in ideophones as meaningful (due to their structural markedness), they are more likely to attach conflicting associations to ideophones, leading to a stronger sense that the ideophone should correspond to the *opposite* of the given meaning [for more on this see discussion in @webster_2017; @akita_ideophone_2019: 19].
+This is supported by the larger person-total correlations reported for ideophones compared to prosaic words in Section 3.3; that participants were more consistent with each other when rating ideophones suggests that intuitions about these words were more pervasive.
+
+Finally, the comparison between guesses and ratings highlights a bias in the design of the rating task.
+All the words in the data were rated  “slightly” iconic, even though the guessing results show a good number of these were not guessed any better than chance.
+This is probably an artefact of the scale used, in which arbitrariness is represented by only 1 of the 7 points, while the other 6 all indicate varying degrees of form-meaning resemblance.
 This is not so problematic, as the ratings still correlate with guessing accuracy, indicating that the relative differences in iconicity still hold.
@@
 
-To sum up, by directly comparing iconicity ratings and guessing accuracies for both ideophones and non-ideophones, we are able to better understand how these measures relate to each other and to iconicity.
-Differences between iconicity ratings of ideophones and non-ideophones--even when guessability is the same--highlight the role of structural markedness in enhancing perceived iconicity.
+To sum up, by directly comparing iconicity ratings and guessing accuracies for both ideophones and prosaic words, we are able to better understand how these measures relate to each other and to iconicity.
+Differences between iconicity ratings for ideophones and prosaic words–even when guessability is the same–highlight the role of structural markedness in enhancing perceived iconicity.
 Consistencies between guesses and ratings within these word types reassure us that, despite this, form-meaning association biases play a large role in explaining each measure.
-The unexpected result of ideophones also being poorly guessed reminds us that these biases are just that--subjective--and thus, while good guessing accuracies can be interpreted as positive evidence of language-external iconicity, average or poor guessing accuracies *cannot* be interpreted as negative evidence of iconicity of either kind (language-internal or external).
-Similarly, while high ratings are likely to be a good indication of iconicity, researchers should be cautious of taking lower ratings indicating "slight" iconicity at face value.
+The unexpected result of ideophones also being poorly guessed reminds us that these biases are just that–subjective–and thus, while good guessing accuracies can be interpreted as positive evidence of language-external iconicity, average or poor guessing accuracies *cannot* be interpreted as negative evidence of iconicity of either kind (language-internal or external).
+Similarly, while high ratings are likely to be a good indication of iconicity, researchers should be cautious of taking lower ratings indicating “slight” iconicity at face value.
 
@@
 Given the limitations of each measure discussed above, for a full picture of iconicity in the lexicon, a synthesis of measures is recommended.
-Iconicity ratings from native speakers can tell us which mappings are meaningful to them, while comparisons with guessability for non-speakers can establish which of these mappings are likely to be meaningful on their own, versus which *become* meaningful through experience with the rest of the lexicon (language-external versus language-internal iconicity).
-@occhino_role_2020 found differential effects of these two types of mappings in sign processing by signers of different proficiencies.
-They found that both types of iconicity were helpful to signers of a lower proficiency, but that for highly proficient signers only the most pervasive, language-external mappings made a difference to processing.
-
-Since structural markedness appears to boost ratings but not guessability, the two measures could also be used together to tease apart the influence of structural markedness versus form-meaning resemblances in driving iconic effects.
-Iconic effects are generally assumed to be driven by form-meaning resemblances, but since these often go together with structural markedness it would be useful to know the relative contribution of each factor in different situations and tasks.
-Since structural markedness is also subjective and language-relative, the choice of participants used in the rating task will be important.
-Finally, having guesses alongside ratings would allow researchers to make better decisions about the cut-off point between "high" and "low" iconicity ratings, as these could be motivated by correlations with guessing accuracy, rather than e.g.
+Iconicity ratings from native speakers can tell us which mappings are meaningful to them, while comparisons with guessability for non-speakers can establish which of these mappings are likely to be meaningful on their own, versus which *become* meaningful through experience with the rest of the lexicon.
+Occhino et al.
+[-@occhino_role_2020] refer to this distinction as language-external versus language-internal iconicity.
+It is a distinction with real correlates, as their study found differential effects for each type of iconicity on sign language processing.
+
+Since structural markedness appears to boost ratings but not guessability, the two measures could be used together to tease apart the influence of structural markedness versus form-meaning resemblances in driving iconic effects.
+Iconic effects are generally assumed to be driven by form-meaning resemblances, but as these often go together with structural markedness it would be useful to know the relative contribution of each factor in different situations and tasks.
+Having guesses alongside ratings would also allow researchers to make better decisions about the cut-off point between “high” and “low” iconicity ratings, as these could be motivated by correlations with guessing accuracy, rather than e.g.
 arbitrarily dividing the scale at the half-way point, or using percentiles tied to particular datasets.
@@
 @kwon_empirically_2017].
-Similarly, descriptive (semiotic) analysis, along with cross-linguistic comparisons where possible could be used to understand and explain why some mappings are stronger or more universal than others.
-
-## Methodological improvements and evaluation
-
-We also sought to evaluate different rating and guessing paradigms, and were able to make some methodological improvements--particularly to the guessing design.
-We contrasted two different guessing paradigms--one where participants are given a word and have to match it to the correct meaning from two translations, and another where participants are given a meaning and have to match it to the correct word from two words.
-Content-wise, choosing between words is more comparable to the design of a rating task, as both give the meaning first and involve only one English translation.
-This is important as the use of translations leads to several complications in the experiment design.
+Similarly, descriptive (semiotic) analysis, along with cross-linguistic comparisons where possible, could be used to understand where these associations come from and explain why some are stronger or more universal than others.
+
+## Methodological contributions
+
+As a final contribution of this study, having evaluated different guessing and rating paradigms, we were able to make some methodological improvements—particularly to the guessing design.
+We contrasted two different guessing paradigms–one where participants are given a word and asked to match it to the correct meaning from two translations, and another where participants are given a meaning and have to match it to the correct word from two words.
+Content-wise, choosing between words is more comparable to the design of the rating task, as both give the meaning first and involve only a single English translation.
+This is important as the use of translations leads to several complications in the interpretation of guessing results.
 First, English-speaking participants can be expected to have more associations with English words than with unknown Japanese words, which could make the task more sensitive to the particular translations chosen.
-In addition, care has to be taken when choosing foils as well, as they should preferably be from the same semantic domain, of a similar length of characters, and not synonyms or antonyms of the correct translation.
-This makes the guessing between translations design more difficult to use, particularly in small semantic domains (e.g.
+In addition, care has to be taken when choosing foils, as they should preferably be from the same semantic domain, of a similar length of characters, and neither synonyms nor antonyms of the correct translation (see description in Section 2.3).
+This makes the guessing between translations design more difficult to implement, particularly for small semantic domains (e.g.
 taste).
@@
 In contrast, a task in which participants guess between words is much easier to operationalise.
-This design can be easily adopted to any semantic domain or any kind of data, and the foils can be chosen either randomly from the other trials or selected based on specific criteria.
-In our case we chose foils that were phonologically as distinct as possible from the word being tested.
-The first reason for this was theoretical: in a task designed to pick up on form-meaning resemblance, words that sound very different should not be suited to that meaning, enhancing the effect of iconicity.
-The second was practical: our stimuli had artificially flat intonations, which has been shown to decrease performance in guessing studies [@kunihira_effects_1971; @dingemanse_what_2016].
-By creating opposite sounding words, we tried to increase performance in the guessing task despite the degraded stimuli.
-
-When comparing results from the two designs, choosing between words is again the more favourable of the two.
-First, as expected changing the translation or foil used led to less inconsistent results when choosing between words compared to when choosing between translations.
-Second, the range of guessing scores is much wider when choosing between words compared to choosing between translations, with more words guessed at high accuracy levels, and fewer words around chance level.
+This design can be easily adopted to any semantic domain or type of data, with foils either chosen randomly from among other items in the task, or specified using motivated criteria.
+In our case, we used foils that were maximally phonologically distinct from the word being tested.
+Our logic was that if the real word is a good fit for the meaning, then a word that sounds very different to it should be a bad fit for the meaning.
+So using opposite-sounding foils enhances the task’s sensitivity to iconicity.
+
+When comparing results between the two designs, the meaning-to-word design clearly emerges as the more favourable of the two.
+First, as expected changing the translation or foil used led to less inconsistent results when choosing between words compared to when choosing between translations (Section 3.1).
+Second, the range of guessing scores is much wider in the meaning-to-word design compared to the word-to-meaning design, with more words guessed at high (and low) accuracy levels, and fewer words guessed at chance (Section 3.2).
 This is especially true when the foils used are maximally phonologically distinct.
-However, for datasets that are relatively higher in iconicity to begin with--e.g.
-gestures or hand signs--using random foils will likely already produce good results.
-The better results in the choosing between words design can be easily explained, as the task was comparatively easier than in the choosing between translations design, where participants were restricted to choosing between two similar options (non-antonyms from the same semantic domain).
-The options in the choosing between words design are more distinct--even maximally so.
-In sum, the choosing between words design is both more robust, more sensitive to iconicity, and more discriminating between lesser and greater amounts of iconicity, so this is the design that we recommend and that we have implemented in `icotools`.
-
-We also compared our iconicity ratings from non-speakers with iconicity ratings from native speakers in Thompson et al.
-[-@thompson_iconicity_2020].
-We found that, although using non-speakers resulted in a lesser spread of measures (suggesting that native speakers are more confident in giving high and low ratings than non-native speakers), when evaluating the agreement between raters, ratings from non-speakers were just as reliable as ratings from native speakers--as well as being fairly robust to different choices of translation.
-Ratings from non-speakers were more reliable for ideophones than for non-ideophones--but this is not to say that the ratings for non-ideophones were unreliable.
-Rather, the ratings for ideophones were *particularly* reliable, probably because raters were more likely to have stronger intuitions about these words due to their structural markedness, and because they are more likely to be iconic in the first place.
-The same pattern was seen in the ratings from native speakers, although it did not reach statistical significance.
-Since both types of ratings are fairly reliable, our recommendation would be to choose participants for rating tasks according to how the ratings are going to be used.
-For example, to predict language processing in adult native speakers of a language, it would make sense to collect ratings from other adult native speakers of the same language.
+The same effect can be seen in form-to-meaning designs when comparing baseline differences in guessing accuracies between studies that used antonyms versus random words as foils [e.g.
+@lockwood_sound2016 versus @dingemanse_what_2016].
+In sum, our new meaning-to-word guessing design is both more robust to different choices of translations and foils, more sensitive to iconicity, and more discriminating between lesser and greater amounts of iconicity.
+
+We also considered the effects of using non-native speakers versus native speakers as raters in the rating task.
+We found that using native speakers provided a greater spread of measures (Section 3.2), probably because native speakers’ familiarity with the words makes them more confident in giving high or low ratings.
+However, we did not find any difference in the consistency of the ratings provided between the two groups—non-native speakers were just as consistent as native speakers in rating the iconicity of Japanese words.
+Since both types of ratings are fairly reliable, we recommend choosing raters according to what makes the most theoretical sense in regards to the question being asked.
+For example, to predict language processing in adult native speakers, it makes sense to also use native speakers as raters; to predict outcomes in second language acquisition, using non-speakers is more theoretically sound.
+The important thing to remember is that perceptions of iconicity are subjective and experience dependent, and this needs to be accounted for when collecting iconicity measures [@occhino_iconicity_2017; @occhino_role_2020].
+
+We also created a python package, icotools, which can be used to automatically generate guessing and rating tasks from wordlists, following the designs described in Section 2.4 and Section 2.5.
+A full discussion of icotools and its functionality is provided in the Supplementary Materials.
+Some of its main advantages are (1) the ability to generate both guessing and rating tasks from the same wordlist, (2) the ability to specify multiple translations and multiple foils per word, so that results cannot be unduly influenced by one particular choice of translation or foil, and (3) the ability to include a set of ‘control items’ in every experiment, as an additional way to monitor whether participants are behaving as expecting (see Section 2.2).
+As well as audio files, the package supports videos and images as stimuli formats, making it suitable for investigations of iconicity in multiple modalities.
 
@@
 
-This study has asked how we can make existing measures of iconicity even better, by critically evaluating and comparing two of the most promising behavioural measures of iconicity--iconicity ratings and guessing tasks.
+This study has asked how we can make existing measures of iconicity even better, by critically evaluating and comparing two of the most promising behavioural measures of iconicity–iconicity ratings and guessing tasks.
 In comparing the two measures, we were able to get a better sense of the relative strengths and weaknesses of each.
-Our main finding is that the two measures are more informative when used together than when used in isolation.
-In isolation, it is difficult to determine the degree to which high iconicity ratings are driven by form-meaning associations versus structural markedness, and to have an objective sense of which ratings are "low" or "high".
-In isolation, guesses provide only a narrow window into iconicity of a particular kind--strong, language-external associations.
-However, in *combination* ratings and guesses together can provide a picture of iconicity at different levels (both language internal and external), and in different degrees (low and high), while also uncovering how perceptions of iconicity are driven by both form-meaning associations and structural markedness.
+Our main finding is that the two measures are more informative when used together than when used alone.
+In isolation, it is difficult to determine the degree to which high iconicity ratings are driven by form-meaning associations versus structural markedness, and to have an objective sense of which ratings are “low” or “high”.
+In isolation, guesses provide only a narrow window into iconicity of a particular kind–strong, language-external associations.
+However in *combination,* ratings and guesses together provide a picture of iconicity of different types (language internal and external), and in different degrees (low and high), while also uncovering how perceptions of iconicity are driven by both form-meaning associations and structural markedness.
 As the empirical study of ideophones and iconicity is coming of age, it is critical to couple descriptive and theoretical work with quantification and reproducible methods.

### 2022-01-30 paper.Rmd
version of R markdown which has the iconicity box code at the end

@@
 # References
+
+```{r}
+oppres%>%
+  rename(guessing_accuracy=score)%>%
+  left_join(othersratings,by="identifier")->t
+
+t%>%
+  ggplot(aes(x=mean_rating,y=guessing_accuracy))+geom_point()->plot
+
+ggplotly(plot)
+
+classify <- function(score){
+  if (score<0.5){return(1)}
+  else if(score<0.75){return(2)}
+  else{return(3)}
+}
+
+othersratings%>%
+  arrange(mean_rating)%>%
+  rowid_to_column()%>%
+  mutate(quartile=rowid/304)%>%
+  rowwise()%>%
+  mutate(rating_score=classify(quartile))->ratings_transformed
+
+guess_classify <- function(score){
+  if (score<=1/3){return(NA)}
+  else if(score<2/3){return(1)}
+  else if(score<5/6){return(2)}
+  else{return(3)}
+}
+
+oppres%>%
+  rowwise()%>%
+  mutate(guess_score=guess_classify(score))->guesses_transformed
+
+thing <- inner_join(guesses_transformed,ratings_transformed,by="identifier")%>%drop_na()
+
+table(thing$guess_score,thing$rating_score)
+
+thing%>%
+  rowwise()%>%
+  mutate(form=str_split(identifier,"_")[[1]][1])%>%
+  left_join(info,by="form")%>%
+  mutate(random_x=runif(min=1,max=4,n=1))%>%
+  mutate(random_y=runif(min=1,max=4,n=1))%>%
+  ggplot(aes(x=random_x,y=random_y,label=identifier,colour=ideophone))+facet_grid(guess_score~rating_score)+geom_jitter()+geom_text_repel()->plot
+p <- ggplotly(plot)
+p
+htmltools::save_html(
+  html = htmltools::as.tags(
+    x = plotly::toWebGL(p),
+    standalone = TRUE),
+  file = "test.html")
+htmlwidgets::saveWidget(p,"test.html")
+```

### 2022-02-28 paper.Rmd
deleted iconicity box code
anonymise

--- 2022-01-29 paper.Rmd
@@
 Behavioural approaches involve the collection of data from naive experimental participants, which can reveal something about the iconicity of given form-meaning pairings.
-The only requirement is the human participants for the study, and the largest amount of iconicity measurements from the widest variety of languages have been collected using these methods.
+The only requirement is the human participants for the study, and the largest number of iconicity measurements from the widest variety of languages have been collected using these methods.
 There are two main approaches: iconicity rating tasks and guessing experiments.
@@
 
-For the new version of the guessing experiments, we minimised the amount of English words involved in the task by having participants match a single English translation to the corresponding word in Japanese, choosing between two possible Japanese words.
+For the new version of the guessing experiments, we minimised the number of English words involved in the task by having participants match a single English translation to the corresponding word in Japanese, choosing between two possible Japanese words.
 The instructions used were as follows:
@@
 Since /a/ is often the most phonologically distant vowel from many of the vowels in the Japanese sound system, to avoid the foil words all having similar vowels, a different approach was used for substituting vowels.
-Instead of using feature values, vowels were substituted with the vowel obtained by rotating the vowel space 180 clockwise or counterclockwise.
-So /u/ is substituted with either /a/ or /i/, and /a/ is substituted with either /i/ or /u/ (see Figure \@ref(fig:vowels)).
+Instead of using feature values, vowels were substituted with the vowel obtained by rotating the vowels at the endpoints of the vowel space triangle 120 degrees clockwise or counterclockwise, and flipping the vowels in the middle.
+So /u/ is substituted with either /a/ or /i/, /a/ is substituted with either /i/ or /u/, /i/ is substituted with either /a/ or /u/, and /e/ and /o/ are substituted with each other (see Figure \@ref(fig:vowels)).
 Finally, reduplicated words were ‘unreduplicated’ when creating foil words.
@@
 However, the data from the current study was chosen from a domain known to be high in iconicity, whereas the data from Thompson et al.
-was more varied, with proportionally less ideophones.
+was more varied, with proportionally fewer ideophones.
 So, this could simply be a reflection of the differences between the two datasets rather than relating to the methods used.
@@
 What the ratings seem to be picking up on is both form-meaning associations *and* structural markedness.
-If they were only picking up on structural markedness, then we would not expect the ratings to vary with the guesses in the same way for both ideophones and prosaic words.
+If they were only picking up on structural markedness, then we would not expect the ratings to correspond with the guesses in the same way for both ideophones and prosaic words.
 However, if they were only picking up on form-meaning associations (like the guesses seem to), then we would not expect ideophones to consistently receive higher iconicity ratings, even when guessed at the same accuracies.
@@
 
-It is interesting that conflicting associations appear to have a stronger effect in ideophones (some of which were guessed at accuracies significantly below chance) than in prosaic words (which were guessed below chance only rarely).
-Perhaps because participants are more likely to view form-meaning relationships in ideophones as meaningful (due to their structural markedness), they are more likely to attach conflicting associations to ideophones, leading to a stronger sense that the ideophone should correspond to the *opposite* of the given meaning [for more on this see discussion in @webster_2017; @akita_ideophone_2019: 19].
+It is interesting that conflicting associations appear to have a stronger effect in ideophones (some of which were guessed at accuracies significantly below chance, reflecting a strong bias *against* the word having the specified meaning) than in prosaic words (which were guessed below chance only rarely).
+Perhaps because participants are more likely to view form-meaning relationships in ideophones as meaningful (due to their structural markedness), they attach more weight to perceived conflicts between a form and its given meaning, resulting in a stronger pull away from the correct form [for more on this see discussion in @webster_2017; @akita_ideophone_2019: 19].
 This is supported by the larger person-total correlations reported for ideophones compared to prosaic words in Section 3.3; that participants were more consistent with each other when rating ideophones suggests that intuitions about these words were more pervasive.
